### 2016-08-21 ensemble_clustering.tex
first commit, init by Yan, ensemble_clustering

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{color}
\usepackage{bm}
%\usepackage[vlined,boxed,ruled]{algorithm2e}
\usepackage{url}
\usepackage{xspace}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\def\bE{{\bf E}}
\def\blambda{{\bm \lambda}}
\def\calL{{\mathcal{L}}}
\def\bL{{\bf L}}
\def\bO{{\bf O}}
\def\bU{{\bf U}}
\def\bV{{\bf V}}
\def\dsR{\mathds{R}}
\def\bX{{\bf X}}
\def\bx{{\bf x}}
\def\btx{{\tilde{\bf x}}}
\def\by{{\bf y}}
\def\bw{{\bf w}}
\def\btw{{\tilde{\bf w}}}
\def\tK{\tilde{K}}
\def\txi{\tilde{\xi}}
\def\tildeb{{\tilde{b}}}
\def\tphi{{\tilde{\phi}}}
\def\bz{{\bf z}}
\def\br{{\bf r}}
\def\bv{{\bf v}}
\def\bb{{\bf b}}
\def\bp{{\bf p}}
\def\bA{{\bf A}}
\def\bI{{\bf I}}

\def\bx{{\bf x}}
\def\bX{{\bf X}}
\def\by{{\bf y}}
\def\bY{{\bf Y}}
\def\bw{{\bf w}}
\def\bW{{\bf W}}
\def\balpha{{\bm \alpha}}
\def\bmu{{\bm \mu}}
\def\bK{{\bf K}}
\def\bg{{\bf g}}
\def\bp{{\bf p}}
\def\p{p}
\def\bP{{\bf P}}

\def\balpha{{\bm \alpha}}
\def\bbeta{{\bm \beta}}
\def\eg{{\emph{e.g.}}}

\def\ttTP{{\tt TP}}
\def\ttFP{{\tt FP}}
\def\ttFN{{\tt FN}}

\def\st{{\text{s.t.}}}
\def\rank{{\text{rank}}}

\def\yanred{\textcolor{red}}
\def\yanblue{\textcolor{blue}}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}
 \begin{document}

% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

\title{Maximum Margin Matrix Factorization for Ensemble Clustering}

%\author{AAAI Press\\
%Association for the Advancement of Artificial Intelligence\\
%2275 East Bayshore Road, Suite 160\\
%Palo Alto, California 94303\\
%}

\maketitle

\begin{abstract}
In this paper, we propose an efficient maximum margin matrix factorization algorithm for ensemble clustering.
Our contributions include i) introduction of an efficient optimization for matrix completion based ensemble clustering methods; ii) an intuitive motivation for a $\ell_{2,1}$ loss.
\end{abstract}

\section{Introduction}

A single clustering result could be inaccurate, so some researchers study ensemble clustering methods to boost the performance,
such as the algorithms proposed in~\cite{yiicdm2012robust,gaoijcai2016robust}, to name a few.

The key aim of matrix completion based methods is to detect the anomalous clusters (bad partitions/assigments) and reconstruct the real assignments,
which is shown in Figure~\ref{fig:anomalous_cluster}.
A typical formulation of matrix completion based methods then can be written as below:
\begin{align}\label{eq:typical_mc}
  \min_{\bX} ~&~ || \bX - \bL ||_2^2   \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  ,
\end{align}
\noindent
where $k$ is a pre-defined rank constraint,
and $\bL \in \dsR^{N \times MK}$.
Here we denote $M$ and $K$ as the number of single clustering assignments and the number of clusters, respectively.
However, the least square loss used in matrix completion is sensitive to the abnormal errors, namely outliers, the not appropriate to capture the anomalous assignments.
The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{2,1}$ norm on $\bX$, which is as follow
\begin{align}\label{eq:mc_l21_gaospaper}
  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{2,1}   \nonumber \\
  \st        ~&~ \rank(\bX) \leq k   ,
\end{align}
\noindent
where $|| \bX ||_{2,1} = \sum_{j = 1}^{MK} \sqrt(\sum_{i=1}^{N}) = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
which would make some columns of $\bX$ as zeros (beware the direction of the computation of the $\ell_{2,1}$ norm, more details in~\cite{nienips2010efficient}).
Nevertheless, it does not consider the outliers in their loss function.
In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{2,1}$ is equivalent to $|| \bX - \bO ||_{2,1}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
Therefore, we propose to apply $\ell_{2,1}$ to capture the outliers as well as anomalous columns, which can be written as below
\begin{align}\label{eq:mc_l21}
  \min_{\bX} ~&~ || \bL - \bX ||_{2,1}    \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  .
\end{align}
Problem~(\ref{eq:mc_l21}) is NP-hard due to the presence of the low rank constraint.
For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as
\begin{align}\label{eq:mf_l21}
  \min_{\bX} ~&~ || \bL - \bX ||_{2,1}    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
\end{align}
\noindent
Note that we have totally $K$ single clustering assignments.
Intuitively, we could set $k = K$ in Problem~(\ref{eq:mf_l21}).
Most existing matrix factorization optimization methods only consider smooth loss functions,
but the $\ell_{2,1}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
In this paper, we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.

\section{ALM Optimization}

By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:mf_l21}) as below:
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{2,1}   \nonumber \\
  \st             ~&~ \bE = \bL - \bX   \nonumber \\
                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}
\end{align}
The augmented Lagrangian function of Problem~(\ref{eq:mf_l21}) is as below
\begin{align}\label{eq:lagrangian_l21}
  \calL = || \bE ||_{2,1} + \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2   ,
\end{align}
\noindent
where $\bX = \bU \bV$,
and $\blambda$ are the Lagrangian multipliers (or dual variables).
Then we could update $\bX$ and $\bE$ alternatively.

Specifically, to update $\bX$, we consider the following problem:
\begin{align}\label{eq:problem_X}
  \min_{\bX} ~&~ \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2  \nonumber  \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
\end{align}
Problem~(\ref{eq:problem_X}) includes a smooth loss function w.r.t. $\bX$, thus can be solved by a standard matrix factorization method, such as~\cite{yanijcai2015scalable,tanicml2014riemannian,vandereyckensiamjo2013low}.

Problem~(\ref{eq:problem_X}) can also be rewritten as below
\begin{align}\label{eq:problem_X2}
  \min_{\bX} ~&~ \frac{\mu}{2} \Big( || \bX - \bL + \bE ||_F^2 + \frac{2}{\mu} \blambda^{\top} (\bX - \bL + \bE) + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
             ~&~ - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
  \st.       ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
\end{align}
\noindent
We can obtain the final problem w.r.t. $\bX$:
\begin{align}\label{eq:problem_X3}
  \min_{\bX} ~&~ || \bX - \bL + \bE + \frac{\blambda}{\mu} ||_F^2   \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
\end{align}
\noindent
There are a number of optimization algorithms for Problem~(\ref{eq:problem_X3}), such as LRGeomCG\footnote{\yanred{Code available at~\url{http://www.unige.ch/math/vandereycken/matrix_completion.html}}}.

To update $\bE$, we consider the following problem:
\begin{align}\label{eq:problem_E}
  \yanred{
  \min_{\bE} ~ || \bE ||_{2,1} + \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2   .
  }
\end{align}
\noindent
The above problem could be solved by the algorithm proposed in~\cite{nienips2010efficient,yangijcai2011l21}.
\yanred{Yan Yan: I am working on this optimization algorithm.}

\section{An Option on Loss Function: Max Margin}

In fact, the assignments $\bL$ contains only $0/1$ values (discrete ordinal values).
This fits the setting in~\cite{yanijcai2015scalable} very much.
It could be a contribution, since maximum margin loss achieves better performance on discrete ordinal values.
\yanred{Note: we may leave this extension as a journal?}

\section{Another Option on Loss Function: $\ell_{2,1}$ to $\ell_1$ loss}

$ell_{2,1}$ loss could be difficult to optimize.
A simple way is to replace $\ell_{2,1}$ to $\ell_1$, which would be much easier.

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{anomalous_clusters.png}
  \caption{An example of anomalous cluster assignments which is retrieved from~\cite{gaoijcai2016robust}}\label{fig:anomalous_cluster}
\end{figure}

\begin{quote}
\begin{small}
  \bibliographystyle{aaai}
  \bibliography{ensemble_clustering}
\end{small}
\end{quote}

\end{document}

### 2016-09-03 ensemble_clustering.tex
beta 1.0 by dxy

@@
 
+\def\bD{{\bf D}}
+\def\bI{{\bf I}}
 \def\bE{{\bf E}}
@@
 \def\calL{{\mathcal{L}}}
+\def\calC{{\mathcal{C}}}
+\def\calS{{\mathcal{S}}}
+\def\calF{{\mathcal{F}}}
 \def\bL{{\bf L}}
@@
 \def\eg{{\emph{e.g.}}}
+\def\zerocolumn{{\bf 0}}
 
@@
 \def\rank{{\text{rank}}}
+\def\Tr{{\text{Tr}}}
 
@@
 \begin{abstract}
-In this paper, we propose an efficient maximum margin matrix factorization algorithm for ensemble clustering.
-Our contributions include i) introduction of an efficient optimization for matrix completion based ensemble clustering methods; ii) an intuitive motivation for a $\ell_{2,1}$ loss.
+We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
+SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability).
+To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion.
+Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101
+%In this paper, we propose an efficient maximum margin matrix factorization algorithm for ensemble clustering.
+%Our contributions include i) introduction of an efficient optimization for matrix completion based ensemble clustering methods; ii) an intuitive motivation for a $\ell_{1,2}$ loss.
+%[Gao] , FM
 \end{abstract}
@@
 
-A single clustering result could be inaccurate, so some researchers study ensemble clustering methods to boost the performance,
-such as the algorithms proposed in~\cite{yiicdm2012robust,gaoijcai2016robust}, to name a few.
+A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}.
+Fusion techniques can be grouped into two types which are early fusion and late fusion, early fusion fusion multiple models in the feature level, late fusion merge the result of each classifier.
 
+In the early fusion, a linear combination or more complex functions,eg.
+3D convolution , of different features is utilized to capture inner correlation bettwen each model, such as \cite{Feichtenhofer2016Convolutional}.
+A more simple but effective method in early fusion is to calculate multiple kernel matrix from different features and then average them together to train a SVM classifier.
+Another fusion technique is late fusion, which train classifiers of seperate features and then fuses the results based on the predicted scores, such as \cite{gehler2009feature} learns a linear combination on decision values of individual features to boost the performance of single model.
+
+Most previous works in late fusion focus on how to learn weights on different models, (disadvantage?)
+
+Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
+
+In this paper, we propose a method for ensemble multiple results from different features.
+As aforementioned, we could use the connection between different classifiers to remove outliers in their results.
+To be noticed, the number of class K in vision recoginition task is a great information to constrain the results and connect each other.
+Suppose we have got an label assigment matrix from each features, and concact them together into L.
+This label matrix L is inaccurate due to (xxxxxx), we could use the prior knowledge to restore L by fixing the outlier in it, formulate as below:
+\begin{align}\label{eq:typical_mc}
+  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
+  \st        ~&~ \rank(\bX) \leq k  ,
+\end{align}
+\noindent
+Considering on column-wise sparsity of X, it's naturally to lear a $\ell_{1,2}$ on loss function.
+(xxxxxxxx)our main contribution can be summarized in three entries:
+\begin{itemize}
+  \item propose an efficient late fusion algorithm.
+  \item a novel sense of $\ell_{1,2}$
+  \item a linear time complexity ALM Optimization
+\end{itemize}
+
+%A single clustering result could be inaccurate, so some researchers study ensemble clustering methods to boost the performance,
+%such as the algorithms proposed in~\cite{yiicdm2012robust,gaoijcai2016robust}, to name a few.
+
+\iffalse
 The key aim of matrix completion based methods is to detect the anomalous clusters (bad partitions/assigments) and reconstruct the real assignments,
@@
 However, the least square loss used in matrix completion is sensitive to the abnormal errors, namely outliers, the not appropriate to capture the anomalous assignments.
-The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{2,1}$ norm on $\bX$, which is as follow
+The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{1,2}$ norm on $\bX$, which is as follow
 \begin{align}\label{eq:mc_l21_gaospaper}
-  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{2,1}   \nonumber \\
+  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{1,2}   \nonumber \\
   \st        ~&~ \rank(\bX) \leq k   ,
@@
 \noindent
-where $|| \bX ||_{2,1} = \sum_{j = 1}^{MK} \sqrt(\sum_{i=1}^{N}) = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
-which would make some columns of $\bX$ as zeros (beware the direction of the computation of the $\ell_{2,1}$ norm, more details in~\cite{nienips2010efficient}).
+where $|| \bX ||_{1,2} = \sum_{j = 1}^{MK} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
+which would make $\bX$ column-wise sparse (beware the direction of the computation of the $\ell_{1,2}$ norm, more details in~\cite{nienips2010efficient}).
 Nevertheless, it does not consider the outliers in their loss function.
-In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{2,1}$ is equivalent to $|| \bX - \bO ||_{2,1}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
-Therefore, we propose to apply $\ell_{2,1}$ to capture the outliers as well as anomalous columns, which can be written as below
-\begin{align}\label{eq:mc_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{2,1}    \nonumber \\
+In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{1,2}$ is equivalent to $|| \bX - \bO ||_{1,2}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
+\fi
+
+\section{Related Work}
+
+Many late fusion alogrithm have been proposed to improve the performance of recognition model.
+\cite{gehler2009feature} learns linear funciont to combine multiple classifiers after training SVM on each features.
+\cite{xuiccv2013feature} introduce thresholding and smooth parameters to joint learn weights for each classifier.
+\cite{Rakotomamonjy2008Simplemkl} apply mkl on feature combination, treat each feature as a diffierent kernel function in SVMs to train a robust fusion classifier, which could select the most important feature.
+\cite{gaoijcai2016robust} propose a Robust Convex Ensemble Clustering method utilize a $\ell_{1,2}$ regularization, it could also be applied into late fusion.
+However, \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl} are variant of MKL, (xxxxx), \cite{gaoijcai2016robust} have a high time complexity.
+
+\section{The Proposed Approach}
+We first elaborate the formulation of our SFEC algorithm.
+Then we show the details about how to use ensemble clustering to fuse multiple classifiers' scores.
+Finally, we introduce a novel optimization for the $\ell_{2,1}$ loss ensemble clustering problem.
+
+\begin{figure}[t]
+\centering\includegraphics[width=3.5in]{resource/framework.pdf}
+\caption{something}\label{fig:framework}
+\end{figure}
+
+\subsection{Problem Formulation}{}
+Suppose there are n testing instances, we denote each instance as a variable $x_i \belong R^d (1<=i<=n)$.
+Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
+f_m(x)$, per classifier will predict a score vector $s_{ij}, 1<=i<=n, 1<=j<=m$，represent the result of j-th classifier on i-th testing instance.
+Our goal is to fusion these score vectors.
+Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance.
+Then using label assigment, we convert multiple P matrixs into a 01 matrix L, see as{\ref{fig:framework}}.
+The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, which can be written as below
+\begin{align}\label{eq:l12e}
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
   \st        ~&~ \rank(\bX) \leq k  .
@@
 \begin{align}\label{eq:mf_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{2,1}    \nonumber \\
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
   \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
@@
 Most existing matrix factorization optimization methods only consider smooth loss functions,
-but the $\ell_{2,1}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
-In this paper, we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
+but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
+we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently desccribed in the following section.
 
-\section{ALM Optimization}
+\subsection{ALM Optimization}
 
 By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:mf_l21}) as below:
+
 \begin{align}\label{eq:mf_l21_constrained}
-  \min_{\bE, \bX} ~&~ || \bE ||_{2,1}   \nonumber \\
+  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}   \nonumber \\
   \st             ~&~ \bE = \bL - \bX   \nonumber \\
@@
 \begin{align}\label{eq:lagrangian_l21}
-  \calL = || \bE ||_{2,1} + \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2   ,
+  \calL = & || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
 \end{align}
@@
 where $\bX = \bU \bV$,
-and $\blambda$ are the Lagrangian multipliers (or dual variables).
+and $\blambda \in \dsR^{MK \times N}$ are the Lagrangian multipliers (or dual variables).
 Then we could update $\bX$ and $\bE$ alternatively.
@@
 \begin{align}\label{eq:problem_X}
-  \min_{\bX} ~&~ \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2  \nonumber  \\
+  \min_{\bX} ~&~ \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
   \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
@@
 \begin{align}\label{eq:problem_X2}
-  \min_{\bX} ~&~ \frac{\mu}{2} \Big( || \bX - \bL + \bE ||_F^2 + \frac{2}{\mu} \blambda^{\top} (\bX - \bL + \bE) + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
+  \min_{\bX} ~&~ \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
              ~&~ - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
@@
 \begin{align}\label{eq:problem_X3}
-  \min_{\bX} ~&~ || \bX - \bL + \bE + \frac{\blambda}{\mu} ||_F^2   \nonumber \\
+  \min_{\bX} ~&~ || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2   \nonumber \\
   \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
@@
   \yanred{
-  \min_{\bE} ~ || \bE ||_{2,1} + \blambda^{\top} (\bX - \bL + \bE) + \frac{\mu}{2} || \bX - \bL + \bE ||_F^2   .
+  \min_{\bE} ~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2   .
   }
@@
 \noindent
-The above problem could be solved by the algorithm proposed in~\cite{nienips2010efficient,yangijcai2011l21}.
-\yanred{Yan Yan: I am working on this optimization algorithm.}
+Similarly, we could reformulate the above problem as below:
+\begin{align}\label{eq:problem_E2}
+  \min_{\bE} & \frac{2}{\mu} || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2    .
+\end{align}
+\noindent
+Let $\bY = \bL - \bX + \frac{\blambda}{\mu}$.
+The above problem can be efficiently solved by the following column-wise soft-thresholding operator:
+\begin{align}\label{eq:column_wise_soft_thresholding}
+  \bE_{i} = \calS_{\alpha}(\bY_{i}) = \left\{
+    \begin{aligned}
+      & \zerocolumn,~\text{if}~ ||\bY_{i}||_2 \leq \alpha   \\
+      & \bY_{i} - \frac{\alpha \bY_{i}}{|| \bY_{i} ||_2},~\text{otherwise,}
+    \end{aligned}
+    \right.
+\end{align}
+\noindent
+where $\bE_{i}$ and $\bY_{i}$ denote the $i$-th column of $\bE$ and $\bY$,
+and $\alpha = \frac{2}{\mu}$.
 
+We summarize the proposed algorithm for Problem~(\ref{eq:mf_l21_constrained}) in Algorithm~\
+\begin{algorithm}[h!]
+\begin{algorithmic}
+\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(t)} = 0$, and $\mu^{(t)} > 0$.
+
+\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:problem_X3}) via LRGeomCG.
+
+\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
+
+\STATE 2: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
+
+\STATE 3: $\mu^{(t+1)} = \rho \mu^{(t)}$.
+
+\STATE 4: t = t + 1.
+
+\STATE 5: Go to step 1 until convergence.
+
+\end{algorithmic}
+\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})} \label{Alg:overview_alm}
+\end{algorithm}
+
+\subsection{Final Post Process}
+As we recover the low rank matrix X from the label assisnment matrix L.
+Intuitively, there is two possible way to get our final fusion results from X.
+Although L is a 01 matrix obtain by hard label, we could treat it as a soft score matrix, which the position of highest score represent the most possible label predicted by classifiers.
+X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L.
+And two possible post way to processing X is applied.
+(1)average the score matrixs, each is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X.
+Then we got $X^*$, a N*K score matrix.
+we make the position of the highest value in each rows as the predicted label of the i-th instance.(2)seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum.
+For each matrix $Y_j$, we obtain a column vector by selecting the index of the highest score in each row.
+Then we use voting from M index matrix to select the final label.
+According to the experiments, methods (1) outperform than (2), we choose (1) as our final post process of fusion method.
+
+\iffalse
 \section{An Option on Loss Function: Max Margin}
@@
 \yanred{Note: we may leave this extension as a journal?}
+\fi
 
-\section{Another Option on Loss Function: $\ell_{2,1}$ to $\ell_1$ loss}
+%\section{Another Option on Loss Function: $\ell_{1,2}$ to $\ell_1$ loss}
 
-$ell_{2,1}$ loss could be difficult to optimize.
-A simple way is to replace $\ell_{2,1}$ to $\ell_1$, which would be much easier.
+%$\ell_{1,2}$ loss could be difficult to optimize.
+%A simple way is to replace $\ell_{1,2}$ to $\ell_1$, which would be much easier.
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{anomalous_clusters.png}
+  \includegraphics[width=0.49\textwidth]{resource/anomalous_clusters.png}
   \caption{An example of anomalous cluster assignments which is retrieved from~\cite{gaoijcai2016robust}}\label{fig:anomalous_cluster}
 \end{figure}
+
+\section{Experiments}
+We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset\cite{soomro2012ucf101}, Cifar10\cite{krizhevsky2009learning} dataset, PASCAL VOC’07\cite{pascal-voc-2007}, Oxford Flower 17\cite{nilsback2006visual} and Pascal Sentences dataset.
+In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model\cite{he2015deep}, `fc6' layer of AlexNet\cite{krizhevsky2012imagenet} model\cite{alex} and caffenet model (described in caffe model zoo) and Two-Stream Convolutional Networks.
+Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{twostream}(25 volumes for C3D).
+Following the same produce in \cite{tran2015learning} and \cite{simonyan2014two}, the features for the whole video are then calculated by averaging the features across the sampled frames.
+In Cifar10 dataset, features are extracted from `global\_pool' layer of the ResnNt-20,32,44,56,110 models\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164 models\cite{he2016identity}. 
+In all other dataset,features are extracted from `fc6' layer of VGG16,VGG19\cite{chatfield2014return},AlexNet,CaffeNet models, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of ResNet-50,101,152 models.
+To be noted, all our cnn features are extracted using Caffe\cite{jia2014caffe}.
+
+LIBLINEAR\cite{fan2008liblinear} is adopted for our classification toolbox, the confidence scores are generated from the outputs of LIBLINEAR.
+Then we put the confidence scores as the input into our alogrithm.
+
+Five state-of-the-art fusion methods are compared with our proposed alogrithm : (1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers.
+(2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust} (4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
+In this method, the result scores of each classifier are combined by learning thresholding, smoothing parameters and weights.
+(5)LPBoost\cite{gehler2009feature}.
+In this method, a variant linear combination are applied to multiple classifiers.
+
+The parameter $\mu$ are selected from {0.1, 1, 5, 10}, $\rho$ are select from {1.01, 1.05, 1.1} in all our experiments. For SVM, we use the default parameters set in the LIBLINEAR.
+
+\subsection{Synthetic Experiments}
+
+In synthetic experiments, we set N = 320, M = 15, K = 20, randomly generate N instances with K kinds of labels.
+We randomly change 30% instances' labels, repeat M times to get M classifiers results.
+By appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure \ref{fig:ensemble_cluster}.
+
+\iffalse
+\begin{figure}[htp]
+\center
+    \subfigure[{Ground Truth}]{
+    \begin{minipage}[t]{0.5\linewidth}
+    \centering
+    \label{subfig:gt_pdf}
+    \includegraphics[width=2.2in]{resource/ground_truth.pdf}
+    \end{minipage}
+
+    }
+
+    \subfigure[{\%30 Random Noise}]{
+    \begin{minipage}[t]{0.5\linewidth}
+    \centering
+    \label{subfig:er_pdf}
+    \includegraphics[width=2.2in]{resource/random_error.pdf}
+    \end{minipage}
+    }
+
+    \subfigure[{Recovered Results}]{
+    \begin{minipage}[t]{0.33\linewidth}
+    \centering
+    \label{subfig:re_pdf}
+    \includegraphics[width=1in]{resource/recover.pdf}
+    \end{minipage}
+    }
+    \caption{visualized results of the synthetic dataset} \label{fig:ensemble_cluster}
+\end{figure}
+
+%We perform two experiments to show the effectiveness of the proposed outlier label pruning method.
+%The first experiment is image classification with multiple features.
+%The second experiment is ensemble classification.
+%By these two experiments, we aim to demonstrate that our method is able to effectively remove the anomalous labels from the class indicator matrix, and thus improve the fusion performance of classification.
+We have the following datasets:
+\begin{itemize}
+  \item Oxford flower 17
+  \item Pascal Sentences
+  \item Wikipedia
+  \item mnist
+  \item CIFAR10
+  \item Imagenet
+\end{itemize}
+We compare our proposed method with the following five baselines:
+\begin{itemize}
+  \item Score average
+  \item MKL of multiple features (or base learners)
+  \item LPBoost
+  \item The method proposed in~\cite{gaoijcai2016robust}
+  \item the method proposed in~\cite{xuiccv2013feature}
+\end{itemize}
+
+\fi
+
+\subsection{Experiment on UCF 101 dataset}
+For action recognition, we present our results on UCF 101 dataset\cite{soomro2012ucf101}.
+UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
+We use the official split1 described in \cite{soomro2012ucf101}, which have 9573 training videos 3783 testing videos.
+As mentioned above, fives features are provided from the state of the art deep convolution networks, 4096 demitions features in `fc6' layer from C3D, 1028 demitions features in `pool5/7x7\_s1' layer from  GoogleNet, 2048 demitions features in `pool5' layer of ResNet-152, 4096 demitions features in `fc6' layer in Spatial and Temporal Net.
+All models used in UCF-101 are published by their authors.
+
+We use liblinear to train seperate classifiers on each features with the default parameters in liblinear.
+By appling trained classifiers on test data, we can obtain 5 * 20 confidence score for each video.
+After emsenable fusion, we choose the class with highest confidence score as our predicted class.
+Results are shown in \ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare several fusion method.
+
+\begin{table}[h]\small
+\centering
+\label{table:ucf101}
+\begin{tabular}{c|c}
+\hline
+Method & Mean Accuracy(\%) \\\hline
+SVM on Temporal Net Features & 86.2\% \\\hline
+ASF &  86.8\% \\
+MKL &  000 \\
+RCEC &  000 \\
+FWOT &  000 \\
+LPBoost &  000 \\\hline
+Ours &  000 \\
+\hline
+\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
+\end{tabular}
+\end{table}
+
+\subsection{Experiment on PASCAL VOC 2007 dataset}
+PASCAL VOC 2007 is a dataset for object detection and image classification.
+For our experiment we only use the image level annotation information.
+Since each image may contain more than one label, we filter the multilabel images.
+Using the offical split provided by \cite{pascal-voc-2007}, we have 2954 trainval images and 3192 test images with 20 classes after filtration.
+We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features.
+
+After the procesure of classification and fusion, we got the results as \ref{table:voc}.
+Since in PASCAL VOC 2007 dataset, more classifiers are utilized than UCF101, it's clear that our method achieve significant improvement than single model and a slight improvement than other fusion algorithm.
+
+\begin{table}[t]\small
+\centering
+\caption{Statistics of the Real-world data sets.}
+\label{table:voc}
+\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c}
+\hline
+Method & aeroplane & bicycle & bird & boat & bottle & bus & car & cat & chair & cow & diningtable & dog & horse & motorbike & person & pottedplant & sheep & sofa & train & tvmonitor & Mean Accuracy(\%) \\\hline
+Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\%\\\hline
+ASF & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\% \\
+MKL & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 00 \\
+RCEC & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+FWOT & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+LPBoost & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\\hline
+Ours & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Experiment on Cifar10 dataset}
+In CIFAR-10 dataset, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
+There are 50000 training data and 10000 testing data.
+We extract 14 CNN features from multiple state of the art models (eg.
+ResNet20,32,44,56,110,164).
+large scale ability...(how to say).
+
+Fourteen linear SVM model are trained on each features, then our fusion method are applied to the predicted scores of test images. Results are shown on \ref{table:cifar10}
+
+\begin{table}[h]\small
+\centering
+\caption{Statistics of the Real-world data sets.}
+\label{table:cifar10}
+\begin{tabular}{c|c|c|c}
+\hline
+Method & Mean Accuracy(\%) & Classification Time & Fusion Time\\\hline
+ASF &  86.8\% & 0 & 0 \\
+MKL &  000 & 0 & 0 \\
+RCEC &  000 & 0 & 0 \\
+FWOT &  000 & 0 & 0 \\
+LPBoost & 000 & 0 & 0 \\\hline
+Ours &  000 & 0 & 0 \\
+\hline
+\end{tabular}
+\end{table}
 

### 2016-09-04 ensemble_clustering.tex
revise abs

@@
 \begin{abstract}
-We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
+% First: A big picture of the scenario which we would consider
+In many real world applications, data can be represented in multiple ways/features, which would describe various characteristics of data.
+Many works have shown that it could often improve the performance to make use of these features together.
+% Second: what BIG problem would we like to solve?
+Late fusion, which combines the predictions of multiple features, is a commonly used approach to generate the final decision for a test instance.
+% Third: specify the detailed problem: find a precise position for our paper
+However, it is ubiquitous that different features would dispute on some data, leading to the requirement of outlier rejection for late fusion algorithms.
+% Fourth: general introduction of our method
+In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources, which could
+relieve the performance degeneration caused by the controversy of multiple features on test data.
+% Some unvalued sentence(s)
+Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.
+% Written by DXY:
+%We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
 SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability).
@@
 Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101
-%In this paper, we propose an efficient maximum margin matrix factorization algorithm for ensemble clustering.
-%Our contributions include i) introduction of an efficient optimization for matrix completion based ensemble clustering methods; ii) an intuitive motivation for a $\ell_{1,2}$ loss.
-%[Gao] , FM
 \end{abstract}
@@
 \subsection{Problem Formulation}{}
-Suppose there are n testing instances, we denote each instance as a variable $x_i \belong R^d (1<=i<=n)$.
+Suppose there are n testing instances, we denote each instance as a variable $x_i \in \dsR^d (1<=i<=n)$.
 Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
@@
 \hline
+\end{tabular}
 \caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
-\end{tabular}
 \end{table}

### 2016-09-05 ensemble_clustering.tex
beta 1.0 for Abstract and Introduction, Update

@@
 
-\title{Maximum Margin Matrix Factorization for Ensemble Clustering}
+\title{Outlier Reject for Late Fusion on Visual Recognition}
+\author{Yan Yan$^1$, Yi Yang$^1$\\
+$^1$Centre for Quantum Computation and Intelligent Systems, University of Technology, Sydney, Australia\\
+yan.yan-3@student.uts.edu.au,yee.i.yang@gmail.com}
 
@@
 
-A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}.
+%背景 多model融合
+Image or video data in the real world can be represented in multiple features, such as motion features of videos (eg.Dense Trajectories\cite{Wang2011Action}), shape features of frames (eg.
+Histograms of Oriented Gradients\cite{dalal2005histograms}, SIFT\cite{lowe2004distinctive}), or some complex CNN features for both frames and sequences(eg.\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}).
+Each of these features contain rich information of data, which can not capture all views of our data.
+A single classifier model will bias on some characteristics of training data based on different features.
+Combine multiple features together and capture more views on data can significantly improve the performance.
+
+%%A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}.
 Fusion techniques can be grouped into two types which are early fusion and late fusion, early fusion fusion multiple models in the feature level, late fusion merge the result of each classifier.
 
-In the early fusion, a linear combination or more complex functions,eg.
+%% late fusion is a common sigle model -> single feature, 介绍late fusion
+Late fusion is a common method to make the combination of different features.
+Single model is firstly trained on different features using SVM or other classifiers, then late fusion method combine the predicted decision results of each single model to decide the final result.
+A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.Multiple Kernel Learning\cite{Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm(eg.
+\cite{gehler2009feature,xuiccv2013feature,lai2015learning}).
+The alogrithms proposed in ensemble clustering problem might also be used for late fusion, which are capable to find the anomalous results among multiple classifers(eg.\cite{gaoijcai2016robust}).
+\yanred{Robust Principal Component Analysis xxxxx}.
+
+%%In the early fusion, a linear combination or more complex functions,eg.
 3D convolution , of different features is utilized to capture inner correlation bettwen each model, such as \cite{Feichtenhofer2016Convolutional}.
-A more simple but effective method in early fusion is to calculate multiple kernel matrix from different features and then average them together to train a SVM classifier.
-Another fusion technique is late fusion, which train classifiers of seperate features and then fuses the results based on the predicted scores, such as \cite{gehler2009feature} learns a linear combination on decision values of individual features to boost the performance of single model.
+A more simple but effective method in early fusion is to calculate multiple kernel matrix from different features and then average them together to train a SVM classifier.Another fusion technique is late fusion, which train classifiers of seperate features and then fuses the results based on the predicted scores, such as \cite{gehler2009feature} learns a linear combination on decision values of individual features to boost the performance of single model.
+%%Most previous works in late fusion focus on how to learn weights on different models, (disadvantage?)
 
-Most previous works in late fusion focus on how to learn weights on different models, (disadvantage?)
+%% 不同的features 会有意见不同的时候，具体 outlier rejection，might [Gao low rank sparse loss, but the nuclear norm 
+%% scale poorly , expensive single vd(SVDs) present of , the other way of low MF foucs on least square smooth function
+%% least square loss is sensitive to outlier
+%% it's unclear to extend MF to nonsmooth function .
+%% In this paper we proposed a 
+%%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
+It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem.
+There are some researchers have ability to reject the outlier of multiple results, such as \cite{gaoijcai2016robust} use low rank sparse $\ell_{1,2}$ loss and nuclear norm to solve, which are poorly to extend to large scale data due to the expensive cost of Singular Value Decomposition(SVDs) present in the alogrithm.
+The other research on matrix factorization foucs on least square smooth loss funcion, which is sensitive to outlier and it's unclear to extend matrix factorization to nonsmooth $\ell_{1,2}$ loss.
 
-Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
-
-In this paper, we propose a method for ensemble multiple results from different features.
+In this paper, we introduce an efficient matrix factorization based alogrithm to do late fuse for multiple predictions of vision recoginition, named Outlier Rejection for Late Fusion(ORLF).
+We utilize the robust $\ell_{1,2}$ nonsmooth loss fuction \ref{eq:typical_mc} to reject the outlier results from different classifiers.
+The low rank constrain is the number of classes in vision recoginition task.
+%%%In this paper, we propose a method for ensemble multiple results from different features.
 As aforementioned, we could use the connection between different classifiers to remove outliers in their results.
@@
 \noindent
-Considering on column-wise sparsity of X, it's naturally to lear a $\ell_{1,2}$ on loss function.
-(xxxxxxxx)our main contribution can be summarized in three entries:
+Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
+For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as \ref{eq:mc_l21}
+\begin{align}\label{eq:mf_l21}
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
+  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
+\end{align}
+\noindent
+Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mc_l21} is nonsmooth.
+In this paper, we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
+
+Our main contribution can be summarized in three entries:
 \begin{itemize}
-  \item propose an efficient late fusion algorithm.
-  \item a novel sense of $\ell_{1,2}$
-  \item a linear time complexity ALM Optimization
+  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
+  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
+  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
 \end{itemize}
@@
 \section{Related Work}
-
+%% RPCA robust 
+%% Matrix F...
+%% 
 Many late fusion alogrithm have been proposed to improve the performance of recognition model.
@@
 
+%% Latent Fusion
+
 \section{The Proposed Approach}
@@
 \begin{figure}[t]
-\centering\includegraphics[width=3.5in]{resource/framework.pdf}
+\centering\includegraphics[width=0.45\textwidth]{resource/framework.pdf}
 \caption{something}\label{fig:framework}
@@
 
-\subsection{Problem Formulation}{}
-Suppose there are n testing instances, we denote each instance as a variable $x_i \in \dsR^d (1<=i<=n)$.
+\subsection{Problem Formulation}
+Suppose there are n testing instances, we denote each instance as a variable $x_i \in \dsR^d (1{\leq}i{\leq}n)$.
 Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
-f_m(x)$, per classifier will predict a score vector $s_{ij}, 1<=i<=n, 1<=j<=m$，represent the result of j-th classifier on i-th testing instance.
+f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m$，represent the result of j-th classifier on i-th testing instance.
 Our goal is to fusion these score vectors.
@@
 The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, which can be written as below
-\begin{align}\label{eq:l12e}
+\begin{align}\label{eq:mc_l21}
   \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{resource/anomalous_clusters.png}
+  \includegraphics[width=0.45\textwidth]{resource/anomalous_clusters.png}
   \caption{An example of anomalous cluster assignments which is retrieved from~\cite{gaoijcai2016robust}}\label{fig:anomalous_cluster}
@@
 We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset\cite{soomro2012ucf101}, Cifar10\cite{krizhevsky2009learning} dataset, PASCAL VOC’07\cite{pascal-voc-2007}, Oxford Flower 17\cite{nilsback2006visual} and Pascal Sentences dataset.
-In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model\cite{he2015deep}, `fc6' layer of AlexNet\cite{krizhevsky2012imagenet} model\cite{alex} and caffenet model (described in caffe model zoo) and Two-Stream Convolutional Networks.
-Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{twostream}(25 volumes for C3D).
+In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model\cite{he2015deep}, `fc6' layer of AlexNet\cite{krizhevsky2012imagenet} model\cite{krizhevsky2012imagenet} and caffenet model (described in caffe model zoo) and Two-Stream Convolutional Networks.
+Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{simonyan2014two} volumes for C3D).
 Following the same produce in \cite{tran2015learning} and \cite{simonyan2014two}, the features for the whole video are then calculated by averaging the features across the sampled frames.
@@
 
-\iffalse
 \begin{figure}[htp]
 \center
-    \subfigure[{Ground Truth}]{
-    \begin{minipage}[t]{0.5\linewidth}
-    \centering
+    \subfigure[Ground Truth]{
     \label{subfig:gt_pdf}
-    \includegraphics[width=2.2in]{resource/ground_truth.pdf}
-    \end{minipage}
-
+    \includegraphics[width=0.14\textwidth]{resource/ground_truth.eps}
     }
-
-    \subfigure[{\%30 Random Noise}]{
-    \begin{minipage}[t]{0.5\linewidth}
-    \centering
+    \subfigure[Random Noise]{
     \label{subfig:er_pdf}
-    \includegraphics[width=2.2in]{resource/random_error.pdf}
-    \end{minipage}
+    \includegraphics[width=0.14\textwidth]{resource/random_error.eps}
     }
-
-    \subfigure[{Recovered Results}]{
-    \begin{minipage}[t]{0.33\linewidth}
-    \centering
+    \subfigure[Outlier Reject]{
     \label{subfig:re_pdf}
-    \includegraphics[width=1in]{resource/recover.pdf}
-    \end{minipage}
+    \includegraphics[width=0.14\textwidth]{resource/recover.eps}
     }
@@
 
+\iffalse
 %We perform two experiments to show the effectiveness of the proposed outlier label pruning method.
@@
 
+\begin{table*}[t]\scriptsize
+\centering
+\label{table:voc}
+\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c}
+\hline
+Method & Mean Accuracy & aeroplane & bicycle & bird & boat & bottle & bus & car & cat & chair & cow \\\hline
+       &   & diningtable & dog & horse & motorbike & person & pottedplant & sheep & sofa & train & tvmonitor \\\hline
+Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\hline
+ASF     & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\% \\
+MKL     & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 00 \\
+RCEC    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+FWOT    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+LPBoost & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\\hline
+Ours    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
+\hline
+\end{tabular}
+\caption{Statistics of the Real-world data sets.}
+\end{table*}
+
 \subsection{Experiment on PASCAL VOC 2007 dataset}
@@
 
-\begin{table}[t]\small
-\centering
-\caption{Statistics of the Real-world data sets.}
-\label{table:voc}
-\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c}
-\hline
-Method & aeroplane & bicycle & bird & boat & bottle & bus & car & cat & chair & cow & diningtable & dog & horse & motorbike & person & pottedplant & sheep & sofa & train & tvmonitor & Mean Accuracy(\%) \\\hline
-Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\%\\\hline
-ASF & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\% \\
-MKL & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 00 \\
-RCEC & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-FWOT & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-LPBoost & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\\hline
-Ours & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-\hline
-\end{tabular}
-\end{table}
-
 \subsection{Experiment on Cifar10 dataset}
@@
 
-\begin{table}[h]\small
+\begin{table}[h]\scriptsize
 \centering
-\caption{Statistics of the Real-world data sets.}
 \label{table:cifar10}
@@
 \end{tabular}
+\caption{Accuracy and Time cost on cifar10 dataset}
 \end{table}

### 2016-09-06 ensemble_clustering.tex
beta 2.0 for Introduction and Related Work, Update

@@
 \usepackage{color}
+\usepackage{epstopdf}
 \usepackage{bm}
@@
 \title{Outlier Reject for Late Fusion on Visual Recognition}
-\author{Yan Yan$^1$, Yi Yang$^1$\\
-$^1$Centre for Quantum Computation and Intelligent Systems, University of Technology, Sydney, Australia\\
-yan.yan-3@student.uts.edu.au,yee.i.yang@gmail.com}
 
@@
 %背景 多model融合
-Image or video data in the real world can be represented in multiple features, such as motion features of videos (eg.Dense Trajectories\cite{Wang2011Action}), shape features of frames (eg.
-Histograms of Oriented Gradients\cite{dalal2005histograms}, SIFT\cite{lowe2004distinctive}), or some complex CNN features for both frames and sequences(eg.\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}).
-Each of these features contain rich information of data, which can not capture all views of our data.
+Image or video data in the real world can be represented in multiple features.
+For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}, shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
+Each feature contains rich information of real data, which can not capture all views of our data.
 A single classifier model will bias on some characteristics of training data based on different features.
-Combine multiple features together and capture more views on data can significantly improve the performance.
+It can significantly improve the performance by combining multiple features together and capturing more views on data.
 
@@
 Late fusion is a common method to make the combination of different features.
-Single model is firstly trained on different features using SVM or other classifiers, then late fusion method combine the predicted decision results of each single model to decide the final result.
-A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.Multiple Kernel Learning\cite{Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm(eg.
-\cite{gehler2009feature,xuiccv2013feature,lai2015learning}).
-The alogrithms proposed in ensemble clustering problem might also be used for late fusion, which are capable to find the anomalous results among multiple classifers(eg.\cite{gaoijcai2016robust}).
-\yanred{Robust Principal Component Analysis xxxxx}.
+Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
+A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
+Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
+\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
+}
+%%这提了Gao，下一段也提了Gao这样好么？
 
@@
 
-In this paper, we introduce an efficient matrix factorization based alogrithm to do late fuse for multiple predictions of vision recoginition, named Outlier Rejection for Late Fusion(ORLF).
-We utilize the robust $\ell_{1,2}$ nonsmooth loss fuction \ref{eq:typical_mc} to reject the outlier results from different classifiers.
-The low rank constrain is the number of classes in vision recoginition task.
-%%%In this paper, we propose a method for ensemble multiple results from different features.
-As aforementioned, we could use the connection between different classifiers to remove outliers in their results.
-To be noticed, the number of class K in vision recoginition task is a great information to constrain the results and connect each other.
-Suppose we have got an label assigment matrix from each features, and concact them together into L.
-This label matrix L is inaccurate due to (xxxxxx), we could use the prior knowledge to restore L by fixing the outlier in it, formulate as below:
+In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
+We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers.
+We introduce the low rank constraint to maintain the consistency among differernt classifers.
+The formulation can be written as bellow:
+
 \begin{align}\label{eq:typical_mc}
@@
 \noindent
+
+L a is observed matrix, represent the label indicator matrix in our vision recoginition case.
+X is a low rank matrix recovered from L.
+Rank function measures the rank of a matrix.
+$|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
 Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
-For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as \ref{eq:mc_l21}
+For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
 \begin{align}\label{eq:mf_l21}
@@
 \noindent
-Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mc_l21} is nonsmooth.
-In this paper, we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
+Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth.
+In our proposed method(ORLF), we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
 
-Our main contribution can be summarized in three entries:
+Our main contribution can be summarized as below:
 \begin{itemize}
@@
 %% 
-Many late fusion alogrithm have been proposed to improve the performance of recognition model.
-\cite{gehler2009feature} learns linear funciont to combine multiple classifiers after training SVM on each features.
-\cite{xuiccv2013feature} introduce thresholding and smooth parameters to joint learn weights for each classifier.
-\cite{Rakotomamonjy2008Simplemkl} apply mkl on feature combination, treat each feature as a diffierent kernel function in SVMs to train a robust fusion classifier, which could select the most important feature.
-\cite{gaoijcai2016robust} propose a Robust Convex Ensemble Clustering method utilize a $\ell_{1,2}$ regularization, it could also be applied into late fusion.
-However, \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl} are variant of MKL, (xxxxx), \cite{gaoijcai2016robust} have a high time complexity.
+\yanred{MF method}
 
-%% Latent Fusion
+%%RPCA Methods
+Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix.
+This could also be used in our late fusion application to remove outlier column in the indicator matrix L.
+\cite{wright2009robust} instroduce a representative Robust PCA algorithm, and \cite{ye2012robust} propose a rank minimization method optimize the RPCA to fuse the predicted confidence scores of multiple models.
+\yanred{other RPCA and disadvantage}
+
+MKL~\cite{Rakotomamonjy2008Simplemkl} based method is a simple but efficient way to combine different features for late fusion.
+\cite{vedaldi2009multiple} use MKL to learn an optimal combination of exponential ${\chi}^2$.
+\cite{gehler2009feature} introduce two boosting approaches inspired by the MKL.
+\cite{natarajan2012multimodal} combines these diverse features using a two-step strategy employing MKL and late score fusion methods.
+\cite{lai2015learning} proposed a late fusion method that determines the optimal fusion weights for each sample.
+\yanred{\cite{xuiccv2013feature} learns the weights, thresholding and smoothing parameters in a joint framework to combine the decision values.
+Copy from Abs}.
+\yanred{However, MKL based method...}
+
+%% Latent Fusion,
 
 \section{The Proposed Approach}
-We first elaborate the formulation of our SFEC algorithm.
-Then we show the details about how to use ensemble clustering to fuse multiple classifiers' scores.
-Finally, we introduce a novel optimization for the $\ell_{2,1}$ loss ensemble clustering problem.
+We first elaborate the formulation of our ORLF algorithm.
+Then we show the details about how to use augmented Lagrangian multiplier (ALM) to solve the $\ell_{1,2}$ objective function.
+Finnaly we introduce our post process strategy to convert the recovered matrix X in \ref{eq:mf_l21} to the final predicted label.
 
-\begin{figure}[t]
-\centering\includegraphics[width=0.45\textwidth]{resource/framework.pdf}
+\subsection{Problem Formulation}
+Suppose there are n testing instances, we denote each instance as a variable $x_i{\in}\dsR^{d}(1{\leq}i{\leq}n)$.
+Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
+f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m $，represent the result of j-th classifier on i-th testing instance.
+Our goal is to fusion these predicted confidence score vectors.
+Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance.
+Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
+The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown in \ref{eq:mf_l21}.
+The k of the low rank constraint in (\ref{eq:mf_l21}) is the number of class in recoginition task.
+
+\begin{figure}[h]
+\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
 \caption{something}\label{fig:framework}
@@
 
-\subsection{Problem Formulation}
-Suppose there are n testing instances, we denote each instance as a variable $x_i \in \dsR^d (1{\leq}i{\leq}n)$.
-Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
-f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m$，represent the result of j-th classifier on i-th testing instance.
-Our goal is to fusion these score vectors.
-Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance.
-Then using label assigment, we convert multiple P matrixs into a 01 matrix L, see as{\ref{fig:framework}}.
-The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, which can be written as below
-\begin{align}\label{eq:mc_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k  .
-\end{align}
-Problem~(\ref{eq:mc_l21}) is NP-hard due to the presence of the low rank constraint.
-For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as
-\begin{align}\label{eq:mf_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
-\end{align}
-\noindent
-Note that we have totally $K$ single clustering assignments.
-Intuitively, we could set $k = K$ in Problem~(\ref{eq:mf_l21}).
-Most existing matrix factorization optimization methods only consider smooth loss functions,
-but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
-we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently desccribed in the following section.
-
 \subsection{ALM Optimization}
+Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
+We apply ALM to optimize the nonsmooth objective function efficiently, desccribed as bellow:
 
@@
 X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L.
-And two possible post way to processing X is applied.
-(1)average the score matrixs, each is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X.
+Two possible post way to processing X are described as bellow:
+\begin{itemize}
+  \item Average the score matrixs, each of which is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X.
 Then we got $X^*$, a N*K score matrix.
-we make the position of the highest value in each rows as the predicted label of the i-th instance.(2)seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum.
+we make the position of the highest value in each rows as the predicted label of the i-th instance.
+  \item Seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum.
 For each matrix $Y_j$, we obtain a column vector by selecting the index of the highest score in each row.
 Then we use voting from M index matrix to select the final label.
-According to the experiments, methods (1) outperform than (2), we choose (1) as our final post process of fusion method.
+\end{itemize}
+According to the experiments, the first strategy outperform than the second one, we choose the first one as our final post process of fusion method.
 
@@
 \section{An Option on Loss Function: Max Margin}
-
 In fact, the assignments $\bL$ contains only $0/1$ values (discrete ordinal values).
@@
 \yanred{Note: we may leave this extension as a journal?}
+
+\section{Another Option on Loss Function: $\ell_{1,2}$ to $\ell_1$ loss}
+$\ell_{1,2}$ loss could be difficult to optimize.
+A simple way is to replace $\ell_{1,2}$ to $\ell_1$, which would be much easier.
 \fi
 
-%\section{Another Option on Loss Function: $\ell_{1,2}$ to $\ell_1$ loss}
-
-%$\ell_{1,2}$ loss could be difficult to optimize.
-%A simple way is to replace $\ell_{1,2}$ to $\ell_1$, which would be much easier.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{resource/anomalous_clusters.png}
-  \caption{An example of anomalous cluster assignments which is retrieved from~\cite{gaoijcai2016robust}}\label{fig:anomalous_cluster}
-\end{figure}
-
 \section{Experiments}
-We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset\cite{soomro2012ucf101}, Cifar10\cite{krizhevsky2009learning} dataset, PASCAL VOC’07\cite{pascal-voc-2007}, Oxford Flower 17\cite{nilsback2006visual} and Pascal Sentences dataset.
-In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model\cite{he2015deep}, `fc6' layer of AlexNet\cite{krizhevsky2012imagenet} model\cite{krizhevsky2012imagenet} and caffenet model (described in caffe model zoo) and Two-Stream Convolutional Networks.
+We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, PASCAL VOC’07~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual} and Pascal Sentences dataset.
+In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model~\cite{he2015deep}, `fc6' layer of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet} and Two-Stream Convolutional Networks~\cite{simonyan2014two}.
 Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{simonyan2014two} volumes for C3D).
@@
 In Cifar10 dataset, features are extracted from `global\_pool' layer of the ResnNt-20,32,44,56,110 models\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164 models\cite{he2016identity}.
-In all other dataset,features are extracted from `fc6' layer of VGG16,VGG19\cite{chatfield2014return},AlexNet,CaffeNet models, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of ResNet-50,101,152 models.
-To be noted, all our cnn features are extracted using Caffe\cite{jia2014caffe}.
+In all other dataset, features are extracted among `fc6' layer of VGG network~\cite{chatfield2014return} and AlexNet network~\cite{krizhevsky2012imagenet}, `pool5/7x7\_s1' layer from GoogleNet network~\cite{szegedy2015going}, `pool5' layer of Residual network~\cite{he2015deep}.
+To be noted, all our cnn features are extracted using Caffe\cite{jia2014caffe}, a deep learning framework.
 
@@
 In synthetic experiments, we set N = 320, M = 15, K = 20, randomly generate N instances with K kinds of labels.
-We randomly change 30% instances' labels, repeat M times to get M classifiers results.
+We randomly change 30\% instances' labels, repeat M times to get M classifiers' results.
 By appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure \ref{fig:ensemble_cluster}.
+Each subfigure contrains $N\times M$ small narrow blocks, which visualized in diverse colors according to their different label.
+The first picture~\ref{subfig:gt_pdf}, show the ground truth and copied M times.
+And M noised classifiers' results are pictured as~\ref{subfig:er_pdf}.
+After we recover the low rank matrix from the noised matrix by using ORLF late fusion method, we visualize it as~\ref{subfig:er_pdf}.
 
@@
 %By these two experiments, we aim to demonstrate that our method is able to effectively remove the anomalous labels from the class indicator matrix, and thus improve the fusion performance of classification.
-We have the following datasets:
-\begin{itemize}
-  \item Oxford flower 17
-  \item Pascal Sentences
-  \item Wikipedia
-  \item mnist
-  \item CIFAR10
-  \item Imagenet
-\end{itemize}
-We compare our proposed method with the following five baselines:
-\begin{itemize}
-  \item Score average
-  \item MKL of multiple features (or base learners)
-  \item LPBoost
-  \item The method proposed in~\cite{gaoijcai2016robust}
-  \item the method proposed in~\cite{xuiccv2013feature}
-\end{itemize}
-
 \fi
@@
 
-\begin{table*}[t]\scriptsize
-\centering
-\label{table:voc}
-\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c}
-\hline
-Method & Mean Accuracy & aeroplane & bicycle & bird & boat & bottle & bus & car & cat & chair & cow \\\hline
-       &   & diningtable & dog & horse & motorbike & person & pottedplant & sheep & sofa & train & tvmonitor \\\hline
-Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
-Best Single Model & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\hline
-ASF     & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 86.8\% \\
-MKL     & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 00 \\
-RCEC    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-FWOT    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-LPBoost & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\\hline
-Ours    & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 000 \\
-\hline
-\end{tabular}
-\caption{Statistics of the Real-world data sets.}
-\end{table*}
-
 \subsection{Experiment on PASCAL VOC 2007 dataset}
@@
 Using the offical split provided by \cite{pascal-voc-2007}, we have 2954 trainval images and 3192 test images with 20 classes after filtration.
-We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features.
+We extract features from AlexNet,VGG,GoogleNet,ResNet, totally seven diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50 and ResNet101).
 
@@
 Since in PASCAL VOC 2007 dataset, more classifiers are utilized than UCF101, it's clear that our method achieve significant improvement than single model and a slight improvement than other fusion algorithm.
+
+\begin{table*}[h]\scriptsize
+\centering
+\label{table:voc}
+\begin{tabular}{c|c|c|c}
+\hline
+Method            & Mean Accuracy & Classification Time(s)& Fusion Time \\\hline
+Best Single Model & 88.44\%       &  2.347                &      0    \\\hline
+ASF               & 88.69\%       &  10.2347              &    0.008   \\ % Average
+MKL               &     0 & 00 & 0 \\
+RCEC              &     0 & 0 & 000 \\
+FWOT              &     0 & 0 & 000 \\
+LPBoost           &     0 & 0 & 000 \\\hline
+Ours              & 88.78\%       & 10.2347               & 9.918 \\
+\hline
+\end{tabular}
+\caption{Statistics of the Real-world data sets.}
+\end{table*}
 
@@
 
+\subsection{Experiment on Oxford Flowers}
+Oxford Flowers 17 dataset~\cite{nilsback2006visual} havs 17 flower categories with 80 images for each class.
+There are three predefined splits training set with 680 images, validation set with 340 images and testing set 340 images.
+2048 dimetions `pool5' features from ResNet-50,101,152 proposed in \cite{he2015deep} and 4096 dimetions `fc6' features from CaffeNet,AlexNet proposed in \cite{krizhevsky2012imagenet} are used for linear SVM.
+The models are download from Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}, with no finetuning on the current dataset.
+
+We use the predefined training set and validation set as our training data, trained on liblinear with default parameters.
+Results are shown in \ref{table:flower17}
+
+\begin{table}[h]\scriptsize
+\centering
+\label{table:flower17}
+\begin{tabular}{c|c|c|c}
+\hline
+Method & Split 1 & Split 2 & Split 3\\\hline
+ASF &  97.94\% & 0 & 0 \\
+MKL &  000 & 0 & 0 \\
+RCEC &  000 & 0 & 0 \\
+FWOT &  000 & 0 & 0 \\
+LPBoost & 000 & 0 & 0 \\\hline
+Ours &  98.24\% & 0 & 0 \\
+\hline
+\end{tabular}
+\caption{Accuracy on Three Official Split}
+\end{table}
+
 \begin{quote}

### 2016-09-07 ensemble_clustering.tex
Experiment on Cifar10, OK

@@
 Five state-of-the-art fusion methods are compared with our proposed alogrithm : (1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers.
+We use $L_2$ norm on each classifiers for normalization.
 (2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/} ; \url{https://github.com/minghen/liblinear-mkl}} to train out MKL model.
 (3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust} (4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
-In this method, the result scores of each classifier are combined by learning thresholding, smoothing parameters and weights.
+The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
 (5)LPBoost\cite{gehler2009feature}.
@@
 
-\begin{table*}[h]\scriptsize
+\begin{table}[!h]\scriptsize
 \centering
@@
 \end{tabular}
-\caption{Statistics of the Real-world data sets.}
-\end{table*}
+\caption{Accuracy and Time cost on VOC2007 dataset}
+\end{table}
 
@@
 There are 50000 training data and 10000 testing data.
-We extract 14 CNN features from multiple state of the art models (eg.
-ResNet20,32,44,56,110,164).
-large scale ability...(how to say).
+Fourteen CNN features are extracted from multiple state of the art models for training svm.
+These features are `global\_pool' layers' features of ResNet-20,32,44,56,110~\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164~\cite{he2016identity},  `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}} and `global\_pool' layers' features from two modified network from~\cite{szegedy2015going,chatfield2014return}.
+This experiments show the ability of our ORLF to handle large scale data.\yanred{(how to say)}
 
-Fourteen linear SVM model are trained on each features, then our fusion method are applied to the predicted scores of test images. Results are shown on \ref{table:cifar10}
+As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day) and LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train.
+We use `-s 2' parameters in liblinear to speedup training training process.
+Results of other contrast algorithms are shown on \ref{table:cifar10}
 
@@
 \label{table:cifar10}
-\begin{tabular}{c|c|c|c}
+\begin{tabular}{c|c|c}
 \hline
-Method & Mean Accuracy(\%) & Classification Time & Fusion Time\\\hline
-ASF &  86.8\% & 0 & 0 \\
-MKL &  000 & 0 & 0 \\
-RCEC &  000 & 0 & 0 \\
-FWOT &  000 & 0 & 0 \\
-LPBoost & 000 & 0 & 0 \\\hline
-Ours &  000 & 0 & 0 \\
+Method & Mean Accuracy(\%) & Classification Time + Fusion Time(s)\\\hline
+ASF &  94.21\% & 55.6 + 0.02 \\
+MKL &  94.15\% & 865.09 \\
+RCEC &  94.87\% & 55.6 + 3.5 \\
+FWOT &  - & - \\
+LPBoost & - & - \\\hline
+Ours &  95.05\% & 55.6 + 32.1 \\
 \hline
@@
 We use the predefined training set and validation set as our training data, trained on liblinear with default parameters.
+For LPBoost Methods, we use 5 fold cross validation to select the best hyperparmeter $\nu$.
 Results are shown in \ref{table:flower17}
@@
 FWOT &  000 & 0 & 0 \\
-LPBoost & 000 & 0 & 0 \\\hline
+LPBoost & 97.94\% & 0 & 0 \\\hline
 Ours &  98.24\% & 0 & 0 \\

### 2016-09-08 ensemble_clustering.tex
Update Experiment on UCF101

@@
 Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.
-% Written by DXY:
-%We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
+
+%% Written by DXY:
+%%% We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
 SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability).
 To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion.
-Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101
+Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101.
 \end{abstract}
@@
 Results are shown in \ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare several fusion method.
+To be noted, FWOT~\cite{xuiccv2013feature} is too slow to train, we didn't show it's result (more than one day).
 
@@
 Method                       & Mean Accuracy(\%) \\\hline
-SVM on Temporal Net Features & 86.2\% \\\hline
-ASF &  86.8\% \\
-MKL &  000 \\
-RCEC &  000 \\
-FWOT &  000 \\
-LPBoost &  000 \\\hline
-Ours &  000 \\
+SVM on Temporal Net Features & 86.23\%            \\\hline
+ASF                          & 86.78\%           \\
+MKL                          & 85.38\%           \\
+RCEC                         & 88.29\%           \\
+FWOT                         & -                 \\
+LPBoost                      & 86.24\%           \\\hline
+Ours                         & 88.89\%           \\
 \hline
@@
 \subsection{Experiment on Cifar10 dataset}
-In CIFAR-10 dataset, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
+In CIFAR-10 dataset~\cite{krizhevsky2009learning}, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
 There are 50000 training data and 10000 testing data.
@@
 
-As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day) and LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train.
-We use `-s 2' parameters in liblinear to speedup training training process.
+As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day).
+LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
+the use `-s 2' parameters in liblinear to speedup training training process.
 Results of other contrast algorithms are shown on \ref{table:cifar10}
@@
 FWOT    & -                 & -                                   \\
-LPBoost & - & - \\\hline
+LPBoost & 94.88\%           & 54.99                               \\\hline
 Ours    & 95.05\%           & 55.6 + 32.1                         \\

### 2016-09-08 ensemble_clustering.tex
Update Experiment Oxford Pet

@@
 \usepackage{courier}
+
+\def\grad{\mbox{\text{\textbf{grad}}}}
+\def\bzero{{\bf{0}}}
 
@@
 Image or video data in the real world can be represented in multiple features.
-For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}, shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
+For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
+Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
 Each feature contains rich information of real data, which can not capture all views of our data.
@@
 
-We summarize the proposed algorithm for Problem~(\ref{eq:mf_l21_constrained}) in Algorithm~\
+We summarize the proposed algorithm for Problem~(\ref{eq:mf_l21_constrained}) in Algorithm~\ref{alg:alm_mf}.
 \begin{algorithm}[h!]
@@
 \STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(t)} = 0$, and $\mu^{(t)} > 0$.
+
+\WHILE{not converge}
+
+  \WHILE{not converge}
 
@@
 
-\STATE 2: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
+  \ENDWHILE
 
-\STATE 3: $\mu^{(t+1)} = \rho \mu^{(t)}$.
+  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
 
-\STATE 4: t = t + 1.
+  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
 
-\STATE 5: Go to step 1 until convergence.
+  \STATE 5: t = t + 1.
+
+\ENDWHILE
 
 \end{algorithmic}
-\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})} \label{Alg:overview_alm}
+\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
+\label{alg:alm_mf}
 \end{algorithm}
 
+\begin{theorem}\label{theorem:alm_convergence}
+  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
+\end{theorem}
+
+\begin{proof}
+    Considering the $(k+1)$-th iteration of Algorithm~\ref{alg:alm_mf}, we have the following development:
+    \begin{align}\label{eq:proof1}
+      & \calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k})   \nonumber \\ 
+      & = || \bE_{k+1} ||_{1,2} + \langle \blambda_{k}, \bL - \bX_{k+1} - \bE_{k+1} \rangle + \frac{\mu}{2} || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2         \nonumber \\
+      & = || \bE_{k+1} ||_{1,2} + \frac{\mu}{2} [ || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2 + \frac{\mu}{2} \langle \blambda_{k}, \bL - \bx_{k+1} - \bE_{k+1} \rangle + \frac{1}{\mu_{k}^2} || \blambda_k ||_F^2 ] - \frac{1}{2\mu_k} || \blambda_k ||_F^2    \nonumber  \\
+      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \bL - \bX_{k+1} - \bE_{k+1} + \frac{\blambda_k}{\mu_k} ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
+      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \frac{1}{\mu_k} [ \mu_k (\bL - \bX_{k+1} - \bE_{k+1}) - \blambda_k ] ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
+      & = || \bE_{k+1} ||_{1,2} + \frac{1}{2\mu_k} ( || \blambda_{k+1} || - || \blambda_{k} ||_F^2 )   .
+    \end{align}
+    \noindent
+    Let $f^*$ denote a local optimal objective function value, which enables the following development:
+    \begin{align}\label{eq:proof2}
+      f^* & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2}   \nonumber  \\
+          & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} || \bL - \bA - \bE ||_F^2   \nonumber \\
+          & \geq \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} ||  \bL - 
+          \bX - \bE ||_F^2     \nonumber \\
+          & = \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2)   .
+    \end{align}
+    \indent
+    Regarding that $\mu_{k} = \rho \mu_{k+1}$ where $\rho > 1$, and the sequence $\{ \blambda_k \}$ is bounded, we derive that
+    $\frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2) \rightarrow 0$ when $k \rightarrow +\infty .$
+    Therefore, when $k \rightarrow +\infty$, we obtain $\min_{\bE, \bA = \bU \bV} = || \bE^* ||_{1,2} \leq f^*$.
+    On the other hand, by Algorithm~\ref{alg:alm_mf}, $\bL - \bX_{k+1} - \bE_{k+1} = \mu_k^{-1} (\blambda_{k+1} - \blambda_{k}) .$
+    As $k \rightarrow +\infty$, we have $\bL - \bX^* - \bE^* \rightarrow +\infty  ,$
+    which indicates that $(\bX^*, \bE^*)$ is a stationary point.
+    This completes proof.
+\end{proof}
+
 \subsection{Final Post Process}
-As we recover the low rank matrix X from the label assisnment matrix L.
+As we recover the low rank matrix X from the label assignment matrix L.
 Intuitively, there is two possible way to get our final fusion results from X.
@@
 \section{Experiments}
-We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, PASCAL VOC’07~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual} and Pascal Sentences dataset.
+We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, Oxford-IIIT-Pet dataset~\cite{parkhi12a} and Pascal Sentences dataset.
 In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model~\cite{he2015deep}, `fc6' layer of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet} and Two-Stream Convolutional Networks~\cite{simonyan2014two}.
@@
 
-\iffalse
-%We perform two experiments to show the effectiveness of the proposed outlier label pruning method.
-%The first experiment is image classification with multiple features.
-%The second experiment is ensemble classification.
-%By these two experiments, we aim to demonstrate that our method is able to effectively remove the anomalous labels from the class indicator matrix, and thus improve the fusion performance of classification.
-\fi
+\subsection{Experiment on Oxford-IIIT-Pet dataset}
+The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
+Each categories have about 200 pictures with a large variations in scale, pose and lighting.
+We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50, ResNet101 and ResNet152).
+
+We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
+We first traing svm on each seperate features by liblinear and fuse by our ORLF methods, comparison result are shown as below:
+
+\begin{table}[h]\small
+\centering
+\label{table:oxford_pet}
+\begin{tabular}{c|c}
+\hline
+Method                       & Mean Accuracy(\%) \\\hline
+ASF                          & 92.46\%           \\
+MKL                          & 87.13\%           \\
+RCEC                         & 92.41\%           \\
+FWOT                         & **                \\
+LPBoost                      & 92.73\%           \\\hline
+Ours                         & 92.84\%           \\
+\hline
+\end{tabular}
+\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
+\end{table}
 
@@
 
+\iffalse
 \subsection{Experiment on PASCAL VOC 2007 dataset}
@@
 \end{table}
+\fi
 
@@
 
+\iffalse
 \subsection{Experiment on Oxford Flowers}
@@
 
+\fi
+
 \begin{quote}

### 2016-09-08 ensemble_clustering.tex
theorem

@@
 \section{Experiments}
-We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, Oxford-IIIT-Pet dataset~\cite{parkhi12a} and Pascal Sentences dataset.
+We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, PASCAL VOC’07~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual} and Pascal Sentences dataset.
 In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model~\cite{he2015deep}, `fc6' layer of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet} and Two-Stream Convolutional Networks~\cite{simonyan2014two}.
@@
 
-\subsection{Experiment on Oxford-IIIT-Pet dataset}
-The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
-Each categories have about 200 pictures with a large variations in scale, pose and lighting.
-We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50, ResNet101 and ResNet152).
-
-We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
-We first traing svm on each seperate features by liblinear and fuse by our ORLF methods, comparison result are shown as below:
-
-\begin{table}[h]\small
-\centering
-\label{table:oxford_pet}
-\begin{tabular}{c|c}
-\hline
-Method                       & Mean Accuracy(\%) \\\hline
-ASF                          & 92.46\%           \\
-MKL                          & 87.13\%           \\
-RCEC                         & 92.41\%           \\
-FWOT                         & **                \\
-LPBoost                      & 92.73\%           \\\hline
-Ours                         & 92.84\%           \\
-\hline
-\end{tabular}
-\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
-\end{table}
+\iffalse
+%We perform two experiments to show the effectiveness of the proposed outlier label pruning method.
+%The first experiment is image classification with multiple features.
+%The second experiment is ensemble classification.
+%By these two experiments, we aim to demonstrate that our method is able to effectively remove the anomalous labels from the class indicator matrix, and thus improve the fusion performance of classification.
+\fi
 
@@
 
-\iffalse
 \subsection{Experiment on PASCAL VOC 2007 dataset}
@@
 \end{table}
-\fi
 
@@
 
-\iffalse
 \subsection{Experiment on Oxford Flowers}
@@
 
-\fi
-
 \begin{quote}

### 2016-09-09 ensemble_clustering.tex
Update Experiment architecture

--- 2016-09-08 ensemble_clustering.tex
@@
 
-\title{Outlier Reject for Late Fusion on Visual Recognition}
+\title{Outlier Rejection for Late Fusion on Visual Recognition}
 
@@
 Then we use voting from M index matrix to select the final label.
+  \item \yanred{Merge X with original soft score}
 \end{itemize}
@@
 
-\iffalse
-\section{An Option on Loss Function: Max Margin}
-In fact, the assignments $\bL$ contains only $0/1$ values (discrete ordinal values).
-This fits the setting in~\cite{yanijcai2015scalable} very much.
-It could be a contribution, since maximum margin loss achieves better performance on discrete ordinal values.
-\yanred{Note: we may leave this extension as a journal?}
+\section{Experiments}
 
-\section{Another Option on Loss Function: $\ell_{1,2}$ to $\ell_1$ loss}
-$\ell_{1,2}$ loss could be difficult to optimize.
-A simple way is to replace $\ell_{1,2}$ to $\ell_1$, which would be much easier.
-\fi
-
-\section{Experiments}
-We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, Oxford-IIIT-Pet dataset~\cite{parkhi12a} and Pascal Sentences dataset.
-In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model~\cite{he2015deep}, `fc6' layer of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet} and Two-Stream Convolutional Networks~\cite{simonyan2014two}.
-Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{simonyan2014two} volumes for C3D).
-Following the same produce in \cite{tran2015learning} and \cite{simonyan2014two}, the features for the whole video are then calculated by averaging the features across the sampled frames.
-In Cifar10 dataset, features are extracted from `global\_pool' layer of the ResnNt-20,32,44,56,110 models\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164 models\cite{he2016identity}.
-In all other dataset, features are extracted among `fc6' layer of VGG network~\cite{chatfield2014return} and AlexNet network~\cite{krizhevsky2012imagenet}, `pool5/7x7\_s1' layer from GoogleNet network~\cite{szegedy2015going}, `pool5' layer of Residual network~\cite{he2015deep}.
-To be noted, all our cnn features are extracted using Caffe\cite{jia2014caffe}, a deep learning framework.
-
-LIBLINEAR\cite{fan2008liblinear} is adopted for our classification toolbox, the confidence scores are generated from the outputs of LIBLINEAR.
-Then we put the confidence scores as the input into our alogrithm.
+In this section, we first visualize the results of our approach on one synthetic dataset and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, CIFAR-10,100~\cite{krizhevsky2009learning} dataset and Oxford-IIIT-Pet dataset~\cite{parkhi12a}.
+Details about how we select features in each dataset are described in the second subsection.
+LIBLINEAR\cite{fan2008liblinear} is adopted for our basic classification toolbox, and the confidence scores are generated from the outputs of LIBLINEAR.
+Then we put the confidence scores as the input of our alogrithm.
 
@@
 (2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
-We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/} ; \url{https://github.com/minghen/liblinear-mkl}} to train out MKL model.
-(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust} (4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
+We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} to train our MKL model.
+(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
+We use the core alogrithm to recover X from L in ~\ref{eq:mf_l21}, and choose the same post process as our method.
+(4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
 The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
@@
 
-The parameter $\mu$ are selected from {0.1, 1, 5, 10}, $\rho$ are select from {1.01, 1.05, 1.1} in all our experiments. For SVM, we use the default parameters set in the LIBLINEAR.
+The parameter $\mu$ are selected from {0.1, 1, 5}, $\rho$ are select from {1.01, 1.05, 1.1} in all our experiments.
+It shows slight different performance by selecting different parameters in our experiment.
+We use the default parameters set in LIBLINEAR for SVM and liblinear-mkl for MKL, unless otherwise specified.
+For RCEC method, we use 5 folder cross validation to select best parameter $\beta$ from {0.01,1,2,4,6,...,20} and set $\lambda = 0.1 \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
+For LPBoost, the smoothing parameter candidates are {0.5, 0.6, ...
+, 0.9} and the parameter C in is selected from $10^{-4},10^{-2},...,10^{4}$ according to cross-validation, which are same as~\cite{xuiccv2013feature}.
+For LPBoost, we use cross-validation to pick up the best $\nu$ from {0.5,0.6,0.7,0.8,0.9}, which is used in~\cite{xuiccv2013feature}.
 
@@
 
-In synthetic experiments, we set N = 320, M = 15, K = 20, randomly generate N instances with K kinds of labels.
-We randomly change 30\% instances' labels, repeat M times to get M classifiers' results.
+In synthetic experiments, we set N = 320, M = 15, K = 20, and randomly generate N instances with K kinds of labels for each instance.
+Then we randomly change 30\% instances' labels, repeat M times to get M classifiers' results.
 By appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure \ref{fig:ensemble_cluster}.
-Each subfigure contrains $N\times M$ small narrow blocks, which visualized in diverse colors according to their different label.
-The first picture~\ref{subfig:gt_pdf}, show the ground truth and copied M times.
+Each subfigure contains $N\times M$ small narrow blocks, which visualized in diverse color according to different label.
+The first picture~\ref{subfig:gt_pdf}, show the ground truth label repeating M times.
 And M noised classifiers' results are pictured as~\ref{subfig:er_pdf}.
-After we recover the low rank matrix from the noised matrix by using ORLF late fusion method, we visualize it as~\ref{subfig:er_pdf}.
+After we recover the low rank matrix from the noised matrix by using our ORLF method, we visualize it as~\ref{subfig:er_pdf}.
 
@@
 
-\subsection{Experiment on Oxford-IIIT-Pet dataset}
-The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
-Each categories have about 200 pictures with a large variations in scale, pose and lighting.
-We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50, ResNet101 and ResNet152).
+\subsection{Feature Selection}
+In this section, we describe of the details of the feature extraction used in each dataset.
+All convolutional neural network(CNN) features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
 
-We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
-We first traing svm on each seperate features by liblinear and fuse by our ORLF methods, comparison result are shown as below:
+In UCF101 dataset, five different features are extracted from the following:
+\begin{itemize}
+  \item `fc6' of C3D~\cite{tran2015learning}
+  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+  \item `pool5' of ResNet-152~\cite{he2015deep}
+  \item two `fc6' of Two-Stream~\cite{simonyan2014two}
+\end{itemize}
+%%Given a video, we first choose 25 frames with equal temporal spacing.
+For frame-level feature, we extract features on sampled 25 frames as described in~\cite{simonyan2014two}.
+For volum-level feature, we extract features on 25 volumes starting from our sampled frames with several continuous frames, 17 frames for C3D~\cite{simonyan2014two} and 10 frames for Two-Stream.
+Finally, we average the sampled 25 feature vectors for each kind of CNN model as our final training data.
 
-\begin{table}[h]\small
-\centering
-\label{table:oxford_pet}
-\begin{tabular}{c|c}
-\hline
-Method                       & Mean Accuracy(\%) \\\hline
-ASF                          & 92.46\%           \\
-MKL                          & 87.13\%           \\
-RCEC                         & 92.41\%           \\
-FWOT                         & **                \\
-LPBoost                      & 92.73\%           \\\hline
-Ours                         & 92.84\%           \\
-\hline
-\end{tabular}
-\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
-\end{table}
+Given a video, we extract the above five features following the same process in \cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
+All models we used are available on Internet provided by authors.
+
+In Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,68,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,68,110,164 models~\cite{he2016identity}.
+Another feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}.
+We train each ResNet model following the standard procedure in ~\cite{he2015deep,he2016identity} and cifar10\_full model use a official shell\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}} before extracting features.
+In Cifar100 dataset, we use the same model and process as in Cifar10 except the caffe example model and pre-activation ResNet-68, totaly twelve features.
+
+In all other experiments, eight different features are extracted from the following:
+\begin{itemize}
+  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
+  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
+  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
+\end{itemize}
+We use the offical caffe model provided by Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}} for all above features with no extrat operation.
 
 \subsection{Experiment on UCF 101 dataset}
-For action recognition, we present our results on UCF 101 dataset\cite{soomro2012ucf101}.
+For action recognition, we present our results on UCF 101 dataset~\cite{soomro2012ucf101}.
 UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
-We use the official split1 described in \cite{soomro2012ucf101}, which have 9573 training videos 3783 testing videos.
-As mentioned above, fives features are provided from the state of the art deep convolution networks, 4096 demitions features in `fc6' layer from C3D, 1028 demitions features in `pool5/7x7\_s1' layer from  GoogleNet, 2048 demitions features in `pool5' layer of ResNet-152, 4096 demitions features in `fc6' layer in Spatial and Temporal Net.
-All models used in UCF-101 are published by their authors.
-
-We use liblinear to train seperate classifiers on each features with the default parameters in liblinear.
-By appling trained classifiers on test data, we can obtain 5 * 20 confidence score for each video.
-After emsenable fusion, we choose the class with highest confidence score as our predicted class.
+We use the official split1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
+As mentioned above, we extract fives features and use liblinear to train seperate classifiers on each features with the default parameters in liblinear.
+By appling five classifiers on test data, we can obtain 5 * 101 confidence scores for each video.
+After emsenable fusion, we choose the class with the highest confidence score as our predicted class.
 Results are shown in \ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare several fusion method.
@@
 \end{tabular}
-\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
+%\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
+\caption{Mean Accuracy on UCF101 dataset}
+\end{table}
+
+\subsection{Experiment on Cifar10 dataset}
+In CIFAR-10 dataset~\cite{krizhevsky2009learning}, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
+There are 50000 training data and 10000 testing data.
+Fourteen CNN features are extracted from multiple state of the art models for training svm.
+This experiments show the ability of our algorithm to handle large scale data.
+
+As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day).
+LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
+We also use `-s 2' parameters in liblinear to speedup training process.
+Results of other contrast algorithms are shown on \ref{table:cifar10}
+
+\begin{table}[h]\scriptsize
+\centering
+\label{table:cifar10}
+\begin{tabular}{c|c|c}
+\hline
+Method  & Mean Accuracy     & Classification Time + Fusion Time(s)\\\hline
+ASF     & 94.21\%           & 55.6 + 0.02                         \\
+MKL     & 94.15\%           & 865.09                              \\
+RCEC    & 94.87\%           & 55.6 + 3.5                          \\
+FWOT    & -                 & -                                   \\
+LPBoost & 94.88\%           & 54.99                               \\\hline
+Ours    & 95.05\%           & 55.6 + 32.1                         \\
+\hline
+\end{tabular}
+\caption{Mean Accuracy and Time cost on cifar10 dataset}
+\end{table}
+
+\subsection{Experiment on Cifar100 dataset}
+CIFAR-100~\cite{krizhevsky2009learning} is similar with CIFAR-10, except it has 100 classes containing 600 images each.
+There are 50000 training data and 10000 testing data as CIFAR-10.
+Twelve CNN features used in this experiment are describe in the previous section.
+Training and comparison process are the same as in CIFAR-10.
+Results are shown as below:
+
+\begin{table}[h]\scriptsize
+\centering
+\label{table:cifar100}
+\begin{tabular}{c|c|c}
+\hline
+Method  & Mean Accuracy \\\hline
+ASF     & 76.91\%           \\
+MKL     & 72.71\%           \\
+RCEC    & 96.96\%           \\
+FWOT    & -                 \\
+LPBoost & 76.59\%           \\\hline
+Ours    & 77.18\%           \\
+\hline
+\end{tabular}
+\caption{Mean Accuracy on cifar100 dataset}
+\end{table}
+
+\subsection{Experiment on Oxford-IIIT-Pet dataset}
+The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
+Each categories have about 200 pictures with a large variations in scale, pose and lighting.
+We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
+We first traing svm on each seperate features and fuse by our ORLF method.
+The comparison results are shown as below:
+
+\begin{table}[h]\small
+\centering
+\label{table:oxford_pet}
+\begin{tabular}{c|c}
+\hline
+Method                       & Mean Accuracy     \\\hline
+ASF                          & 92.46\%           \\
+MKL                          & 87.13\%           \\
+RCEC                         & 92.41\%           \\
+FWOT                         & 92.90\%           \\
+LPBoost                      & 92.73\%           \\\hline
+Ours                         & 92.84\%           \\
+\hline
+\end{tabular}
+\caption{Mean Accuracy on Oxford-IIIT-Pet dataset}
+\end{table}
+
+\subsection{Post Strategy Selection}
+In this section, we first compare three proposed final post strategy on tree small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}.
+Then we analyse the reason we choose the first strategy as our post process method.
+\yanred{analysis and details of three dataset}.
+
+\begin{table}[h]\small
+\centering
+\label{table:strategy}
+\begin{tabular}{c|c|c|c}
+\hline
+Method                       & VOC 2007 &  Flowers 17  & Caltech 101 \\\hline
+Strategy 1                   & *  &              & \\\hline
+Strategy 2                   & *  &              & \\\hline
+Strategy 3                   & *  &              & \\\hline
+\hline
+\end{tabular}
+\caption{Mean Accuracy on Three Strategies}
+\end{table}
+
+\yanred{Unwork dataset Record Data}
+
+\begin{table}[h]\small
+\centering
+\label{table:voc2007}
+\begin{tabular}{c|c}
+\hline
+Method                       & Mean Accuracy     \\\hline
+ASF                          & 89.04\%           \\
+MKL                          & 85.53\%           \\
+RCEC                         & 89.60\%           \\
+FWOT                         & 89.85\%           \\
+LPBoost                      & 90.54\%           \\\hline
+Ours                         & 89.57\%           \\
+\hline
+\end{tabular}
+\caption{VOC2007}
+\end{table}
+
+\begin{table}[h]\scriptsize
+\centering
+\label{table:flower17}
+\begin{tabular}{c|c}
+\hline
+Method & Mean Accuracy\\\hline
+ASF &  96.81\% \\
+MKL &  93.24\% \\
+RCEC &  96.81\% \\
+FWOT &  96.88\% \\
+LPBoost & 97.24\% \\\hline
+Ours &  96.62\% \\
+\hline
+\end{tabular}
+\caption{Oxford Flowers 17}
 \end{table}
@@
 
-\begin{table}[!h]\scriptsize
-\centering
-\label{table:voc}
-\begin{tabular}{c|c|c|c}
-\hline
-Method            & Mean Accuracy & Classification Time(s)& Fusion Time \\\hline
-Best Single Model & 88.44\%       &  2.347                &      0    \\\hline
-ASF               & 88.69\%       &  10.2347              &    0.008   \\ % Average
-MKL               &     0 & 00 & 0 \\
-RCEC              &     0 & 0 & 000 \\
-FWOT              &     0 & 0 & 000 \\
-LPBoost           &     0 & 0 & 000 \\\hline
-Ours              & 88.78\%       & 10.2347               & 9.918 \\
-\hline
-\end{tabular}
-\caption{Accuracy and Time cost on VOC2007 dataset}
-\end{table}
-\fi
-
-\subsection{Experiment on Cifar10 dataset}
-In CIFAR-10 dataset~\cite{krizhevsky2009learning}, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
-There are 50000 training data and 10000 testing data.
-Fourteen CNN features are extracted from multiple state of the art models for training svm.
-These features are `global\_pool' layers' features of ResNet-20,32,44,56,110~\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164~\cite{he2016identity},  `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}} and `global\_pool' layers' features from two modified network from~\cite{szegedy2015going,chatfield2014return}.
-This experiments show the ability of our ORLF to handle large scale data.\yanred{(how to say)}
-
-As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day).
-LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
-the use `-s 2' parameters in liblinear to speedup training training process.
-Results of other contrast algorithms are shown on \ref{table:cifar10}
-
-\begin{table}[h]\scriptsize
-\centering
-\label{table:cifar10}
-\begin{tabular}{c|c|c}
-\hline
-Method  & Mean Accuracy(\%) & Classification Time + Fusion Time(s)\\\hline
-ASF     & 94.21\%           & 55.6 + 0.02                         \\
-MKL     & 94.15\%           & 865.09                              \\
-RCEC    & 94.87\%           & 55.6 + 3.5                          \\
-FWOT    & -                 & -                                   \\
-LPBoost & 94.88\%           & 54.99                               \\\hline
-Ours    & 95.05\%           & 55.6 + 32.1                         \\
-\hline
-\end{tabular}
-\caption{Accuracy and Time cost on cifar10 dataset}
-\end{table}
-
-\iffalse
 \subsection{Experiment on Oxford Flowers}
@@
 Results are shown in \ref{table:flower17}
-
-\begin{table}[h]\scriptsize
-\centering
-\label{table:flower17}
-\begin{tabular}{c|c|c|c}
-\hline
-Method & Split 1 & Split 2 & Split 3\\\hline
-ASF &  97.94\% & 0 & 0 \\
-MKL &  000 & 0 & 0 \\
-RCEC &  000 & 0 & 0 \\
-FWOT &  000 & 0 & 0 \\
-LPBoost & 97.94\% & 0 & 0 \\\hline
-Ours &  98.24\% & 0 & 0 \\
-\hline
-\end{tabular}
-\caption{Accuracy on Three Official Split}
-\end{table}
 

### 2016-09-10 ensemble_clustering.tex
intro

--- 2016-09-08 ensemble_clustering.tex
@@
 \def\st{{\text{s.t.}}}
+\def\etc{\emph{etc}}
+\def\ie{\emph{ie}}
+\def\eg{\emph{eg}}
 \def\rank{{\text{rank}}}
@@
 
-\title{Outlier Reject for Late Fusion on Visual Recognition}
+%\title{Outlier Reject for Late Fusion on Visual Recognition}
+\title{Robust Late Fusion Based on Matrix Factorization}
 
@@
 % Second: what BIG problem would we like to solve?
-Late fusion, which combines the predictions of multiple features, is a commonly used approach to generate the final decision for a test instance.
+Late fusion, which linearly combines the predictions of multiple features, is a commonly used approach to generate the final decision for a test instance.
 % Third: specify the detailed problem: find a precise position for our paper
@@
 %背景 多model融合
-Image or video data in the real world can be represented in multiple features.
-For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
-Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
-Each feature contains rich information of real data, which can not capture all views of our data.
-A single classifier model will bias on some characteristics of training data based on different features.
-It can significantly improve the performance by combining multiple features together and capturing more views on data.
+Feature extraction, which transforms raw data into numerical features, is a prerequisite for most real world applications.
+There are often multiple ways to generate numerical features from raw data.
+For example, for image data, one can extract hand-crafted features such as scale-invariant feature transform
+(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevskynips2012imagenet}.
+Text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
+%Videos can be represented by Dense Trajectories~\cite{Wang2011Action}, CNNs~\cite{xucvpr2015discriminative}, \etc.
+%\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}
+Each category of features tends to capture a specific characteristics of data.
+A model trained on an individual feature could be biased and hence obtains an unsatisfactory performance.
+Existing works have investigate the performance improvement by combining multiple features in real world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.
+
+%Image or video data in the real world can be represented in multiple features.
+%For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
+%Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}.
+%Each feature contains rich information of real data, which can not capture all views of our data.
+%A single classifier model will bias on some characteristics of training data based on different features.
+%It can significantly improve the performance by combining multiple features together and capturing more views on data.
 
@@
 %% late fusion is a common sigle model -> single feature, 介绍late fusion
-Late fusion is a common method to make the combination of different features.
+Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from each individual feature.
+A commonly used method is to learn weights for predictions of each feature and linearly combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
+Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
+However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
+To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
+Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.
+
+%Late fusion is a common method to make the combination of different features.
 Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
-A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
+%A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
 Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
-\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
+%\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
 }
@@
 %%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
-It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem.
-There are some researchers have ability to reject the outlier of multiple results, such as \cite{gaoijcai2016robust} use low rank sparse $\ell_{1,2}$ loss and nuclear norm to solve, which are poorly to extend to large scale data due to the expensive cost of Singular Value Decomposition(SVDs) present in the alogrithm.
-The other research on matrix factorization foucs on least square smooth loss funcion, which is sensitive to outlier and it's unclear to extend matrix factorization to nonsmooth $\ell_{1,2}$ loss.
 
-In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
-We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers.
-We introduce the low rank constraint to maintain the consistency among differernt classifers.
-The formulation can be written as bellow:
-
-\begin{align}\label{eq:typical_mc}
-  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k  ,
-\end{align}
-\noindent
-
-L a is observed matrix, represent the label indicator matrix in our vision recoginition case.
-X is a low rank matrix recovered from L.
+To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
+As for outlier detection, as shown in Figure~\ref{fig:framework}, we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
+%which can be represented in the following:
+%\begin{align}\label{eq:typical_mc}
+%  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
+%  \st        ~&~ \rank(\bX) \leq k  ,
+%\end{align}
+%\noindent
+%$L$ is the indicator matrix, represent the label indicator matrix in our vision recoginition case.
+%X is a low rank matrix recovered from L.
 Rank function measures the rank of a matrix.
 $|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
-Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
+%Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
 For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
-\begin{align}\label{eq:mf_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
-\end{align}
-\noindent
-Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth.
-In our proposed method(ORLF), we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
-
-Our main contribution can be summarized as below:
+%\begin{align}\label{eq:mf_l21}
+%  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
+%  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
+%\end{align}
+%\noindent
+Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
+We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
+The main contributions are summarized as below:
 \begin{itemize}
-  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
-  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
-  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
+  \item We propose an efficient late fusion algorithm based on matrix factorization.
+  \item We extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
+  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
 \end{itemize}
@@
 %%
-\yanred{MF method}
+
+Matrix factorization has attracted increasing attention recently,
+and many manifold optimization based algorithms have been proposed by exploiting the manifold geometry.
+Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
+In~\cite{vandereycken2013lowrank}, the authors propose a low rank geometric conjugate gradient (LRGeomCG) method.
+In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low rank matrix completion by exploiting the low rank constraint.
+In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
+In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
+The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
+In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
+The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm is proposed to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
+In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
+However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
 
 %%RPCA Methods
-Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix.
+%Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix.
 This could also be used in our late fusion application to remove outlier column in the indicator matrix L.
@@
   \bibliographystyle{aaai}
-  \bibliography{ensemble_clustering}
+  \bibliography{ensemble_clustering,m3frp}
 \end{small}

### 2016-09-10 ensemble_clustering.tex
Merge Introduction By Yan. and Complete Related Work

--- 2016-09-09 ensemble_clustering.tex
@@
 
-\title{Outlier Rejection for Late Fusion on Visual Recognition}
+\title{Robust Late Fusion Based on Matrix Factorization}
 
@@
 
-%% Written by DXY:
-%%% We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC).
-SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability).
-To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion.
-Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101.
 \end{abstract}
@@
 %背景 多model融合
-Image or video data in the real world can be represented in multiple features.
-For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
-Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
-Each feature contains rich information of real data, which can not capture all views of our data.
-A single classifier model will bias on some characteristics of training data based on different features.
-It can significantly improve the performance by combining multiple features together and capturing more views on data.
+Feature extraction, which transforms raw data into numerical features, is a prerequisite for most real world applications.
+There are often multiple ways to generate numerical features from raw data.
+For example, for image data, one can extract hand-crafted features such as scale-invariant feature transform
+(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevskynips2012imagenet}.
+Text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
+%Videos can be represented by Dense Trajectories~\cite{Wang2011Action}, CNNs~\cite{xucvpr2015discriminative}, \etc.
+%\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}
+Each category of features tends to capture a specific characteristics of data.
+A model trained on an individual feature could be biased and hence obtains an unsatisfactory performance.
+Existing works have investigate the performance improvement by combining multiple features in real world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.
 
-%%A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}.
-Fusion techniques can be grouped into two types which are early fusion and late fusion, early fusion fusion multiple models in the feature level, late fusion merge the result of each classifier.
+%背景 多model融合
+%Image or video data in the real world can be represented in multiple features.
+%For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
+%Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and 
+%Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and 
+%sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
+%Each feature contains rich information of real data, which can not capture all views of our data.
+%A single classifier model will bias on some characteristics of training data based on different features.
+%It can significantly improve the performance by combining multiple features together and capturing more views on data.
 
 %% late fusion is a common sigle model -> single feature, 介绍late fusion
-Late fusion is a common method to make the combination of different features.
+Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from each individual feature.
+A commonly used method is to learn weights for predictions of each feature and linearly combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
+Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
+However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
+To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
+Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.
+
+%% late fusion is a common sigle model -> single feature, 介绍late fusion
+%%Late fusion is a common method to make the combination of different features.
 Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
-A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
+%% A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
 Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
-\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
+%% \yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
 }
@@
 %%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
-It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem.
+%% It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem.
 There are some researchers have ability to reject the outlier of multiple results, such as \cite{gaoijcai2016robust} use low rank sparse $\ell_{1,2}$ loss and nuclear norm to solve, which are poorly to extend to large scale data due to the expensive cost of Singular Value Decomposition(SVDs) present in the alogrithm.
@@
 
-In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
-We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers.
+To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
+As for outlier detection, as shown in Figure~\ref{fig:framework}, we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
+Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
+We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
+The main contributions are summarized as below:
+\begin{itemize}
+  \item We propose an efficient late fusion algorithm based on matrix factorization.
+  \item We extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
+  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
+\end{itemize}
+
+%%In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
+%%We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers.
 We introduce the low rank constraint to maintain the consistency among differernt classifers.
-The formulation can be written as bellow:
+%%The formulation can be written as bellow:
 
-\begin{align}\label{eq:typical_mc}
-  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k  ,
-\end{align}
-\noindent
+%\begin{align}\label{eq:typical_mc}
+%  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
+%  \st        ~&~ \rank(\bX) \leq k  ,
+%\end{align}
+%\noindent
 
-L a is observed matrix, represent the label indicator matrix in our vision recoginition case.
+%L a is observed matrix, represent the label indicator matrix in our vision recoginition case.
 X is a low rank matrix recovered from L.
@@
 $|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
-Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
+%Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
 For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
-\begin{align}\label{eq:mf_l21}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
-\end{align}
-\noindent
-Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth.
+%\begin{align}\label{eq:mf_l21}
+%  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
+%  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
+%\end{align}
+%\noindent
+%Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth.
 In our proposed method(ORLF), we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.
 
-Our main contribution can be summarized as below:
-\begin{itemize}
-  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
-  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
-  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
-\end{itemize}
+%Our main contribution can be summarized as below:
+%\begin{itemize}
+%  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
+%  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
+%  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
+%\end{itemize}
 
@@
 
-\iffalse
-The key aim of matrix completion based methods is to detect the anomalous clusters (bad partitions/assigments) and reconstruct the real assignments,
-which is shown in Figure~\ref{fig:anomalous_cluster}.
-A typical formulation of matrix completion based methods then can be written as below:
-\begin{align}\label{eq:typical_mc}
-  \min_{\bX} ~&~ || \bX - \bL ||_2^2   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k  ,
-\end{align}
-\noindent
-where $k$ is a pre-defined rank constraint,
-and $\bL \in \dsR^{N \times MK}$.
-Here we denote $M$ and $K$ as the number of single clustering assignments and the number of clusters, respectively.
-However, the least square loss used in matrix completion is sensitive to the abnormal errors, namely outliers, the not appropriate to capture the anomalous assignments.
-The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{1,2}$ norm on $\bX$, which is as follow
-\begin{align}\label{eq:mc_l21_gaospaper}
-  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{1,2}   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k   ,
-\end{align}
-\noindent
-where $|| \bX ||_{1,2} = \sum_{j = 1}^{MK} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
-which would make $\bX$ column-wise sparse (beware the direction of the computation of the $\ell_{1,2}$ norm, more details in~\cite{nienips2010efficient}).
-Nevertheless, it does not consider the outliers in their loss function.
-In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{1,2}$ is equivalent to $|| \bX - \bO ||_{1,2}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
-\fi
+\section{Related Work}
+%% Matrix factorization
+%% Fusion Methods
+%%
 
-\section{Related Work}
-%% RPCA robust
-%% Matrix F...
-%%
-\yanred{MF method}
+Matrix factorization has attracted increasing attention recently,
+and many manifold optimization based algorithms have been proposed by exploiting the manifold geometry.
+Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
+In~\cite{vandereycken2013lowrank}, the authors propose a low rank geometric conjugate gradient (LRGeomCG) method.
+In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low rank matrix completion by exploiting the low rank constraint.
+In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
+In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
+The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
+In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
+The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm is proposed to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
+In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
+However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
 
-%%RPCA Methods
-Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix.
-This could also be used in our late fusion application to remove outlier column in the indicator matrix L.
-\cite{wright2009robust} instroduce a representative Robust PCA algorithm, and \cite{ye2012robust} propose a rank minimization method optimize the RPCA to fuse the predicted confidence scores of multiple models.
-\yanred{other RPCA and disadvantage}
-
-MKL~\cite{Rakotomamonjy2008Simplemkl} based method is a simple but efficient way to combine different features for late fusion.
-\cite{vedaldi2009multiple} use MKL to learn an optimal combination of exponential ${\chi}^2$.
-\cite{gehler2009feature} introduce two boosting approaches inspired by the MKL.
-\cite{natarajan2012multimodal} combines these diverse features using a two-step strategy employing MKL and late score fusion methods.
-\cite{lai2015learning} proposed a late fusion method that determines the optimal fusion weights for each sample.
-\yanred{\cite{xuiccv2013feature} learns the weights, thresholding and smoothing parameters in a joint framework to combine the decision values.
-Copy from Abs}.
-\yanred{However, MKL based method...}
+MKL based method is a simple but efficient way to combine different features for multi-model fusion,
+and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
+In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel. 
+In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
+In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
+In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
+which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
+In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values, 
+which learns the weights, thresholding and smoothing parameters in a joint framework.
+However, all these mkl based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.
 
@@
 Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
-The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown in \ref{eq:mf_l21}.
+The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown bellow:
+
+\begin{align}\label{eq:mf_l21}
+    \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
+    \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
+\end{align}
 The k of the low rank constraint in (\ref{eq:mf_l21}) is the number of class in recoginition task.
@@
 \centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
-\caption{something}\label{fig:framework}
+\caption{Frame Work}
+\label{fig:framework}
 \end{figure}
@@
 X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L.
-Two possible post way to processing X are described as bellow:
+Three possible post ways processing X are described as bellow, $X_{*j}$ represents the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X:
 \begin{itemize}
-  \item Average the score matrixs, each of which is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X.
-Then we got $X^*$, a N*K score matrix.
+  \item Average the score matrixs $X_{*j}$, which is a subset of X.
+Then we got $X^*$, a $N\times K$ score matrix.
 we make the position of the highest value in each rows as the predicted label of the i-th instance.
-  \item Seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum.
-For each matrix $Y_j$, we obtain a column vector by selecting the index of the highest score in each row.
-Then we use voting from M index matrix to select the final label.
-  \item \yanred{Merge X with original soft score}
+  \item The same pre-process as the first strategy, but we use voting to predict the final label the i-th instance.
+  \item We normalize each subset of X by softmax function and the corresponding confidence score matrix Y by L2 norm.
+Then we treat each element as a gate to the corresponding one in Y, which effects on Y by production.
+Finally the indicator of the highest value is selected to be the predicted label as the first strategy.
 \end{itemize}
-According to the experiments, the first strategy outperform than the second one, we choose the first one as our final post process of fusion method.
+According to the experiments, the first strategy outperforms than the others, we choose the first one as our final post process of fusion method and analyse inner reason during experiment section.
 
@@
 In this section, we first compare three proposed final post strategy on tree small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}.
-Then we analyse the reason we choose the first strategy as our post process method.
-\yanred{analysis and details of three dataset}.
+PASCAL VOC 2007 contrains 6146 images classified into 20 classes, after filtering the multi-label data.
+Oxford Flowers 17 dataset havs 17 flower categories with 80 images for each class.
+Caltech 101 contains a total of 9,146 images, split between 101 distinct object categories and a background category.
+
+Experiment results show that the first strategy outperforms than the others in most cases and never performe under the others. \yanred{Lack Analysis}
 
@@
 Method                       & VOC 2007 &  Flowers 17  & Caltech 101 \\\hline
-Strategy 1                   & *  &              & \\\hline
-Strategy 2                   & *  &              & \\\hline
-Strategy 3                   & *  &              & \\\hline
+Strategy 1                   & 89.56\%  &  96.76\%     &    -        \\\hline
+Strategy 2                   & 89.26\%  &  96.61\%     &    -        \\\hline
+Strategy 3                   & 89.16\%  &  96.75\%     &    -        \\\hline
 \hline
@@
 
-\yanred{Unwork dataset Record Data}
+\subsection{\yanred{Unwork dataset Record Data}}
+
+\yanred{On PASCAL VOC 2007 and Oxford Flowers 17 Datasets.}
 
@@
 \end{tabular}
-\caption{VOC2007}
+\caption{VOC 2007}
 \end{table}

### 2016-09-10 ensemble_clustering.tex
Complete Experiments and Post Process Subsection

@@
 We introduce the low rank constraint to maintain the consistency among differernt classifers.
-%%The formulation can be written as bellow:
+%%The formulation can be written as below:
 
@@
 %Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
-For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
+For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as below:
 %\begin{align}\label{eq:mf_l21}
@@
 Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
-The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown bellow:
+The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown below:
 
@@
 Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
-We apply ALM to optimize the nonsmooth objective function efficiently, desccribed as bellow:
+We apply ALM to optimize the nonsmooth objective function efficiently, desccribed as below:
 
@@
 
-\subsection{Final Post Process}
-As we recover the low rank matrix X from the label assignment matrix L.
-Intuitively, there is two possible way to get our final fusion results from X.
-Although L is a 01 matrix obtain by hard label, we could treat it as a soft score matrix, which the position of highest score represent the most possible label predicted by classifiers.
-X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L.
-Three possible post ways processing X are described as bellow, $X_{*j}$ represents the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X:
+\subsection{Post Process}
+As we recover the low rank matrix X from the label assignment matrix L,
+it does need a post process to generate the predicted label for each testing data.
+Intuitively, there might be several possible ways to select as below : 
 \begin{itemize}
-  \item Average the score matrixs $X_{*j}$, which is a subset of X.
-Then we got $X^*$, a $N\times K$ score matrix.
-we make the position of the highest value in each rows as the predicted label of the i-th instance.
-  \item The same pre-process as the first strategy, but we use voting to predict the final label the i-th instance.
-  \item We normalize each subset of X by softmax function and the corresponding confidence score matrix Y by L2 norm.
-Then we treat each element as a gate to the corresponding one in Y, which effects on Y by production.
-Finally the indicator of the highest value is selected to be the predicted label as the first strategy.
+  \item A $N\times K$ score matrix $X^{*}$ is obtained by averaging matrixes $X_{*j}$\footnote{the subset matrix of X from (j*k-k+1)-th to (j*k)-th colums} $(1{\leq}j{\leq}m)$. 
+		The indicator of the highest value in each row of $X^{*}$ is regard as the predicted label for the corresponding data.
+  \item For $X_{*j} (1{\leq}j{\leq}m)$, we set $I_{ij}$ is the index of the highest value in the i-th row of $X_{*j}$.
+  		Each $I_{ij}$ contributes one point to the i-th data with label j. 
+  		Finally, we choose the label with the most votes to be the predicted results.
+  \item $X_{*j}$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by L2 norm. 
+  		As $X_{*j}$ contains outlier rejection information, we product the $X_{*j}$ by the corresponding score matrix after softmax and normalization.
+  		The similar process as the first strategy is applied to the above results, which predictes the final label.
 \end{itemize}
-According to the experiments, the first strategy outperforms than the others, we choose the first one as our final post process of fusion method and analyse inner reason during experiment section.
+According to the experiments, the last strategy outperforms than the others. 
+So We choose the last one as the post process for fusion method and analyse inner reasons during experiment section.
 
@@
 
-In this section, we first visualize the results of our approach on one synthetic dataset and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, CIFAR-10,100~\cite{krizhevsky2009learning} dataset and Oxford-IIIT-Pet dataset~\cite{parkhi12a}.
-Details about how we select features in each dataset are described in the second subsection.
-LIBLINEAR\cite{fan2008liblinear} is adopted for our basic classification toolbox, and the confidence scores are generated from the outputs of LIBLINEAR.
-Then we put the confidence scores as the input of our alogrithm.
+In this section, we first visualize the results of our approach on one synthetic dataset 
+and evaluate the perfomance on four publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, CIFAR-10,100~\cite{krizhevsky2009learning} dataset and Oxford-IIIT-Pet dataset~\cite{parkhi12a}.
+Details on feature extraction for each dataset are described in the second subsection.
+LIBLINEAR\cite{fan2008liblinear} is adopted for our basic classification toolbox, and the confidence scores are set as outputs of LIBLINEAR. 
+Then we put the confidence scores as the input X of our alogrithm.
 
-Five state-of-the-art fusion methods are compared with our proposed alogrithm : (1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers.
-We use $L_2$ norm on each classifiers for normalization.
+Five state-of-the-art fusion methods are compared with our proposed alogrithm : 
+(1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization. 
 (2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
 We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} to train our MKL model.
-(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
-We use the core alogrithm to recover X from L in ~\ref{eq:mf_l21}, and choose the same post process as our method.
+(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}. The core alogrithm in RCEC can be modified to recover X from L in ~\ref{eq:mf_l21}, and the post process is same as our method. 
 (4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
 The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
-(5)LPBoost\cite{gehler2009feature}.
-In this method, a variant linear combination are applied to multiple classifiers.
+(5)LPBoost\cite{gehler2009feature}. In this method, a variant linear combination are applied to multiple classifiers to boost performance.
 
-The parameter $\mu$ are selected from {0.1, 1, 5}, $\rho$ are select from {1.01, 1.05, 1.1} in all our experiments.
-It shows slight different performance by selecting different parameters in our experiment.
-We use the default parameters set in LIBLINEAR for SVM and liblinear-mkl for MKL, unless otherwise specified.
-For RCEC method, we use 5 folder cross validation to select best parameter $\beta$ from {0.01,1,2,4,6,...,20} and set $\lambda = 0.1 \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
-For LPBoost, the smoothing parameter candidates are {0.5, 0.6, ...
-, 0.9} and the parameter C in is selected from $10^{-4},10^{-2},...,10^{4}$ according to cross-validation, which are same as~\cite{xuiccv2013feature}.
-For LPBoost, we use cross-validation to pick up the best $\nu$ from {0.5,0.6,0.7,0.8,0.9}, which is used in~\cite{xuiccv2013feature}.
+The parameter $\mu$ is selected from \{0.1, 1, 5\} and $\rho$ is select from \{1.01, 1.05, 1.1\} in all our experiments.
+It shows slight performance change during selecting different parameters. 
+We use the default parameters set in LIBLINEAR and liblinear-mkl, unless otherwise specified. 
+For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from \{0.01,1,2,4,6,...,20\} and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
+For FWOT, the smoothing parameter candidates are \{0.5, 0.6, ...
+, 0.9\} and the parameter C in is selected from \{$10^{-4},10^{-2},...,10^{4}$\} according to cross-validation, which is same in~\cite{xuiccv2013feature}.
+For LPBoost, we use cross-validation to pick up the best $\nu$ from \{0.5,0.6,0.7,0.8,0.9\} suggested by~\cite{xuiccv2013feature}.
 
@@
 Then we randomly change 30\% instances' labels, repeat M times to get M classifiers' results.
-By appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure \ref{fig:ensemble_cluster}.
+Appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure~\ref{fig:ensemble_cluster}.
 Each subfigure contains $N\times M$ small narrow blocks, which visualized in diverse color according to different label. 
@@
 And M noised classifiers' results are pictured as~\ref{subfig:er_pdf}. 
-After we recover the low rank matrix from the noised matrix by using our ORLF method, we visualize it as~\ref{subfig:er_pdf}.
+We recover the low rank matrix from the noised matrix by using our late fusion method, which is visualized as~\ref{subfig:er_pdf}.
 
@@
 
-\subsection{Feature Selection}
-In this section, we describe of the details of the feature extraction used in each dataset.
+\subsection{Feature Extraction}
+In this section, we describe the details of the feature extraction for each dataset. 
 All convolutional neural network(CNN) features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
@@
   \item `pool5' of ResNet-152~\cite{he2015deep}
-  \item two `fc6' of Two-Stream~\cite{simonyan2014two}
+  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
 \end{itemize}
-%%Given a video, we first choose 25 frames with equal temporal spacing.
-For frame-level feature, we extract features on sampled 25 frames as described in~\cite{simonyan2014two}.
-For volum-level feature, we extract features on 25 volumes starting from our sampled frames with several continuous frames, 17 frames for C3D~\cite{simonyan2014two} and 10 frames for Two-Stream.
-Finally, we average the sampled 25 feature vectors for each kind of CNN model as our final training data.
-
-Given a video, we extract the above five features following the same process in \cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
+Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
 All models we used are available on Internet provided by authors.
@@
 Another feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}.
-We train each ResNet model following the standard procedure in ~\cite{he2015deep,he2016identity} and cifar10\_full model use a official shell\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}} before extracting features.
+We train each ResNet model following the standard procedure in~\cite{he2015deep,he2016identity} and cifar10\_full model using a official shell\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}} before extracting features.
 In Cifar100 dataset, we use the same model and process as in Cifar10 except the caffe example model and pre-activation ResNet-68, totaly twelve features.
@@
 \end{itemize}
-We use the offical caffe model provided by Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}} for all above features with no extrat operation.
+We use the offical caffe model provided by Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}.
+For above eight features, we don't do extra operation.
 
 \subsection{Experiment on UCF 101 dataset}
+
 For action recognition, we present our results on UCF 101 dataset~\cite{soomro2012ucf101}. 
@@
 We use the official split1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
-As mentioned above, we extract fives features and use liblinear to train seperate classifiers on each features with the default parameters in liblinear.
-By appling five classifiers on test data, we can obtain 5 * 101 confidence scores for each video.
-After emsenable fusion, we choose the class with the highest confidence score as our predicted class.
-Results are shown in \ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare several fusion method.
+
+As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by liblinear. 
+Appling five classifiers on test data, we obtain 5 * 101 confidence scores for each video, which forms the input matrix X of our algorithm. 
+Results are shown in Table~\ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare six fusion methods. 
 To be noted, FWOT~\cite{xuiccv2013feature} is too slow to train, we didn't show it's result (more than one day).
@@
 MKL                          & 85.38\%           \\
-RCEC                         & 88.29\%           \\
+RCEC                         & 86.60\%           \\          %ori: 0.88290  vote : 0.88158
 FWOT                         & -                 \\
 LPBoost                      & 86.24\%           \\\hline
-Ours                         & 88.89\%           \\
+Ours                         & 89.03\%           \\          %ori: 0.8888   vote : 0.88686
 \hline
@@
 \subsection{Experiment on Cifar10 dataset}
+
 In CIFAR-10 dataset~\cite{krizhevsky2009learning}, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class. 
 There are 50000 training data and 10000 testing data. 
-Fourteen CNN features are extracted from multiple state of the art models for training svm.
+Fourteen CNN features are extracted from multiple state of the art models. 
 This experiments show the ability of our algorithm to handle large scale data.
@@
 LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
-We also use `-s 2' parameters in liblinear to speedup training process.
-Results of other contrast algorithms are shown on \ref{table:cifar10}
+We also use `-s 2' parameters in liblinear to speedup training process. Results of other contrast algorithms are shown on \ref{table:cifar10}
 
@@
 MKL     & 94.15\%           & 865.09                              \\
-RCEC    & 94.87\%           & 55.6 + 3.5                          \\
+RCEC    & 94.99\%           & 55.6 + 3.5                          \\         % ori:0.94850  vote:0.94820 / 0.95070
 FWOT    & -                 & -                                   \\
 LPBoost & 94.88\%           & 54.99                               \\\hline
-Ours    & 95.05\%           & 55.6 + 32.1                         \\
+Ours    & 95.11\%           & 55.6 + 32.1                         \\         % ori:0.95050  vote:0.95030
 \hline
@@
 \subsection{Experiment on Cifar100 dataset}
+
 CIFAR-100~\cite{krizhevsky2009learning} is similar with CIFAR-10, except it has 100 classes containing 600 images each.
 There are 50000 training data and 10000 testing data as CIFAR-10. 
-Twelve CNN features used in this experiment are describe in the previous section.
-Training and comparison process are the same as in CIFAR-10.
-Results are shown as below:
+Twelve CNN features used in this experiment are described in the previous section. 
+Training and comparison process are the same as CIFAR-10. Results are shown as below:
 
-\begin{table}[h]\scriptsize
+\begin{table}[h]\small
 \centering
 \label{table:cifar100}
-\begin{tabular}{c|c|c}
+\begin{tabular}{c|c}
 \hline
@@
 MKL     & 72.71\%           \\
-RCEC    & 96.96\%           \\
+RCEC    & 77.13\%           \\  %ori: 0.76960,  vote: 0.77050
 FWOT    & -                 \\
 LPBoost & 76.59\%           \\\hline
-Ours    & 77.18\%           \\
+Ours    & 77.72\%           \\  %ori: 0.77170, vote: 0.77160
 \hline
@@
 \subsection{Experiment on Oxford-IIIT-Pet dataset}
+
 The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs. 
-Each categories have about 200 pictures with a large variations in scale, pose and lighting.
+Each categories have about 200 pictures with a large variations in multiple views, such as scale, pose and lighting.
 We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
@@
 MKL                          & 87.13\%           \\
-RCEC                         & 92.41\%           \\
+RCEC                         & 92.11\%           \\          % ori: 92.41
 FWOT                         & 92.90\%           \\			 
 LPBoost                      & 92.73\%           \\\hline
-Ours                         & 92.84\%           \\
+Ours                         & 92.90\%           \\			 % ori: 92.84
 \hline
@@
 \subsection{Post Strategy Selection}
-In this section, we first compare three proposed final post strategy on tree small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}.
+In this section, we first compare three proposed final post strategy on three small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}.
 PASCAL VOC 2007 contrains 6146 images classified into 20 classes, after filtering the multi-label data. 
@@
 Caltech 101 contains a total of 9,146 images, split between 101 distinct object categories and a background category.
+We sample fifty percent data as training data and the others as testing data, repeat 10 times on all three datasets.
 
-Experiment results show that the first strategy outperforms than the others in most cases and never performe under the others. \yanred{Lack Analysis}
+Experiment results show that the first strategy outperforms than the others in most cases and never performes under the others. 
+The reason that the first strategy is better than the second one might because the soft average method would reserve more detail information than the hard voting method.
+Since the recover matrix X contains the outlier rejection information, 
+the last strategy combines the outlier results as a rejection decision operating on the original confidence score matrix, which utlizing more than both the first and second strategy.
 
@@
 Method                       & VOC 2007 &  Flowers 17  & Caltech 101 \\\hline
-Strategy 1                   & 89.56\%  &  96.76\%     &    -        \\\hline
-Strategy 2                   & 89.26\%  &  96.61\%     &    -        \\\hline
-Strategy 3                   & 89.16\%  &  96.75\%     &    -        \\\hline
+Strategy 1                   & 89.60\%  &  96.77\%     &   96.04\%   \\\hline
+Strategy 2                   & 89.41\%  &  96.61\%     &   95.91\%   \\\hline
+Strategy 3                   & 90.10\%  &  96.77\%     &   96.08\%   \\
 \hline
@@
 LPBoost                      & 90.54\%           \\\hline
-Ours                         & 89.57\%           \\
+Ours                         & 90.10\%           \\
 \hline
@@
 
-\begin{table}[h]\scriptsize
+\begin{table}[h]\small
 \centering
@@
 LPBoost & 97.24\% \\\hline
-Ours &  96.62\% \\
+Ours   &  96.74\% \\
 \hline

### 2016-09-11 ensemble_clustering.tex
revise body part

--- 2016-09-10 ensemble_clustering.tex
@@
 
+\def\bA{{\bf A}}
+\def\bB{{\bf B}}
+\def\bN{{\bf N}}
+\def\bM{{\bf M}}
 \def\bD{{\bf D}}
@@
 \def\etc{\emph{etc}}
+\def\wrt{\emph{w.r.t}}
 \def\ie{\emph{ie}}
@@
 
-%\author{AAAI Press\\
-%Association for the Advancement of Artificial Intelligence\\
-%2275 East Bayshore Road, Suite 160\\
-%Palo Alto, California 94303\\
-%}
+\author{AAAI Press\\
+Association for the Advancement of Artificial Intelligence\\
+2275 East Bayshore Road, Suite 160\\
+Palo Alto, California 94303\\
+}
 
@@
 For example, for image data, one can extract hand-crafted features such as scale-invariant feature transform
-(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevskynips2012imagenet}.
+(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevsky2012imagenet}.
 Text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
@@
 \section{The Proposed Approach}
-We first elaborate the formulation of our ORLF algorithm.
-Then we show the details about how to use augmented Lagrangian multiplier (ALM) to solve the $\ell_{1,2}$ objective function.
-Finnaly we introduce our post process strategy to convert the recovered matrix X in \ref{eq:mf_l21} to the final predicted label.
+In this section, we first elaborate the formulation of ORLF.
+Then we show the details of the application of ALM to extend matrix factorization to handle $\ell_{1,2}$ loss.
+Finally we introduce our post-process strategy to convert the recovered label matrix to final predictions.
 
-\subsection{Problem Formulation}
-Suppose there are n testing instances, we denote each instance as a variable $x_i{\in}\dsR^{d}(1{\leq}i{\leq}n)$.
-Assuming we have already training m classifiers, $f_1(x), f_2(x), ...
-f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m $，represent the result of j-th classifier on i-th testing instance.
-Our goal is to fusion these predicted confidence score vectors.
-Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance.
-Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
-The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown in \ref{eq:mf_l21}.
-The k of the low rank constraint in (\ref{eq:mf_l21}) is the number of class in recoginition task.
-
-\begin{figure}[h]
+\begin{figure}[htp]
 \centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
@@
 
-\subsection{ALM Optimization}
-Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
-We apply ALM to optimize the nonsmooth objective function efficiently, desccribed as bellow:
+\subsection{Problem Formulation}
 
-By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:mf_l21}) as below:
+Suppose there are $n$ testing instances and $\calC$ classes.
+We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
+Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
+Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times m}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
+Let $\bL = [ \bL_1, \bL_2, ..., \bL_\calC ]$.
+On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
+On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which can be computed by
+$$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
+Thus, the proposed model can be written as below:
+\begin{align}\label{eq:l12_rankconstraint}
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
+  \st ~&~ \rank(\bX) = p   ,
+\end{align}
+\noindent
+where $\bX$ is the underlying low rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
+and $p$ is a scalar.
+In our setting, to preserve the consistency among various classifiers, we set $p = \calC$.
 
+It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
+We hence transform the original problem as a matrix factorization formulation as below:
+\begin{align}\label{eq:l12_mf}
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
+             ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
+\end{align}
+\noindent
+Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a nonsmooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
+In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).
+
+\subsection{Optimization Based on ALM}
+
+Most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth $\ell_{1,2}$ loss used in Problem~(\ref{eq:l12_mf}).
+In this section, we present an ALM based algorithm to optimize Problem~(\ref{eq:l12_mf}).
+
+By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
 \begin{align}\label{eq:mf_l21_constrained}
@@
   \st             ~&~ \bE = \bL - \bX   \nonumber \\
-                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}
+                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
 \end{align}
-The augmented Lagrangian function of Problem~(\ref{eq:mf_l21}) is as below
+The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
 \begin{align}\label{eq:lagrangian_l21}
-  \calL = & || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
+  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle      \nonumber \\
+                                    & + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
 \end{align}
 \noindent
-where $\bX = \bU \bV$,
-and $\blambda \in \dsR^{MK \times N}$ are the Lagrangian multipliers (or dual variables).
-Then we could update $\bX$ and $\bE$ alternatively.
+where $\bX = \bU \bV$, $\mu$ is a scalar,
+and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
+Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
+Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.
 
-Specifically, to update $\bX$, we consider the following problem:
-\begin{align}\label{eq:problem_X}
-  \min_{\bX} ~&~ \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
-\end{align}
-Problem~(\ref{eq:problem_X}) includes a smooth loss function w.r.t.
-$\bX$, thus can be solved by a standard matrix factorization method, such as~\cite{yanijcai2015scalable,tanicml2014riemannian,vandereyckensiamjo2013low}.
-
-Problem~(\ref{eq:problem_X}) can also be rewritten as below
-\begin{align}\label{eq:problem_X2}
-  \min_{\bX} ~&~ \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
-             ~&~ - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
-  \st.       ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
+In particular, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
+\begin{align}\label{eq:langrangian_wrt_X}
+  \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
+              = & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
+                & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
+              = & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
+              = & || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
 \noindent
-We can obtain the final problem w.r.t. $\bX$:
-\begin{align}\label{eq:problem_X3}
-  \min_{\bX} ~&~ || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2   \nonumber \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK}   .
+where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
+Hence, we derive the following subproblem \wrt. $\bX$:
+\begin{align}\label{eq:subproblem_wrt_X}
+  \min_{\bX} ~&~ || \bM - \bX ||_F^2    \nonumber \\
+  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}   .
+\end{align}
+Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt.
+$\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}%\footnote{\yanred{Code available at~\url{http://www.unige.ch/math/vandereycken/matrix_completion.html}}}.
+
+Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
+\begin{align}\label{eq:subproblem_wrt_E}
+  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
+              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
 \noindent
-There are a number of optimization algorithms for Problem~(\ref{eq:problem_X3}), such as LRGeomCG\footnote{\yanred{Code available at~\url{http://www.unige.ch/math/vandereycken/matrix_completion.html}}}.
-
-To update $\bE$, we consider the following problem:
-\begin{align}\label{eq:problem_E}
-  \yanred{
-  \min_{\bE} ~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2   .
-  }
+where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
+We thus obtain the subproblem \wrt. $\bE$ as below:
+\begin{align}\label{eq:subproblem_wrt_E}
+  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 \\
 \end{align}
 \noindent
-Similarly, we could reformulate the above problem as below:
-\begin{align}\label{eq:problem_E2}
-  \min_{\bE} & \frac{2}{\mu} || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2    .
-\end{align}
-\noindent
-Let $\bY = \bL - \bX + \frac{\blambda}{\mu}$.
-The above problem can be efficiently solved by the following column-wise soft-thresholding operator:
+The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
 \begin{align}\label{eq:column_wise_soft_thresholding}
@@
     \begin{aligned}
-      & \zerocolumn,~\text{if}~ ||\bY_{i}||_2 \leq \alpha   \\
-      & \bY_{i} - \frac{\alpha \bY_{i}}{|| \bY_{i} ||_2},~\text{otherwise,}
+      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
+      & \bY_{i} - \frac{\alpha \bY_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
     \end{aligned}
@@
 \noindent
-where $\bE_{i}$ and $\bY_{i}$ denote the $i$-th column of $\bE$ and $\bY$,
+where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bY$,
 and $\alpha = \frac{2}{\mu}$.
 
-We summarize the proposed algorithm for Problem~(\ref{eq:mf_l21_constrained}) in Algorithm~\ref{alg:alm_mf}.
 \begin{algorithm}[h!]
@@
 
-    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:problem_X3}) via LRGeomCG.
+    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
 
@@
 \begin{proof}
-    Considering the $(k+1)$-th iteration of Algorithm~\ref{alg:alm_mf}, we have the following development:
-    \begin{align}\label{eq:proof1}
-      & \calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k})   \nonumber \\
-      & = || \bE_{k+1} ||_{1,2} + \langle \blambda_{k}, \bL - \bX_{k+1} - \bE_{k+1} \rangle + \frac{\mu}{2} || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2         \nonumber \\
-      & = || \bE_{k+1} ||_{1,2} + \frac{\mu}{2} [ || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2 + \frac{\mu}{2} \langle \blambda_{k}, \bL - \bx_{k+1} - \bE_{k+1} \rangle + \frac{1}{\mu_{k}^2} || \blambda_k ||_F^2 ] - \frac{1}{2\mu_k} || \blambda_k ||_F^2    \nonumber  \\
-      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \bL - \bX_{k+1} - \bE_{k+1} + \frac{\blambda_k}{\mu_k} ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
-      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \frac{1}{\mu_k} [ \mu_k (\bL - \bX_{k+1} - \bE_{k+1}) - \blambda_k ] ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
-      & = || \bE_{k+1} ||_{1,2} + \frac{1}{2\mu_k} ( || \blambda_{k+1} || - || \blambda_{k} ||_F^2 )   .
-    \end{align}
-    \noindent
-    Let $f^*$ denote a local optimal objective function value, which enables the following development:
-    \begin{align}\label{eq:proof2}
-      f^* & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2}   \nonumber  \\
-          & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} || \bL - \bA - \bE ||_F^2   \nonumber \\
-          & \geq \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} ||  \bL -
-          \bX - \bE ||_F^2     \nonumber \\
-          & = \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2)   .
-    \end{align}
-    \indent
-    Regarding that $\mu_{k} = \rho \mu_{k+1}$ where $\rho > 1$, and the sequence $\{ \blambda_k \}$ is bounded, we derive that
-    $\frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2) \rightarrow 0$ when $k \rightarrow +\infty .$
-    Therefore, when $k \rightarrow +\infty$, we obtain $\min_{\bE, \bA = \bU \bV} = || \bE^* ||_{1,2} \leq f^*$.
-    On the other hand, by Algorithm~\ref{alg:alm_mf}, $\bL - \bX_{k+1} - \bE_{k+1} = \mu_k^{-1} (\blambda_{k+1} - \blambda_{k}) .$
-    As $k \rightarrow +\infty$, we have $\bL - \bX^* - \bE^* \rightarrow +\infty  ,$
-    which indicates that $(\bX^*, \bE^*)$ is a stationary point.
-    This completes proof.
+  The proof can be found in Appendix A.
 \end{proof}
+%\begin{proof}
+%    Considering the $(k+1)$-th iteration of Algorithm~\ref{alg:alm_mf}, we have the following development:
+%    \begin{align}\label{eq:proof1}
+%      & \calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k})   \nonumber \\
+%      & = || \bE_{k+1} ||_{1,2} + \langle \blambda_{k}, \bL - \bX_{k+1} - \bE_{k+1} \rangle + \frac{\mu}{2} || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2         \nonumber \\
+%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu}{2} [ || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2 + \frac{\mu}{2} \langle \blambda_{k}, \bL - \bx_{k+1} - \bE_{k+1} \rangle + \frac{1}{\mu_{k}^2} || \blambda_k ||_F^2 ] - \frac{1}{2\mu_k} || \blambda_k ||_F^2    \nonumber  \\
+%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \bL - \bX_{k+1} - \bE_{k+1} + \frac{\blambda_k}{\mu_k} ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
+%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \frac{1}{\mu_k} [ \mu_k (\bL - \bX_{k+1} - \bE_{k+1}) - \blambda_k ] ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
+%      & = || \bE_{k+1} ||_{1,2} + \frac{1}{2\mu_k} ( || \blambda_{k+1} || - || \blambda_{k} ||_F^2 )   .
+%    \end{align}
+%    \noindent
+%    Let $f^*$ denote a local optimal objective function value, which enables the following development:
+%    \begin{align}\label{eq:proof2}
+%      f^* & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2}   \nonumber  \\
+%          & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} || \bL - \bA - \bE ||_F^2   \nonumber \\
+%          & \geq \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} ||  \bL -
+%          \bX - \bE ||_F^2     \nonumber \\
+%          & = \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2)   .
+%    \end{align}
+%    \indent
+%    Regarding that $\mu_{k} = \rho \mu_{k+1}$ where $\rho > 1$, and the sequence $\{ \blambda_k \}$ is bounded, we derive that
+%    $\frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2) \rightarrow 0$ when $k \rightarrow +\infty .$
+%    Therefore, when $k \rightarrow +\infty$, we obtain $\min_{\bE, \bA = \bU \bV} = || \bE^* ||_{1,2} \leq f^*$.
+%    On the other hand, by Algorithm~\ref{alg:alm_mf}, $\bL - \bX_{k+1} - \bE_{k+1} = \mu_k^{-1} (\blambda_{k+1} - \blambda_{k}) .$
+%    As $k \rightarrow +\infty$, we have $\bL - \bX^* - \bE^* \rightarrow +\infty  ,$
+%    which indicates that $(\bX^*, \bE^*)$ is a stationary point.
+%    This completes proof.
+%\end{proof}
 

### 2016-09-11 RLF_MF.tex
Beta4.0, near completion, problem :title, frame work chart, syntax details.

--- 2016-09-11 ensemble_clustering.tex
@@
 
-%\title{Outlier Reject for Late Fusion on Visual Recognition}
-\title{Robust Late Fusion Based on Matrix Factorization}
-
+\title{Consistent Late Fusion for Visual Recognition}
+%% Efficient
 \author{AAAI Press\\
@@
 % First: A big picture of the scenario which we would consider
-In many real world applications, data can be represented in multiple ways/features, which would describe various characteristics of data.
-Many works have shown that it could often improve the performance to make use of these features together.
+In many real world applications, data can be represented in multiple ways or multi-view features,
+in order to describe various characteristics of data.
+In this way, it could often improve the prediction performance by taking advantage of these feature together.
 % Second: what BIG problem would we like to solve?
-Late fusion, which linearly combines the predictions of multiple features, is a commonly used approach to generate the final decision for a test instance.
+Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
 % Third: specify the detailed problem: find a precise position for our paper
-However, it is ubiquitous that different features would dispute on some data, leading to the requirement of outlier rejection for late fusion algorithms.
+However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
+There is a requirement of outlier rejection for late fusion algorithms.
 % Fourth: general introduction of our method
-In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources, which could
-relieve the performance degeneration caused by the controversy of multiple features on test data.
+In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources, 
+which could avoid the performance degeneration caused by the controversy of multiple features on test data.
 % Some unvalued sentence(s)
@@
 %背景 多model融合
-Feature extraction, which transforms raw data into numerical features, is a prerequisite for most real world applications.
+Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
 There are often multiple ways to generate numerical features from raw data.
-For example, for image data, one can extract hand-crafted features such as scale-invariant feature transform
-(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevsky2012imagenet}.
-Text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
-%Videos can be represented by Dense Trajectories~\cite{Wang2011Action}, CNNs~\cite{xucvpr2015discriminative}, \etc.
-%\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}
-Each category of features tends to capture a specific characteristics of data.
-A model trained on an individual feature could be biased and hence obtains an unsatisfactory performance.
-Existing works have investigate the performance improvement by combining multiple features in real world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.
-
-%Image or video data in the real world can be represented in multiple features.
-%For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
-%Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}.
-%Each feature contains rich information of real data, which can not capture all views of our data.
-%A single classifier model will bias on some characteristics of training data based on different features.
-%It can significantly improve the performance by combining multiple features together and capturing more views on data.
-
-%%A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}.
-Fusion techniques can be grouped into two types which are early fusion and late fusion, early fusion fusion multiple models in the feature level, late fusion merge the result of each classifier.
+For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
+(SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
+or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevskynips2012imagenet}.
+Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
+Each category of features tends to capture some specific characteristics of data,
+such as textures of images and frequencies of text data.
+When building a prediction model, the model trained on one kind of feautures could be biased and hence may incur unsatisfactory performance.
+Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.
 
 %% late fusion is a common sigle model -> single feature, 介绍late fusion
-Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from each individual feature.
-A commonly used method is to learn weights for predictions of each feature and linearly combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
+Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
+A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
 Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
@@
 
-%Late fusion is a common method to make the combination of different features.
-Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
-%A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation.
-Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
-%\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}.
-}
-%%这提了Gao，下一段也提了Gao这样好么？
-
-%%In the early fusion, a linear combination or more complex functions,eg.
-3D convolution , of different features is utilized to capture inner correlation bettwen each model, such as \cite{Feichtenhofer2016Convolutional}.
-A more simple but effective method in early fusion is to calculate multiple kernel matrix from different features and then average them together to train a SVM classifier.Another fusion technique is late fusion, which train classifiers of seperate features and then fuses the results based on the predicted scores, such as \cite{gehler2009feature} learns a linear combination on decision values of individual features to boost the performance of single model.
-%%Most previous works in late fusion focus on how to learn weights on different models, (disadvantage?)
-
-%% 不同的features 会有意见不同的时候，具体 outlier rejection，might [Gao low rank sparse loss, but the nuclear norm
-%% scale poorly , expensive single vd(SVDs) present of , the other way of low MF foucs on least square smooth function
-%% least square loss is sensitive to outlier
-%% it's unclear to extend MF to nonsmooth function .
-%% In this paper we proposed a
-%%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
-
 To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
 As for outlier detection, as shown in Figure~\ref{fig:framework}, we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
-%which can be represented in the following:
-%\begin{align}\label{eq:typical_mc}
-%  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
-%  \st        ~&~ \rank(\bX) \leq k  ,
-%\end{align}
-%\noindent
-%$L$ is the indicator matrix, represent the label indicator matrix in our vision recoginition case.
-%X is a low rank matrix recovered from L.
-Rank function measures the rank of a matrix.
-$|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
-%Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint.
-For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
-%\begin{align}\label{eq:mf_l21}
-%  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-%  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
-%\end{align}
-%\noindent
 Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
@@
 \begin{itemize}
-  \item We propose an efficient late fusion algorithm based on matrix factorization.
+  %\item We propose an efficient late fusion algorithm based on matrix factorization.
+  \item We formulate the late fusion problem as robust matrix recovery problem based on matrix factorization.
   \item We extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
@@
 
-%A single clustering result could be inaccurate, so some researchers study ensemble clustering methods to boost the performance,
-%such as the algorithms proposed in~\cite{yiicdm2012robust,gaoijcai2016robust}, to name a few.
+\section{Related Work}
+%% Matrix factorization
+%% Fusion Methods
 
-\iffalse
-The key aim of matrix completion based methods is to detect the anomalous clusters (bad partitions/assigments) and reconstruct the real assignments,
-which is shown in Figure~\ref{fig:anomalous_cluster}.
-A typical formulation of matrix completion based methods then can be written as below:
-\begin{align}\label{eq:typical_mc}
-  \min_{\bX} ~&~ || \bX - \bL ||_2^2   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k  ,
-\end{align}
-\noindent
-where $k$ is a pre-defined rank constraint,
-and $\bL \in \dsR^{N \times MK}$.
-Here we denote $M$ and $K$ as the number of single clustering assignments and the number of clusters, respectively.
-However, the least square loss used in matrix completion is sensitive to the abnormal errors, namely outliers, the not appropriate to capture the anomalous assignments.
-The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{1,2}$ norm on $\bX$, which is as follow
-\begin{align}\label{eq:mc_l21_gaospaper}
-  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{1,2}   \nonumber \\
-  \st        ~&~ \rank(\bX) \leq k   ,
-\end{align}
-\noindent
-where $|| \bX ||_{1,2} = \sum_{j = 1}^{MK} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
-which would make $\bX$ column-wise sparse (beware the direction of the computation of the $\ell_{1,2}$ norm, more details in~\cite{nienips2010efficient}).
-Nevertheless, it does not consider the outliers in their loss function.
-In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{1,2}$ is equivalent to $|| \bX - \bO ||_{1,2}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
-\fi
+MKL based method is a simple but efficient way to combine different features for multi-model fusion,
+and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
+In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel. 
+In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
+In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
+In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
+which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
+In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values, 
+which learns the weights, thresholding and smoothing parameters in a joint framework.
+However, all these mkl based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.
 
-\section{Related Work}
-%% RPCA robust
-%% Matrix F...
-%%
-
-Matrix factorization has attracted increasing attention recently,
-and many manifold optimization based algorithms have been proposed by exploiting the manifold geometry.
+Our proposed late fusion algorithm is based on matrix factorization,
+which has attracted increasing attention recently.
+Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry.
 Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
@@
 
-%%RPCA Methods
-%Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix.
-This could also be used in our late fusion application to remove outlier column in the indicator matrix L.
-\cite{wright2009robust} instroduce a representative Robust PCA algorithm, and \cite{ye2012robust} propose a rank minimization method optimize the RPCA to fuse the predicted confidence scores of multiple models.
-\yanred{other RPCA and disadvantage}
-
-MKL~\cite{Rakotomamonjy2008Simplemkl} based method is a simple but efficient way to combine different features for late fusion.
-\cite{vedaldi2009multiple} use MKL to learn an optimal combination of exponential ${\chi}^2$.
-\cite{gehler2009feature} introduce two boosting approaches inspired by the MKL.
-\cite{natarajan2012multimodal} combines these diverse features using a two-step strategy employing MKL and late score fusion methods.
-\cite{lai2015learning} proposed a late fusion method that determines the optimal fusion weights for each sample.
-\yanred{\cite{xuiccv2013feature} learns the weights, thresholding and smoothing parameters in a joint framework to combine the decision values.
-Copy from Abs}.
-\yanred{However, MKL based method...}
-
 %% Latent Fusion,
@@
 \section{The Proposed Approach}
-In this section, we first elaborate the formulation of ORLF.
-Then we show the details of the application of ALM to extend matrix factorization to handle $\ell_{1,2}$ loss.
+
+%We first elaborate the formulation of our proposed algorithm. 
+We first elaborate the formulation of our proposed algorithm,
+which regards the late fusion problem as a robust matrix recovery problem.
+%Then we show the details about how to use augmented Lagrangian multiplier (ALM) to solve the $\ell_{1,2}$ objective function.
+And then we present the details of using ALM extending matrix factorization to handle $\ell_{1,2}$ loss.
 Finally we introduce our post-process strategy to convert the recovered label matrix to final predictions.
 
-\begin{figure}[htp]
+\begin{figure}[h]
 \centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
-\caption{something}\label{fig:framework}
+\caption{Frame Work}
+\label{fig:framework}
 \end{figure}
@@
 Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt.
-$\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}%\footnote{\yanred{Code available at~\url{http://www.unige.ch/math/vandereycken/matrix_completion.html}}}.
+$\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
 
 Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
-\begin{align}\label{eq:subproblem_wrt_E}
+\begin{align}\label{eq:subproblem_wrt_E_1}
   \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
@@
 We thus obtain the subproblem \wrt. $\bE$ as below:
-\begin{align}\label{eq:subproblem_wrt_E}
+\begin{align}\label{eq:subproblem_wrt_E_2}
   \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 \\
@@
 
-\begin{theorem}\label{theorem:alm_convergence}
+\begin{theorem}
+\label{theorem:alm_convergence}
   Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
@@
 \begin{proof}
+\label{proof:proof_AA}
   The proof can be found in Appendix A.
 \end{proof}
-%\begin{proof}
-%    Considering the $(k+1)$-th iteration of Algorithm~\ref{alg:alm_mf}, we have the following development:
-%    \begin{align}\label{eq:proof1}
-%      & \calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k})   \nonumber \\
-%      & = || \bE_{k+1} ||_{1,2} + \langle \blambda_{k}, \bL - \bX_{k+1} - \bE_{k+1} \rangle + \frac{\mu}{2} || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2         \nonumber \\
-%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu}{2} [ || \bL - \bX_{k+1} - \bE_{k+1} ||_{F}^2 + \frac{\mu}{2} \langle \blambda_{k}, \bL - \bx_{k+1} - \bE_{k+1} \rangle + \frac{1}{\mu_{k}^2} || \blambda_k ||_F^2 ] - \frac{1}{2\mu_k} || \blambda_k ||_F^2    \nonumber  \\
-%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \bL - \bX_{k+1} - \bE_{k+1} + \frac{\blambda_k}{\mu_k} ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
-%      & = || \bE_{k+1} ||_{1,2} + \frac{\mu_k}{2} || \frac{1}{\mu_k} [ \mu_k (\bL - \bX_{k+1} - \bE_{k+1}) - \blambda_k ] ||_F^2 - \frac{1}{2\mu_k} || \blambda_k ||_F^2   \nonumber \\
-%      & = || \bE_{k+1} ||_{1,2} + \frac{1}{2\mu_k} ( || \blambda_{k+1} || - || \blambda_{k} ||_F^2 )   .
-%    \end{align}
-%    \noindent
-%    Let $f^*$ denote a local optimal objective function value, which enables the following development:
-%    \begin{align}\label{eq:proof2}
-%      f^* & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2}   \nonumber  \\
-%          & = \min_{\bX + \bE = \bL, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} || \bL - \bA - \bE ||_F^2   \nonumber \\
-%          & \geq \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \langle \blambda_k, \bL - \bX - \bE \rangle + \frac{\mu_k}{2} ||  \bL -
-%          \bX - \bE ||_F^2     \nonumber \\
-%          & = \min_{\bE, \bX = \bU \bV} || \bE ||_{1,2} + \frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2)   .
-%    \end{align}
-%    \indent
-%    Regarding that $\mu_{k} = \rho \mu_{k+1}$ where $\rho > 1$, and the sequence $\{ \blambda_k \}$ is bounded, we derive that
-%    $\frac{1}{2\mu_k} (|| \blambda_{k+1} ||_F^2 - || \blambda_{k} ||_F^2) \rightarrow 0$ when $k \rightarrow +\infty .$
-%    Therefore, when $k \rightarrow +\infty$, we obtain $\min_{\bE, \bA = \bU \bV} = || \bE^* ||_{1,2} \leq f^*$.
-%    On the other hand, by Algorithm~\ref{alg:alm_mf}, $\bL - \bX_{k+1} - \bE_{k+1} = \mu_k^{-1} (\blambda_{k+1} - \blambda_{k}) .$
-%    As $k \rightarrow +\infty$, we have $\bL - \bX^* - \bE^* \rightarrow +\infty  ,$
-%    which indicates that $(\bX^*, \bE^*)$ is a stationary point.
-%    This completes proof.
-%\end{proof}
 
-\subsection{Final Post Process}
-As we recover the low rank matrix X from the label assignment matrix L.
-Intuitively, there is two possible way to get our final fusion results from X.
-Although L is a 01 matrix obtain by hard label, we could treat it as a soft score matrix, which the position of highest score represent the most possible label predicted by classifiers.
-X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L.
-Two possible post way to processing X are described as bellow:
+\subsection{Post Process}
+As we recover the low rank matrix $\bX$ from the label assignment matrix $\bL$,
+it needs a post process to make the predicted label for each testing data.
+Intuitively, there might be several possible ways to select as below: 
 \begin{itemize}
-  \item Average the score matrixs, each of which is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X.
-Then we got $X^*$, a N*K score matrix.
-we make the position of the highest value in each rows as the predicted label of the i-th instance.
-  \item Seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum.
-For each matrix $Y_j$, we obtain a column vector by selecting the index of the highest score in each row.
-Then we use voting from M index matrix to select the final label.
+  \item A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
+		The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
+  \item For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ is the index of the highest value in the $i$-th row of $\bX_j$.
+  		Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
+  		Finally, we choose the label with the most votes to be the prediction results.
+  \item $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
+  		As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
+  		The similar process as the first strategy is applied to the above results, which predictes the final label.
 \end{itemize}
-According to the experiments, the first strategy outperform than the second one, we choose the first one as our final post process of fusion method.
+According to the experiments, the last strategy outperforms than the others.
+So We choose the last one as the post process for fusion method and analyse inner reasons during experiment section.
 
-\iffalse
-\section{An Option on Loss Function: Max Margin}
-In fact, the assignments $\bL$ contains only $0/1$ values (discrete ordinal values).
-This fits the setting in~\cite{yanijcai2015scalable} very much.
-It could be a contribution, since maximum margin loss achieves better performance on discrete ordinal values.
-\yanred{Note: we may leave this extension as a journal?}
+\section{Empirical Studies}
 
-\section{Another Option on Loss Function: $\ell_{1,2}$ to $\ell_1$ loss}
-$\ell_{1,2}$ loss could be difficult to optimize.
-A simple way is to replace $\ell_{1,2}$ to $\ell_1$, which would be much easier.
-\fi
+In this section, we first visualize the results of our approach on one synthetic dataset. 
+Then we evaluate the perfomance on eight publicly available real-world data sets,
+UCF101~\cite{soomro2012ucf101}, CIFAR-10,100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet dataset~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
+The strategy analysis for post process is detailed in the last subsection.
 
-\section{Experiments}
-We visualize the results of our approach on one synthetic and evaluate the perfomance on five publicly available datasets : UCF101 human action dataset~\cite{soomro2012ucf101}, Cifar10~\cite{krizhevsky2009learning} dataset, Oxford-IIIT-Pet dataset~\cite{parkhi12a} and Pascal Sentences dataset.
-In UCF101 dataset, features are extracted from `fc6' layer of C3D model\cite{tran2015learning}, `pool5/7x7\_s1' layer from GoogleNet model\cite{szegedy2015going}, `pool5' layer of Residual Network model~\cite{he2015deep}, `fc6' layer of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet} and Two-Stream Convolutional Networks~\cite{simonyan2014two}.
-Given a video, we sample 25 frames with equal temporal spacing between them as described in \cite{simonyan2014two} volumes for C3D).
-Following the same produce in \cite{tran2015learning} and \cite{simonyan2014two}, the features for the whole video are then calculated by averaging the features across the sampled frames.
-In Cifar10 dataset, features are extracted from `global\_pool' layer of the ResnNt-20,32,44,56,110 models\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164 models\cite{he2016identity}.
-In all other dataset, features are extracted among `fc6' layer of VGG network~\cite{chatfield2014return} and AlexNet network~\cite{krizhevsky2012imagenet}, `pool5/7x7\_s1' layer from GoogleNet network~\cite{szegedy2015going}, `pool5' layer of Residual network~\cite{he2015deep}.
-To be noted, all our cnn features are extracted using Caffe\cite{jia2014caffe}, a deep learning framework.
+%Details on feature extraction for each dataset are described in the second subsection.
+%, and the confidence scores are set as outputs of LIBLINEAR. 
+%Then we put the confidence scores as the input X of our alogrithm.
 
-LIBLINEAR\cite{fan2008liblinear} is adopted for our classification toolbox, the confidence scores are generated from the outputs of LIBLINEAR.
-Then we put the confidence scores as the input into our alogrithm.
+Five state-of-the-art fusion methods are compared with our proposed alogrithm : 
+(1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization. 
+(2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} to train our MKL model.
+(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}. The core alogrithm in RCEC can be modified to recover X from L in ~\ref{eq:l12_mf}, and the post process is same as our method. 
+(4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
+The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
+(5)LPBoost\cite{gehler2009feature}. In this method, a variant linear combination are applied to multiple classifiers to boost performance.
 
-Five state-of-the-art fusion methods are compared with our proposed alogrithm : (1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers.
-We use $L_2$ norm on each classifiers for normalization.
-(2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
-We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/} ; \url{https://github.com/minghen/liblinear-mkl}} to train out MKL model.
-(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust} (4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
-The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
-(5)LPBoost\cite{gehler2009feature}.
-In this method, a variant linear combination are applied to multiple classifiers.
-
-The parameter $\mu$ are selected from {0.1, 1, 5, 10}, $\rho$ are select from {1.01, 1.05, 1.1} in all our experiments. For SVM, we use the default parameters set in the LIBLINEAR.
+The parameter $\mu$ is selected from \{0.1, 1, 5\} and $\rho$ is select from \{1.01, 1.05, 1.1\} in all our experiments.
+It shows slight performance change during selecting different parameters.
+LIBLINEAR\cite{fan2008liblinear} is adopted for our basic classification toolbox.
+The parameters are set as default in LIBLINEAR and liblinear-mkl, unless otherwise specified. 
+For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from \{0.01,1,2,4,6,...,20\} and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
+For FWOT, the smoothing parameter candidates are \{0.5, 0.6, ...
+, 0.9\} and the parameter C in is selected from \{$10^{-4},10^{-2},...,10^{4}$\} according to cross-validation, which is same in~\cite{xuiccv2013feature}.
+For LPBoost, we use cross-validation to pick up the best $\nu$ from \{0.5,0.6,0.7,0.8,0.9\} suggested by~\cite{xuiccv2013feature}.
 
@@
 
-In synthetic experiments, we set N = 320, M = 15, K = 20, randomly generate N instances with K kinds of labels.
-We randomly change 30\% instances' labels, repeat M times to get M classifiers' results.
-By appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure \ref{fig:ensemble_cluster}.
-Each subfigure contrains $N\times M$ small narrow blocks, which visualized in diverse colors according to their different label.
-The first picture~\ref{subfig:gt_pdf}, show the ground truth and copied M times.
-And M noised classifiers' results are pictured as~\ref{subfig:er_pdf}.
-After we recover the low rank matrix from the noised matrix by using ORLF late fusion method, we visualize it as~\ref{subfig:er_pdf}.
+In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to randomly generate $n$ instances with $\calC$ kinds of labels for each instance. 
+Then we randomly permute $40\%$ instances' labels, repeat fifteen times to get $m = 15$ classifiers' results. 
+After appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure~\ref{fig:ensemble_cluster}.
+Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different label. 
+The first picture~\ref{subfig:gt_pdf} show the ground truth label repeating M times. 
+And $m$ noised classifiers' results are pictured as~\ref{subfig:er_pdf}. 
+We recover the low rank matrix $\bX$ from the noised matrix by using our late fusion method, which is visualized as~\ref{subfig:er_pdf}.
 
@@
 
-\subsection{Experiment on Oxford-IIIT-Pet dataset}
-The Oxford-IIIT-Pet dataset~\cite{parkhi12a} contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
-Each categories have about 200 pictures with a large variations in scale, pose and lighting.
-We extract features from AlexNet,VGG,GoogleNet,ResNet, totally eight diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50, ResNet101 and ResNet152).
+\begin{table*}[t]\small
+\centering
+\begin{tabular}{c|c|c|c|c|c}
+\hline
+Method              & UCF-101  & CIFAR-10 & CIFAR-100 & Oxford-IIIT-Pet & PASCAL VOC 2007      \\\hline
+ASF                 & 86.78\%  & 94.21\%  & 76.91\%   & 92.46\%         &   90.51\%            \\
+MKL                 & 85.38\%  & 94.15\%  & 72.71\%   & 87.13\%         &   85.82\%            \\
+RCEC                & 86.60\%  & 94.99\%  & 77.13\%   & 92.11\%         &   90.92\%            \\ 
+FWOT                & -        & -        & -         & 92.90\%         &   90.81\%            \\    %FWOT ***
+LPBoost             & 86.24\%  & 94.88\%  & 76.59\%   & 92.73\%         &   91.42\%            \\\hline
+Ours                & 89.03\%  & 95.11\%  & 77.72\%   & 92.90\%         &   90.98\%            \\ 
+\hline
+\end{tabular}
+\caption{Mean Accuracy on Each Dataset}
+\label{table:total_acc}
+\end{table*}
 
-We randomly sample fifty percent pictures as our training data and the others as our testing data, repeat ten times.
-We first traing svm on each seperate features by liblinear and fuse by our ORLF methods, comparison result are shown as below:
+\begin{table*}[t]\small
+\centering
+\begin{tabular}{c|c|c|c|c|c|c}
+\hline
+Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 & Oxford Flowers 17 \\\hline
+RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         & 3.14   \\ 
+FWOT                & $\infty$   & $\infty$  & $\infty$   & $\geq$ 1e4      &   $\approx$ 9e3 & 229.0  \\
+LPBoost             & 110.81     & 72.45     & $\geq$ 1e4 & 43.67           &   7.46          & 0.26   \\\hline
+Ours                & 421.23     & 5.384     &   lack     & 76.16           &   16.21         & 1.62   \\ 
+\hline
+\end{tabular}
+\caption{Time Consumption on Each Dataset}
+\label{table:total_time}
+\end{table*}
+
+\subsection{Feature Extraction}
+We describe the details of the feature extraction for each dataset we use. 
+All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
+
+In UCF101 dataset, five different features are extracted from the following:
+\begin{itemize}
+  \item `fc6' of C3D~\cite{tran2015learning}
+  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+  \item `pool5' of ResNet-152~\cite{he2015deep}
+  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
+\end{itemize}
+Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
+All models we used are public available on Internet. %% provided by authors.
+
+In Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,110,164 models~\cite{he2016identity}. 
+One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}.
+Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers), trained the same in~\cite{he2015deep}
+Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}} before extracting features.
+In Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of pre-activation ResNet-20,32,44,56,110,164 models, following the same training process as in~\cite{he2015deep,he2016identity}.
+
+In all other experiments, eight different features are extracted from the following:
+\begin{itemize}
+  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
+  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
+  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
+\end{itemize}
+We use the offical pre-trained model provided by Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}.
+For above eight models, we simply extract features with no extra operation.
+
+\subsection{Real-world Experiments}
+
+In this section, we introduce the details about our experiments on each data set,
+and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
+Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
+`-' means the contrast algorithm does not work due to heavy memory or time consumption, and `$\infty$' means it will take more than one day to complete the corresponding method.
+The time cost of cross-validation in FWOT and LPBoost are not counted.
+
+%\subsubsection{Experiment on UCF 101 dataset}
+For action recognition, we present our results on UCF 101 dataset. 
+UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes. 
+We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos. 
+As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by liblinear.
+Then by appling five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm. 
+Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods. 
+To be noted, FWOT~\cite{xuiccv2013feature} is too slow to train, we didn't show it's result (more than one day).
+
+%\subsubsection{Experiment on Cifar10 dataset}
+
+In CIFAR-10 dataset, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class. 
+There are 50000 training data and 10000 testing data. 
+Fourteen CNN features are extracted from multiple state of the art models. 
+This experiments exhibit the ability of our algorithm to handle large scale data.
+
+As we have 50000 training data and 10000 testing data,
+FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day). 
+LPBoost algorithm needs to create a $nm\times \calC$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.},
+which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab. 
+We also use `-s 2' parameters in liblinear to speedup training process. Results of total six contrast algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+
+%\subsubsection{Experiment on Cifar100 dataset}
+
+CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
+There are 50000 training data and 10000 testing data as CIFAR-10. 
+Twelve CNN features used in this experiment are described in the feature selection section. 
+Training and comparison process are the same as CIFAR-10.
+
+%\subsubsection{Experiment on Oxford-IIIT-Pet dataset}
+
+The Oxford-IIIT-Pet dataset contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs. 
+There are roughly 200 pictures in each category with a large variations in multiple views, such as pose, scale and lighting.
+We randomly sample fifty percent pictures as our training data and the others as testing data.
+And then we train svm on each single feature and fuse the predictions by our proposed method.
+We repeat the sample , training and fusion process five times to get fair results.
+The comparison results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+
+%% VOC07
+PASCAL VOC 2007 is a dataset for object detection and image classification.
+In our experiments, we only use the image level annotation information.
+Since each image may contain more than one label, we filter the multi-label images to obtain 6146 clean data.
+There is similar procesure of sampling, classification and fusion as in Oxford-IIIT-Pet.
+
+\subsection{Post Strategy Selection}
+
+In this section, we compare three proposed post strategies on three small dataset: Wikipedia~\cite{rasiwasia2010new}, Oxford Flowers 17~\cite{nilsback2006visual} and Pascal Sentence~\cite{Li2006One}.
+Wikipedia dataset contains paragraphs of text for each picture,
+and total 2866 image-text pairs are categoried into 10 class, we only use the image label annotation.
+PASCAL VOC 2007 contrains 6146 images classified into 20 classes, after filtering the multi-label data. 
+Oxford Flowers 17 has 17 flower categories with 80 images for each class. 
+Pascal Sentence contains 1000 images annotated by caption information and categoried into twenty classes.
+Fifty percent of data are sampled as training set and the others as testing set, repeat experiments five times on above three datasets.
+
+Experiments show that the first strategy outperforms than the others in most cases and never performes under the others. 
+This might be caused by that the soft average method reserves more detail information than the hard voting method.
+Since the recover matrix X contains the outlier rejection information,
+the last strategy combines the recovered results as a confidence gate operating on the original confidence score matrix.
+It utilizes more robust information than both the first and second strategy.
 
@@
 \centering
-\label{table:oxford_pet}
-\begin{tabular}{c|c}
+\begin{tabular}{c|c|c|c}
 \hline
-Method                       & Mean Accuracy(\%) \\\hline
-ASF                          & 92.46\%           \\
-MKL                          & 87.13\%           \\
-RCEC                         & 92.41\%           \\
-FWOT                         & **                \\
-LPBoost                      & 92.73\%           \\\hline
-Ours                         & 92.84\%           \\
+Method                       & Wikipedia &  Flowers 17  & Pascal Sentence \\\hline
+Strategy 1                   & 47.78\%   &  96.77\%     &   66.40\%       \\\hline
+Strategy 2                   & 47.85\%   &  96.61\%     &   66.20\%       \\\hline
+Strategy 3                   & 49.03\%   &  96.77\%     &   67.20\%       \\
 \hline
 \end{tabular}
-\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
+\caption{Mean Accuracy on Three Strategies}
+\label{table:strategy}
 \end{table}
-
-\subsection{Experiment on UCF 101 dataset}
-For action recognition, we present our results on UCF 101 dataset\cite{soomro2012ucf101}.
-UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
-We use the official split1 described in \cite{soomro2012ucf101}, which have 9573 training videos 3783 testing videos.
-As mentioned above, fives features are provided from the state of the art deep convolution networks, 4096 demitions features in `fc6' layer from C3D, 1028 demitions features in `pool5/7x7\_s1' layer from  GoogleNet, 2048 demitions features in `pool5' layer of ResNet-152, 4096 demitions features in `fc6' layer in Spatial and Temporal Net.
-All models used in UCF-101 are published by their authors.
-
-We use liblinear to train seperate classifiers on each features with the default parameters in liblinear.
-By appling trained classifiers on test data, we can obtain 5 * 20 confidence score for each video.
-After emsenable fusion, we choose the class with highest confidence score as our predicted class.
-Results are shown in \ref{table:ucf101}, in which we illustrate the performance of the best single classifier and compare several fusion method.
-To be noted, FWOT~\cite{xuiccv2013feature} is too slow to train, we didn't show it's result (more than one day).
-
-\begin{table}[h]\small
-\centering
-\label{table:ucf101}
-\begin{tabular}{c|c}
-\hline
-Method                       & Mean Accuracy(\%) \\\hline
-SVM on Temporal Net Features & 86.23\%            \\\hline
-ASF                          & 86.78\%           \\
-MKL                          & 85.38\%           \\
-RCEC                         & 88.29\%           \\
-FWOT                         & -                 \\
-LPBoost                      & 86.24\%           \\\hline
-Ours                         & 88.89\%           \\
-\hline
-\end{tabular}
-\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
-\end{table}
-
-\iffalse
-\subsection{Experiment on PASCAL VOC 2007 dataset}
-PASCAL VOC 2007 is a dataset for object detection and image classification.
-For our experiment we only use the image level annotation information.
-Since each image may contain more than one label, we filter the multilabel images.
-Using the offical split provided by \cite{pascal-voc-2007}, we have 2954 trainval images and 3192 test images with 20 classes after filtration.
-We extract features from AlexNet,VGG,GoogleNet,ResNet, totally seven diffierent CNN features(AlexNet for alexnet and caffenet, VGG for VGG16 and VGG19, ResNet for ResNet50 and ResNet101).
-
-After the procesure of classification and fusion, we got the results as \ref{table:voc}.
-Since in PASCAL VOC 2007 dataset, more classifiers are utilized than UCF101, it's clear that our method achieve significant improvement than single model and a slight improvement than other fusion algorithm.
-
-\begin{table}[!h]\scriptsize
-\centering
-\label{table:voc}
-\begin{tabular}{c|c|c|c}
-\hline
-Method            & Mean Accuracy & Classification Time(s)& Fusion Time \\\hline
-Best Single Model & 88.44\%       &  2.347                &      0    \\\hline
-ASF               & 88.69\%       &  10.2347              &    0.008   \\ % Average
-MKL               &     0 & 00 & 0 \\
-RCEC              &     0 & 0 & 000 \\
-FWOT              &     0 & 0 & 000 \\
-LPBoost           &     0 & 0 & 000 \\\hline
-Ours              & 88.78\%       & 10.2347               & 9.918 \\
-\hline
-\end{tabular}
-\caption{Accuracy and Time cost on VOC2007 dataset}
-\end{table}
-\fi
-
-\subsection{Experiment on Cifar10 dataset}
-In CIFAR-10 dataset~\cite{krizhevsky2009learning}, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
-There are 50000 training data and 10000 testing data.
-Fourteen CNN features are extracted from multiple state of the art models for training svm.
-These features are `global\_pool' layers' features of ResNet-20,32,44,56,110~\cite{he2015deep} and pre-activation ResNet-20,32,44,56,110,164~\cite{he2016identity},  `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}} and `global\_pool' layers' features from two modified network from~\cite{szegedy2015going,chatfield2014return}.
-This experiments show the ability of our ORLF to handle large scale data.\yanred{(how to say)}
-
-As we have 50000 training data and 10000 testing data, FWOT~\cite{xuiccv2013feature} has one step to deal with N*N matrixes, which are excessive to train~(more than one day).
-LPBoost~\cite{gehler2009feature} need to create a $NK\times N$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.}, which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
-the use `-s 2' parameters in liblinear to speedup training training process.
-Results of other contrast algorithms are shown on \ref{table:cifar10}
-
-\begin{table}[h]\scriptsize
-\centering
-\label{table:cifar10}
-\begin{tabular}{c|c|c}
-\hline
-Method  & Mean Accuracy(\%) & Classification Time + Fusion Time(s)\\\hline
-ASF     & 94.21\%           & 55.6 + 0.02                         \\
-MKL     & 94.15\%           & 865.09                              \\
-RCEC    & 94.87\%           & 55.6 + 3.5                          \\
-FWOT    & -                 & -                                   \\
-LPBoost & 94.88\%           & 54.99                               \\\hline
-Ours    & 95.05\%           & 55.6 + 32.1                         \\
-\hline
-\end{tabular}
-\caption{Accuracy and Time cost on cifar10 dataset}
-\end{table}
-
-\iffalse
-\subsection{Experiment on Oxford Flowers}
-Oxford Flowers 17 dataset~\cite{nilsback2006visual} havs 17 flower categories with 80 images for each class.
-There are three predefined splits training set with 680 images, validation set with 340 images and testing set 340 images.
-2048 dimetions `pool5' features from ResNet-50,101,152 proposed in \cite{he2015deep} and 4096 dimetions `fc6' features from CaffeNet,AlexNet proposed in \cite{krizhevsky2012imagenet} are used for linear SVM.
-The models are download from Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}, with no finetuning on the current dataset.
-
-We use the predefined training set and validation set as our training data, trained on liblinear with default parameters.
-For LPBoost Methods, we use 5 fold cross validation to select the best hyperparmeter $\nu$.
-Results are shown in \ref{table:flower17}
-
-\begin{table}[h]\scriptsize
-\centering
-\label{table:flower17}
-\begin{tabular}{c|c|c|c}
-\hline
-Method & Split 1 & Split 2 & Split 3\\\hline
-ASF &  97.94\% & 0 & 0 \\
-MKL &  000 & 0 & 0 \\
-RCEC &  000 & 0 & 0 \\
-FWOT &  000 & 0 & 0 \\
-LPBoost & 97.94\% & 0 & 0 \\\hline
-Ours &  98.24\% & 0 & 0 \\
-\hline
-\end{tabular}
-\caption{Accuracy on Three Official Split}
-\end{table}
-
-\fi
 
@@
   \bibliographystyle{aaai}
-  \bibliography{ensemble_clustering,m3frp}
+  \bibliography{RLF_MF}
 \end{small}

### 2016-09-14 RLF_MF.tex
revised on 15 Sept 2016 by Yan Yan with body part and introduction

@@
 \usepackage{algorithmic}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 \usepackage{threeparttable}
@@
 
-\def\grad{\mbox{\text{\textbf{grad}}}}
-\def\bzero{{\bf{0}}}
+\def\M{\mathcal{M}}
+\def\R{{\mathbb R}}
+\def\bR{{\bf R}}
+\def\U{{\bf U}}
+\def\V{{\bf V}}
+\def\diag{\mbox{diag}}
+\def\bsigma{\mbox{{\boldmath $\sigma$}}}
+\def\trsp{{\sf T}}
+\def\I{{\bf I}}
+\def\0{{\bf 0}}
+\def\E{{\bf E}}
+\def\G{{\bf G}}
+\def\grad{{\text{grad}}}
+\def\bZ{{\bf Z}}
+\def\bfeta{\mbox{{\boldmath $\eta$}}}
+\def\mT{{\mathcal T}}
 
@@
 
-\title{Consistent Late Fusion for Visual Recognition}
+%\title{Consistent Late Fusion for Visual Recognition}
+\title{Late Fusion via Subspace Search With Consistency Preservation}
 %% Efficient
+
 \author{AAAI Press\\
@@
 % First: A big picture of the scenario which we would consider
-In many real world applications, data can be represented in multiple ways or multi-view features,
+In many real-world applications, data can be represented in multiple ways or multi-view features,
 in order to describe various characteristics of data.
@@
 However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
-There is a requirement of outlier rejection for late fusion algorithms.
+So there is a requirement of outlier rejection for late fusion algorithms.
 % Fourth: general introduction of our method
@@
 Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
-There are often multiple ways to generate numerical features from raw data.
+There are often multiple ways to generate numerical features from raw data for visual recognition.
 For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
 (SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
-or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevskynips2012imagenet}.
+or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
 Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
@@
 To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
-As for outlier detection, as shown in Figure~\ref{fig:framework}, we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
+As for outlier detection, as shown in Figure~\ref{fig:framework} (notations are introduced shortly), we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
 Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
@@
   %\item We propose an efficient late fusion algorithm based on matrix factorization.
-  \item We formulate the late fusion problem as robust matrix recovery problem based on matrix factorization.
-  \item We extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
+  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
+  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
   \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
@@
 \centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
-\caption{Frame Work}
+\caption{Framework (example of $n=10, \calC=3, m=3$)}
 \label{fig:framework}
@@
 Let $\bL = [ \bL_1, \bL_2, ..., \bL_\calC ]$.
-On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
-On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which can be computed by
+%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
+On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
+On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
 $$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
@@
 \noindent
-where $\bX$ is the underlying low rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
+where $\bX \in \dsR^{n \times m\calC}$ is the underlying low rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
 and $p$ is a scalar.
@@
   \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
-             ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
+         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
 \end{align}
@@
 In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).
+
+\begin{small}
+\begin{algorithm}[h!]
+
+\begin{algorithmic}
+
+\REQUIRE $\bL \in \dsR^{n \times m\calC}$, $p$ (the rank of $\bX$)
+\ENSURE $\bX \in \dsR^{n \times m\calC}$
+\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(0)} = 0$, and $\mu^{(0)} > 0$.
+
+\WHILE{not converge}
+
+  \WHILE{not converge}
+
+    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
+    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
+
+    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
+    \STATE 2: Obtain $\bE^{(t)}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
+
+  \ENDWHILE
+
+  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
+
+  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
+
+  \STATE 5: t = t + 1.
+
+\ENDWHILE
+
+\end{algorithmic}
+\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
+\label{alg:alm_mf}
+\end{algorithm}
+\end{small}
 
@@
   \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
-  \st             ~&~ \bE = \bL - \bX   \nonumber \\
+  \st             ~&~ \bE = \bL - \bX  ,   \nonumber \\
                   ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
@@
 
-In particular, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
+\begin{theorem}
+\label{theorem:alm_convergence}
+  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
+\end{theorem}
+
+\begin{proof}
+\label{proof:proof_AA}
+  The proof can be found in Appendix A.
+\end{proof}
+
+\subsection{Optimization of The Subproblem of $\bX$}
+
+Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
 \begin{align}\label{eq:langrangian_wrt_X}
   \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
-              = & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
-                & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
-              = & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
+              %= & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
+              %  & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
+              %= & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
               = & || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
@@
 \end{align}
-Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt.
+%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt.
 $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
+Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
+We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.
+
+The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
+Let $r$ be a known scalar.
+A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
+\begin{eqnarray}
+\M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
+       &=& \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{r}^{n}, \V \in
+           \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
+\end{eqnarray}
+\noindent
+where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
+\U^{\trsp}\U = \I \}$ dentoes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
+We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
+which is obtained as below
+\begin{eqnarray}\label{eq:tangent_vector}
+&&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
+\U\V_p^{\trsp}: \bM \in \R^{r\times r}, \nonumber\\ && \U_p \in \R^{n\times r},
+\U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
+\end{eqnarray}
+\noindent
+One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{r}$,
+with $\bX \in \M_{r}$ and ${\bA},{\bB} \in T_{\bX}\M_{r}$,
+then $\M_{r}$ becomes a Riemannian manifold by restricting
+$\langle\bA,\bB\rangle$
+to the \emph{tangent bundle}, defined as the disjoint union of all tangent spaces:
+$T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
+         = \! \{(\bX,\E)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \E \in T_{\bX}\M_{r}\}.$
+
+Let $f(\bX) = || \bM - \bX ||_F^2$.
+%Suppose that $\G$ is the gradient of the smooth function $f(\bX)$ in Euclidean space at $\bX = \U\diag(\bsigma)\V^{\trsp} $.
+Suppose that $\G = \nabla f(\bX)$ in Euclidean space at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
+Then, according to~\cite{vandereycken2013lowrank}, the Riemannian gradient of $f(\bX)$ on $\M_r$ is given as the orthogonal
+projection of $\G$ onto the tangent space at $\bX$:
+\begin{eqnarray}\label{eq:grad}
+\grad{f(\bX)} = P_{T_{\bX}\M_{r}}(\G)  ,
+\end{eqnarray}
+\noindent
+where
+$P_{T_{\bX}\M_{r}}(\bZ): \bZ \mapsto P_{U}\bZ P_{V} + P_{U}^{\perp} \bZ P_{V} + P_{U} \bZ P_{V}^{\perp}$
+denotes the orthogonal projection of any
+$\bZ \in \R^{n \times m\calC}$ onto the tangent space at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
+Here $P_U = \U \U^{\trsp}$ and $P_U^{\perp} = \I - \U \U^{\trsp}$ for any $\U \in \textrm{St}_{r}^{n}$.
+
+\begin{small}
+\begin{algorithm}
+  \begin{algorithmic}
+    \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.
+
+    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.
+
+    \STATE 1. $\bR_{u} \leftarrow \G^{\trsp} \U$, $\bR_{v} \leftarrow \G \V$.
+
+    \STATE 2. $\bM \leftarrow \U^{\trsp} \bR_{v}$.
+
+    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
+  \end{algorithmic}
+  \caption{Computation of $\grad f(\bX)$ (Algorithm 2 in~\cite{vandereycken2013lowrank})}
+  \label{alg:compute_riemannian_grad}
+\end{algorithm}
+\end{small}
+
+\begin{lemma}
+  Assuming that $\U_{p}$, $\V_{p}$ and $\bM$ are computed by Algorithm~\ref{alg:compute_riemannian_grad},
+  we have ${\textnormal{grad}} f(\bX) = \U \bM \V + \U_{p} \V^{\trsp} + \U \V^{\trsp}_{p}$.
+\end{lemma}
+
+\begin{proof}
+  The proof can be found in Appendix B.
+\end{proof}
+
+\begin{small}
+\begin{algorithm}
+  \begin{algorithmic}
+    \REQUIRE Initial $\bX_{1} \in \M_{r}$, tangent vector $\bfeta_{0} = \0$, $k = 1$.
+
+    \WHILE{not converge}
+
+      \STATE 1. Compute Riemannian gradient $\bP_{k} = \grad f(\bX)$ by Algorithm~\ref{alg:compute_riemannian_grad}.
+
+      \STATE 2. Compute a conjugate direction with PR+:
+             $\bfeta_t = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.
+
+      \STATE 3. Find a step size $t_{k}$ and set $\bX_{k} = R_{\bX_{t}}(t_{k} \bfeta_{k})$.
+
+      \STATE 4. $k = k + 1$.
+
+    \ENDWHILE
+  \end{algorithmic}
+  \caption{LRGeomCG (Algorithm 1 in~\cite{vandereycken2013lowrank})}
+  \label{alg:LRGeomCG}
+\end{algorithm}
+\end{small}
+
+Particularly, in Step 2 of Algorithm~\ref{alg:LRGeomCG}, $\beta_{k}$ is determined by a Polak-Ribi$\grave{e}$re (PR+) rule~\cite{vandereycken2013lowrank}:
+\begin{eqnarray}\label{eq:beta}
+\beta_{k} = \frac{\grad f(\bX_{k})^{\trsp}(\grad f(\bX_{k}) - \grad f(\bX_{k-1}))}{\langle \grad f(\bX_{k-1}),\grad f(\bX_{k-1})\rangle}.
+\end{eqnarray}
+\noindent
+The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{r}}$, is chosen such that
+\begin{align}\label{eq:choose_step_size}
+  f(R_{\bX_{k}} (t_{k} \bfeta_{k})) \leq f(\bX_{k}) + c_{1} t_{k} \langle \grad f(\bX_{k}), \bfeta_{k} \rangle ,
+\end{align}
+\begin{align}\label{eq+choose_step_size2}
+  | \langle \grad f(R_{\bX_{k}} (t_{k} \bfeta_{k})), & \mT_{\bX_{k-1} \rightarrow \bX_{k}} (\bfeta_{k}) \rangle |  \nonumber \\
+                           & \leq c_{2} | \langle \grad f(\bX_{k}), \bfeta_{k} \rangle |  ,
+\end{align}
+\noindent
+where $0 \leq c_{1} \leq c_{2} \leq \frac{1}{2}$.
+The notation $\mT_{\bX_{k-1} \rightarrow \bX_{k}} (\bfeta_{k-1})$ in Step 2 and $R_{\bX_{k}} (t_k \bfeta_{k})$ denote \emph{vector transport} and \emph{retraction}, respectively.
+For more details of above two operators and the geometry of $\M_{r}$, see~\cite{vandereycken2013lowrank} and the references therein.
+
+%To compute $\grad{f(\bX)}$, we need to calculate the gradient of $f(\bX)$ on Euclidean space.
+%Firstly, the gradient of $\ell(\bX)$ w.r.t. $\bX$, denoted by $\widehat{\G}$, can be calculated by
+%\begin{small}
+%\begin{eqnarray}\label{eq:grad_X_Euc}
+%\widehat{\G}_{ij} = \frac{\partial \ell(\bX)}{\partial \bX_{ij}} = \sum_{z=1}^{L-1} T_{ij}^{z} \cdot h(T_{ij}^{z} \cdot(\theta_{z} - \bX_{ij})).
+%\end{eqnarray}
+%\end{small}
+%where $ij \in \Omega$.
+Note that the gradient of $ \Upsilon (\bX)$ w.r.t.
+$\bX$ is $ \U\diag(\bsigma - \nu/\bsigma^3)\V^{\trsp}$ at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
+The gradient of $f(\bX)$ w.r.t.
+$\bX$ in Euclidian space, denoted by $\G$, can be computed by
+%\begin{small}
+%\begin{eqnarray}
+%\G = \widehat{\G} + \lambda \U\diag(\bsigma - \nu/\bsigma^3)\V^{\trsp}.
+%\end{eqnarray}
+%\end{small}
+%Once $\G$ is computed, $\grad{f(\bX)}$ can be calculated according to equation (\ref{eq:grad}). The details of computation can be found in Appendix A.
+
+\subsection{Optimization of The Subproblem of $\bE$}
 
 Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
+%\begin{align}\label{eq:subproblem_wrt_E_1}
+%  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
+%              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+%\end{align}
 \begin{align}\label{eq:subproblem_wrt_E_1}
-  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
-              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
@@
 \begin{align}\label{eq:subproblem_wrt_E_2}
-  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 \\
+  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
 \end{align}
@@
 
-\begin{algorithm}[h!]
-\begin{algorithmic}
-\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(t)} = 0$, and $\mu^{(t)} > 0$.
-
-\WHILE{not converge}
-
-  \WHILE{not converge}
-
-    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
-
-    \STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
-
-  \ENDWHILE
-
-  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
-
-  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
-
-  \STATE 5: t = t + 1.
-
-\ENDWHILE
-
-\end{algorithmic}
-\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
-\label{alg:alm_mf}
-\end{algorithm}
-
-\begin{theorem}
-\label{theorem:alm_convergence}
-  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
-\end{theorem}
-
-\begin{proof}
-\label{proof:proof_AA}
-  The proof can be found in Appendix A.
-\end{proof}
-
 \subsection{Post Process}
@@
 \begin{itemize}
-  \item A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
+  \item $[AVE]$ A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
 		The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
-  \item For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ is the index of the highest value in the $i$-th row of $\bX_j$.
+  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ is the index of the highest value in the $i$-th row of $\bX_j$.
   		Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
   		Finally, we choose the label with the most votes to be the prediction results.
-  \item $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
+  \item $[GATE]$ $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
   		As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
@@
 According to the experiments, the last strategy outperforms than the others.
-So We choose the last one as the post process for fusion method and analyse inner reasons during experiment section.
+So We choose the last one as the post process for our fusion method and analyse inner reasons during experiment section.
 
@@
 Then we evaluate the perfomance on eight publicly available real-world data sets,
-UCF101~\cite{soomro2012ucf101}, CIFAR-10,100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet dataset~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
+UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
 The strategy analysis for post process is detailed in the last subsection.
@@
 Five state-of-the-art fusion methods are compared with our proposed alogrithm :
-(1)Average Score Fusion(ASF), we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization. 
-(2)Multiple Kernel Learning (MKL),  MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
-We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} to train our MKL model.
-(3)Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}. The core alogrithm in RCEC can be modified to recover X from L in ~\ref{eq:l12_mf}, and the post process is same as our method. 
-(4)Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
+(1)~Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
+(2)~Multiple Kernel Learning (MKL).
+MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
+(3)~Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}. The core alogrithm in RCEC can be modified to recover X from L in~\ref{eq:l12_mf}, and the post process is same as our method.
+(4)~Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
 The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
-(5)LPBoost\cite{gehler2009feature}. In this method, a variant linear combination are applied to multiple classifiers to boost performance.
+(5)~LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
 
-The parameter $\mu$ is selected from \{0.1, 1, 5\} and $\rho$ is select from \{1.01, 1.05, 1.1\} in all our experiments.
-It shows slight performance change during selecting different parameters.
-LIBLINEAR\cite{fan2008liblinear} is adopted for our basic classification toolbox.
+The parameter $\mu$ is selected from $\{0.1, 1, 5\}$ and $\rho$ is select from $\{1.01, 1.05, 1.1\}$ in all our experiments.
+Among different parameters, there are small differences of the prediction performance.
+LIBLINEAR~\cite{fan2008liblinear} is adopted for our basic classification toolbox.
 The parameters are set as default in LIBLINEAR and liblinear-mkl, unless otherwise specified.
-For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from \{0.01,1,2,4,6,...,20\} and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
-For FWOT, the smoothing parameter candidates are \{0.5, 0.6, ...
-, 0.9\} and the parameter C in is selected from \{$10^{-4},10^{-2},...,10^{4}$\} according to cross-validation, which is same in~\cite{xuiccv2013feature}.
-For LPBoost, we use cross-validation to pick up the best $\nu$ from \{0.5,0.6,0.7,0.8,0.9\} suggested by~\cite{xuiccv2013feature}.
+For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from $\{0.01,1,2,4,6,...,20\}$ and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
+For FWOT, the smoothing parameter candidates are $\{0.5, 0.6, ...
+, 0.9\}$ and the parameter $C$ in is selected from $\{10^{-4},10^{-2},...,10^{4}\}$ according to cross-validation, which is same in~\cite{xuiccv2013feature}.
+For LPBoost, we use cross-validation to pick up the best $\nu$ from $\{0.5,0.6,0.7,0.8,0.9\}$ suggested in~\cite{xuiccv2013feature}.
 
@@
 
-In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to randomly generate $n$ instances with $\calC$ kinds of labels for each instance. 
-Then we randomly permute $40\%$ instances' labels, repeat fifteen times to get $m = 15$ classifiers' results. 
-After appling our proposed alogrithm to this synthetic dataset, we visualize the results in Figure~\ref{fig:ensemble_cluster}.
+In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to generate $n$ instances, which are randomly labeled with $c_i, 1 \leq i \leq n, 1 \leq c_i \leq \calC$.
+And we regard these instances as the ground truth data.
+Then we randomly permute $40\%$ instances' labels, repeating $m = 15$ times to get fifteen classifiers' results.
+Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed alogrithm,
+the visualization results are illustrated in Figure~\ref{fig:ensemble_cluster}.
+
 Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different label.
-The first picture~\ref{subfig:gt_pdf} show the ground truth label repeating M times. 
+The first picture~\ref{subfig:gt_pdf} show the visualized ground truth data, which are copied $m$ times.
 And $m$ noised classifiers' results are pictured as~\ref{subfig:er_pdf}.
-We recover the low rank matrix $\bX$ from the noised matrix by using our late fusion method, which is visualized as~\ref{subfig:er_pdf}.
+We recover the low rank matrix $\bX$ from the noised matrix by using our late fusion method, which is visualized as~\ref{subfig:re_pdf}.
 
@@
 
-\begin{table*}[t]\small
+\begin{table*}[t]
+%\small
 \centering
+\begin{scriptsize}
+\caption{Mean accuracy on real-world data sets}
 \begin{tabular}{c|c|c|c|c|c}
@@
 RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
-FWOT                & -        & -        & -         & 92.90\%         &   90.81\%            \\    %FWOT ***
+FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
 LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
-Ours                & 89.03\%  & 95.11\%  & 77.72\%   & 92.90\%         &   90.98\%            \\ 
+\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
 \hline
 \end{tabular}
-\caption{Mean Accuracy on Each Dataset}
+\end{scriptsize}
 \label{table:total_acc}
@@
 
-\begin{table*}[t]\small
+\begin{table*}[t]
+%\small
 \centering
-\begin{tabular}{c|c|c|c|c|c|c}
+\begin{scriptsize}
+\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
+\begin{tabular}{c|c|c|c|c|c}
 \hline
-Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 & Oxford Flowers 17 \\\hline
-RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         & 3.14   \\ 
-FWOT                & $\infty$   & $\infty$  & $\infty$   & $\geq$ 1e4      &   $\approx$ 9e3 & 229.0  \\
-LPBoost             & 110.81     & 72.45     & $\geq$ 1e4 & 43.67           &   7.46          & 0.26   \\\hline
-Ours                & 421.23     & 5.384     &   lack     & 76.16           &   16.21         & 1.62   \\ 
+Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
+RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
+FWOT                & $\infty$   & $\infty$  & $\infty$   & 61697           &   19674         \\
+LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
+Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
 \hline
 \end{tabular}
-\caption{Time Consumption on Each Dataset}
+\end{scriptsize}
 \label{table:total_time}
 \end{table*}
+
+%% Flower 17 Time [3.14] [229] [0.26] [1.62]
 
@@
 Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
-`-' means the contrast algorithm does not work due to heavy memory or time consumption, and `$\infty$' means it will take more than one day to complete the corresponding method.
-The time cost of cross-validation in FWOT and LPBoost are not counted.
+`-' means the contrast algorithm does not work due to heavy memory or time consumption,
+and `$\infty$' means it will take more than one day to complete the corresponding method.
+The computational cost of cross-validation is not counted in FWOT and LPBoost.
 
 %\subsubsection{Experiment on UCF 101 dataset}
-For action recognition, we present our results on UCF 101 dataset. 
+For action recognition, we present the comparison results on UCF 101 dataset.
 UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
@@
 Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
-To be noted, FWOT~\cite{xuiccv2013feature} is too slow to train, we didn't show it's result (more than one day).
+To be noted, FWOT is too slow to train, we didn't show its result (more than one day).
 
@@
 
-In this section, we compare three proposed post strategies on three small dataset: Wikipedia~\cite{rasiwasia2010new}, Oxford Flowers 17~\cite{nilsback2006visual} and Pascal Sentence~\cite{Li2006One}.
-Wikipedia dataset contains paragraphs of text for each picture,
-and total 2866 image-text pairs are categoried into 10 class, we only use the image label annotation.
-PASCAL VOC 2007 contrains 6146 images classified into 20 classes, after filtering the multi-label data. 
+In this section, we compare three proposed post strategies on three small datasets: Wikipedia~\cite{rasiwasia2010new}, Oxford Flowers 17~\cite{nilsback2006visual} and Pascal Sentence~\cite{Li2006One}.
+Wikipedia dataset contains paragraphs of text for each picture, and total 2866 image-text pairs are categoried into 10 class.
+Only the image label annotation is used in our experiments.
+PASCAL VOC 2007 contains 9963 images annotated with object-level information, which means each picture may have zero or more than one class.
+We choose 6146 images classified into 20 classes by filtering out the no-single class data.
 Oxford Flowers 17 has 17 flower categories with 80 images for each class.
 Pascal Sentence contains 1000 images annotated by caption information and categoried into twenty classes.
-Fifty percent of data are sampled as training set and the others as testing set, repeat experiments five times on above three datasets.
+Fifty percent of data are sampled as training set and the others as testing set, and experiments are repeated five times on above three datasets.
 
-Experiments show that the first strategy outperforms than the others in most cases and never performes under the others. 
-This might be caused by that the soft average method reserves more detail information than the hard voting method.
-Since the recover matrix X contains the outlier rejection information,
-the last strategy combines the recovered results as a confidence gate operating on the original confidence score matrix.
-It utilizes more robust information than both the first and second strategy.
+The $[$AVE$]$ strategy outperforms than the $[$VOTE$]$ in our experiments, which may be caused by the soft average method reserves more detail information than the hard voting method.
+In all our experiments, the accuracy performance of the $[$GATE$]$ strategy is higher than the others.
+Since the recover matrix $\bX$ contains the outlier rejection information,
+it's more robust to take advantage of the recovered results as a confidence gate operating on the original confidence score matrix.
 
-\begin{table}[h]\small
+\begin{table}[h]
+%\small
 \centering
+\begin{scriptsize}
+\caption{Mean Accuracy with Different Strategies}
 \begin{tabular}{c|c|c|c}
 \hline
-Method                       & Wikipedia &  Flowers 17  & Pascal Sentence \\\hline
-Strategy 1                   & 47.78\%   &  96.77\%     &   66.40\%       \\\hline
-Strategy 2                   & 47.85\%   &  96.61\%     &   66.20\%       \\\hline
-Strategy 3                   & 49.03\%   &  96.77\%     &   67.20\%       \\
+Strategy            & Wikipedia & Flowers 17 & Pascal Sentence \\\hline
+[AVE]               & 47.78\%   & 96.77\%    &   66.40\%       \\\hline
+[VOTE]              & 47.85\%   & 96.61\%    &   66.20\%       \\\hline
+[GATE]              & 49.03\%   & 96.77\%    &   67.20\%       \\
 \hline
 \end{tabular}
-\caption{Mean Accuracy on Three Strategies}
+\end{scriptsize}
 \label{table:strategy}
 \end{table}
+
+\section{Conclusion}
+
+To relieve the performance degeneration in late label fusion from multiple sources, we formulate this problem as matrix factorization which recovers the underlying low-rank matrix and preserves the consistency among different sources.
+%To deal with the dispute on combining multi-view predictions, we formulate the late fusion problem as a matrix recover problem.
+%Our proposed algorithm is based on matrix factorization, which is unclear to consider smooth loss function from earlier research.
+Existing matrix factorization algorithms usually consider smooth loss, while it is unclear how to extend them to handle nonsmooth robust loss, \eg, $\ell_{1,2}$ loss.
+We propose an ALM based algorithm to solve matrix factorization problems with nonsmooth loss.
+%Specifically, our proposed algorithm first rejects outliers on a label indicator matrix by $\ell_{1,2}$ loss,
+%and then generates the predictions by combining robust outlier rejection information and prediction confidence scores from basic classifiers.
+Empirical studies on large scale real-world data sets demonstrate that our proposed method can effectively improve performance compared to the state-of-the-art late fusion methods.
 

### 2016-09-14 RLF_MF.tex
revised on 15 Sept 2016 by Yan Yan with body part and introduction

@@
 
-Our proposed late fusion algorithm is based on matrix factorization,
-which has attracted increasing attention recently.
+%Our proposed late fusion algorithm is based on matrix factorization,
+%which has attracted increasing attention recently.
+Matrix factorization has attracted increasing attention recently.
 Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry.
@@
 \ENSURE $\bX \in \dsR^{n \times m\calC}$
-\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(0)} = 0$, and $\mu^{(0)} > 0$.
+\STATE Initialize $\rho > 1$, $t = 0$, $\blambda_{0} = 0$, and $\mu_{0} > 0$.
 
@@
     %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
-    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
+    \STATE 1: Obtain $\bX_{t}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
 
     %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
-    \STATE 2: Obtain $\bE^{(t)}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
+    \STATE 2: Obtain $\bE_{t}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
 
@@
 
-  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
+  \STATE 3: $\blambda_{t+1} = \blambda_{t} + \mu_{t} (\bL - \bX_{t+1} - \bE_{t+1})$.
 
-  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
+  \STATE 4: $\mu_{t+1} = \rho \mu_{t}$.
 
@@
 \end{small}
+
+%
+%\begin{small}
+%\begin{algorithm}[h!]
+%
+%\begin{algorithmic}
+%
+%\REQUIRE $\bL \in \dsR^{n \times m\calC}$, $p$ (the rank of $\bX$)
+%\ENSURE $\bX \in \dsR^{n \times m\calC}$
+%\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(0)} = 0$, and $\mu^{(0)} > 0$.
+%
+%\WHILE{not converge}
+%
+%  \WHILE{not converge}
+%
+%    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
+%    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
+%
+%    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
+%    \STATE 2: Obtain $\bE^{(t)}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
+%
+%  \ENDWHILE
+%
+%  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
+%
+%  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
+%
+%  \STATE 5: t = t + 1.
+%
+%\ENDWHILE
+%
+%\end{algorithmic}
+%\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
+%\label{alg:alm_mf}
+%\end{algorithm}
+%\end{small}
 
@@
 $T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
-         = \! \{(\bX,\E)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \E \in T_{\bX}\M_{r}\}.$
+         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \bP \in T_{\bX}\M_{r}\}.$
 
@@
 \begin{table*}[t]
-%\small
+\small
 \centering
-\begin{scriptsize}
-\caption{Mean accuracy on real-world data sets}
+\caption{Mean accuracy on real-world data sets.}
 \begin{tabular}{c|c|c|c|c|c}
@@
 \end{tabular}
-\end{scriptsize}
 \label{table:total_acc}
@@
 \begin{table*}[t]
-%\small
+\small
 \centering
-\begin{scriptsize}
 \caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
@@
 \end{tabular}
-\end{scriptsize}
 \label{table:total_time}
@@
 In UCF101 dataset, five different features are extracted from the following:
-\begin{itemize}
-  \item `fc6' of C3D~\cite{tran2015learning}
-  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-  \item `pool5' of ResNet-152~\cite{he2015deep}
-  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
-\end{itemize}
+%\begin{itemize}
+%  \item `fc6' of C3D~\cite{tran2015learning}
+%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+%  \item `pool5' of ResNet-152~\cite{he2015deep}
+%  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
+%\end{itemize}
+`fc6' of C3D~\cite{tran2015learning},
+`pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going},
+`pool5' of ResNet-152~\cite{he2015deep},
+and two `fc6's of Two-Stream~\cite{simonyan2014two}.
 Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
@@
 In Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,110,164 models~\cite{he2016identity}.
-One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}.
+One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt
+\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}
+.
 Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers), trained the same in~\cite{he2015deep}
-Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}} before extracting features.
+Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell
+\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}}
+before extracting features.
 In Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of pre-activation ResNet-20,32,44,56,110,164 models, following the same training process as in~\cite{he2015deep,he2016identity}.
@@
 In all other experiments, eight different features are extracted from the following:
-\begin{itemize}
-  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
-  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
-  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
-\end{itemize}
-We use the offical pre-trained model provided by Caffe Model Zoo\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}.
+%\begin{itemize}
+%  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
+%  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
+%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+%  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
+%\end{itemize}
+``fc6'' of VGG16, VGG19~\cite{chatfield2014return},
+``fc6'' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet},
+``pool5/7x7\_s1'' from GoogleNet~\cite{szegedy2015going},
+and ``pool5'' of ResNet-50,101,152~\cite{he2015deep}.
+We use the offical pre-trained model provided by Caffe Model Zoo
+\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}
+.
 For above eight models, we simply extract features with no extra operation.
@@
 which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
-We also use `-s 2' parameters in liblinear to speedup training process. Results of total six contrast algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+We also use `-s 2' parameters in liblinear to speedup training process.
+Results of total six competing algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
 
@@
 Since the recover matrix $\bX$ contains the outlier rejection information,
-it's more robust to take advantage of the recovered results as a confidence gate operating on the original confidence score matrix.
+it is more robust to take advantage of the recovered results as a confidence gate operating on the original confidence score matrix.
 
 \begin{table}[h]
-%\small
+\small
 \centering
-\begin{scriptsize}
 \caption{Mean Accuracy with Different Strategies}
@@
 \end{tabular}
-\end{scriptsize}
 \label{table:strategy}

### 2016-09-14 RLF_MF.tex
revised on 15 Sept 2016 by Yan Yan with body part and introduction

@@
 On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
+{\small
 $$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
+}
+\noindent
 Thus, the proposed model can be written as below:
+{\small
 \begin{align}\label{eq:l12_rankconstraint}
@@
 \end{align}
+}
 \noindent
@@
 We hence transform the original problem as a matrix factorization formulation as below:
+{\small
 \begin{align}\label{eq:l12_mf}
@@
 By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
+{\small
 \begin{align}\label{eq:mf_l21_constrained}
@@
 \end{align}
+}
+\noindent
 The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
+{\small
 \begin{align}\label{eq:lagrangian_l21}
@@
 Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
+{\small
 \begin{align}\label{eq:langrangian_wrt_X}
@@
 Hence, we derive the following subproblem \wrt. $\bX$:
+{\small
 \begin{align}\label{eq:subproblem_wrt_X}
@@
 \end{align}
+}
+\noindent
 %Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt.
@@
 A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
+{\small
 \begin{eqnarray}
@@
 \end{eqnarray}
+}
 \noindent
@@
 which is obtained as below
+{\small
 \begin{eqnarray}\label{eq:tangent_vector}
@@
 projection of $\G$ onto the tangent space at $\bX$:
+{\small
 \begin{eqnarray}\label{eq:grad}
@@
 Particularly, in Step 2 of Algorithm~\ref{alg:LRGeomCG}, $\beta_{k}$ is determined by a Polak-Ribi$\grave{e}$re (PR+) rule~\cite{vandereycken2013lowrank}:
+{\small
 \begin{eqnarray}\label{eq:beta}
@@
 \end{eqnarray}
+}
 \noindent
 The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{r}}$, is chosen such that
+{\small
 \begin{align}\label{eq:choose_step_size}
@@
 \end{align}
+}
+{\small
 \begin{align}\label{eq+choose_step_size2}
@@
 %\end{align}
+{\small
 \begin{align}\label{eq:subproblem_wrt_E_1}
@@
 We thus obtain the subproblem \wrt. $\bE$ as below:
+{\small
 \begin{align}\label{eq:subproblem_wrt_E_2}
@@
 \end{align}
+}
 \noindent
 The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
+{\small
 \begin{align}\label{eq:column_wise_soft_thresholding}
@@
 \end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item[*]
+  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``-''.
+\end{tablenotes}
 \label{table:total_acc}
@@
 \end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item[*]
+  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``$\infty$''.
+\end{tablenotes}
 \label{table:total_time}

### 2017-02-28 Fusion-cvpr2017-RebuttalKit/egrebuttal-fusion.tex
prepare for iccv

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}

\def\dxyred{\textcolor{red}}
\def\bE{\bf{E}}
\def\bL{\bf{L}}
\def\bX{\bf{X}}
\def\calL{\mathcal{L}}
\def\blambda{\mbox{{\boldmath $\lambda$}}}

\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3651} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Late Fusion via Subspace Search with Consistency Preservation}

\maketitle
\thispagestyle{empty}

We thank all the reviewers.
%R3 is positive.
%R1 has some suggestions about technical analysis.
%R2 may have some misunderstandings about our paper.
We will take the comments seriously and will carefully revise the paper.
Code will be released.

\noindent\emph{\textbf{To Assigned Reviewer 1}}

{\bf Q1: The technical part in Sec 3.2 a little over-sold.}

{\bf A1:}
\textbf{Thanks for the comments.}
First, ALM is usually used for solving convex problems~[50] and (G. Liu etal, TPAMI 2013),
but our Problem~(2) is \textbf{non-convex},
and thus the convergence behavior of Algorithm 1 is unclear using standard ALM.
Second, we explicitly indicate the connection between the definition (Eq.8) and the computation (Algorithm 2) of Riemannian gradient by presenting Lemma 1,
which has never been discussed in previous works.
Third, we present every step of Algorithm~1 to make the paper self-contained.
To address the concerns, we will add more references (including G. Liu etal, TPAMI 2013) and explain the difference between our paper and the related works.

Typos will be corrected.

\noindent\emph{\textbf{To Assigned Reviewer 2}}

\textbf{Thanks for constructive comments and suggestions.}
We may have not clearly presented our method so that reviewer have misunderstood some points.
Below we mainly clarify reviewer's misunderstandings, illustrate the contributions and highlight the differences between the existing methods.

It it correct that our approach is more efficient than SVD,
but it seems that reviewer may have misunderstood the connections/differences between the STOC paper (P. Jain et al. 2013) and our approach.
At the first glance the STOC paper looks directly applicable to our problem,
but the conditions of the paper and ours are quite different.
Specifically, the STOC paper requires a \textbf{Incoherent Matrix Assumption} for matrix completion,
which is not guaranteed to converge the global solution in our work.
Therefore, we disagree with reviewer that alternating minimization would reach a global solution with a simpler approach.
In addition, as shown in [41], the Riemannian manifold method converges faster than the alternating minimization approach.
%indicating that our approach is more capable of dealing with high-dimensional large scale data.

Apart from the misunderstanding, reviewer's concerns are mainly about the contributions given [10], [50] and (Liu et al. PAMI 2013).
Below, we brief the novelties and contribution over [10], [50] and (Liu et al. PAMI 2013).
%[10] and [50] formulate the fusion problem as a nuclear norm regularization problem, which cannot handle large-scale problems.
First, our method leverages $l_{1,2}$ norm for malicious classifier detection rather than the commonly used robust $l_{1}$ norm [10].
Second, we show the convergence of ALM for solving a non-convex problem rather than the convex problem in previous work (Liu et al. 2013).
Third, we propose to use matrix factorization (MF) technique to improve the efficiency comparing with nuclear norm based methods [10, 50].
Fourth, most MF methods only consider smooth $l_{2}$ loss, but we extend it to non-smooth $l_{1,2}$ loss.

Based on our discussions above,
Algorithm 2/3 should not be replaced by other methods based on the STOC paper.

Regarding the comments on Theorem 1, we clarify a few minor misunderstandings and technical issues.
First, the convergence of $\bX$ is guaranteed by [41].
Second, the proof of Theorem 1 relies on the gradient without the convexity requirement.
Third, the assumption for the boundedness of $\lambda_k$ is common (Th. Oh etal. TPAMI2016).
With $k \rightarrow \infty$, the gradient of $\calL$ vanishes.
Thus our algorithm converges and accumulation points will be achieved.

Thanks for the comments on empirical study.
However, reviewer may have overlooked important results from the tables.
Our method significantly outperforms LPBosst, as reported in Table 1 and 5.
Specifically, our method achieves much higher accuracy \textbf{(89.03\%)} than LPBoost \textbf{(86.24\%)} on UCF-101,
and CIFAR-100 \textbf{(77.72\% vs 76.59\%)}.

As indicated in Sec 4.4, we have provided very detailed approach for post-processing.
All the parameters of all algorithms are tuned by cross-validation with the same setting.
No human intervention was involved.
Therefore, the results should be reproducible and reliable.

It is the convention of CV papers to compare the results reported in recent papers on a standard setting.
CV researchers sometimes do not release their best model for business reasons,
but often share the not-that-new models with the community.
We show that combining a few weak models using our method,
the performance can be better than a single strong model.
To be more specific, the best single model on CIFAR-10 was reported in 12/2016 (see arXiv:1611.05431) with a test error of 3.58.
Our method fuse multiple single models which all perform worse than (arXiv:1611.05431), but can achieve low test error on CIFAR-10 (3.47 in Table 5).
This demonstrates the benefit of a good late fusion method.

We will take reviewer's comments seriously and will revise our paper carefully according to the comments.
We hope reviewer will find our paper contains novel ideas and acceptable for CVPR based on our explanations.

\noindent\emph{\textbf{To Assigned Reviewer 3}}

\textbf{Thanks for comments.}
Inappropriate figures, notations and typos will be revised/corrected.
$\ell_{1,2}$ loss preserves the fidelity within columns (lines 106-110),
and we will add more discussions and results of using $\ell_{2}$ norm.
Regarding the question on adversarial classifiers, we have discussed this issue in Sec4.1 \textbf{visualized in Fig.2.}
We will add more discussions and cite the related paper.
Thanks for the last suggestion, and it will be investigated in our future work.

\end{document}

### 2017-02-28 back-aaai/RLF_MF.tex
prepare for iccv

--- 2016-09-14 RLF_MF.tex
@@
 %\title{Consistent Late Fusion for Visual Recognition}
-\title{Late Fusion via Subspace Search With Consistency Preservation}
+\title{Late Fusion via Subspace Search with Consistency Preservation}
 %% Efficient
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
@@
 
-\begin{small}
-\begin{algorithm}[h!]
+%\begin{small}
+\begin{algorithm}[ht]
 
@@
 
-\REQUIRE $\bL \in \dsR^{n \times m\calC}$, $p$ (the rank of $\bX$)
-\ENSURE $\bX \in \dsR^{n \times m\calC}$
-\STATE Initialize $\rho > 1$, $t = 0$, $\blambda_{0} = 0$, and $\mu_{0} > 0$.
+\REQUIRE $\bL \in \dsR^{n \times m\calC}$, rank($\bX$) = $p$
+
+\STATE Initialize $\rho > 1$, $t = 0$, $\blambda_{0} = 0$, $\bE_{0} = 0$, and $\mu_{0} > 0$.
 
@@
     %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
-    \STATE 1: Obtain $\bX_{t}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
+    \STATE 1: Obtain $\bX_{t+1}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
 
     %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
-    \STATE 2: Obtain $\bE_{t}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
+    \STATE 2: Obtain $\bE_{t+1}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
 
@@
 
+\ENSURE $\bX \in \dsR^{n \times m\calC}$
+
 \end{algorithmic}
@@
 \end{algorithm}
-\end{small}
+%\end{small}
 
@@
 
-\begin{small}
+%\begin{small}
 \begin{algorithm}
@@
     \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.
-
-    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.
 
@@
     \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
+
+    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.
+
   \end{algorithmic}
@@
 
-      \STATE 1. Compute Riemannian gradient $\bP_{k} = \grad f(\bX)$ by Algorithm~\ref{alg:compute_riemannian_grad}.
+      \STATE 1. Compute Riemannian gradient $\bP_{k} = \grad f(\bX_{k})$ by Algorithm~\ref{alg:compute_riemannian_grad}.
 
       \STATE 2. Compute a conjugate direction with PR+:
-             $\bfeta_t = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.
+             $\bfeta_k = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.
 
-      \STATE 3. Find a step size $t_{k}$ and set $\bX_{k} = R_{\bX_{t}}(t_{k} \bfeta_{k})$.
+      \STATE 3. Find a step size $t_{k} = \min_{t} f(\bX + t\bfeta_{k}) $
 
-      \STATE 4. $k = k + 1$.
+      \STATE 4. Update $\bX_{k+1} = R_{\bX_{k}}(t_{k} \bfeta_{k})$.
+
+      \STATE 5. $k = k + 1$.
 
     \ENDWHILE
+
+    \ENSURE $\bX \in \M_{r}$.
+
   \end{algorithmic}
@@
 \begin{align}\label{eq:column_wise_soft_thresholding}
-  \bE_{i} = \calS_{\alpha}(\bY_{i}) = \left\{
+  \bE_{i} = \calS_{\alpha}(\bN_{i}) = \left\{
     \begin{aligned}
       & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
-      & \bY_{i} - \frac{\alpha \bY_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
+      & \bN_{i} - \frac{\alpha \bN_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
     \end{aligned}
@@
 \noindent
-where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bY$,
-and $\alpha = \frac{2}{\mu}$.
+where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bN$,
+%and $\alpha = \frac{2}{\mu}$.
+and $\alpha = \frac{1}{2}$.
 
@@
 As we recover the low rank matrix $\bX$ from the label assignment matrix $\bL$,
-it needs a post process to make the predicted label for each testing data.
+it needs a post process to generate the prediction label for each testing data.
 Intuitively, there might be several possible ways to select as below:
@@
 		The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
-  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ is the index of the highest value in the $i$-th row of $\bX_j$.
+  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
   		Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
@@
   		As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
-  		The similar process as the first strategy is applied to the above results, which predictes the final label.
+  		The similar process as the first strategy is applied to the above results, which predictes the final labels.
 \end{itemize}
-According to the experiments, the last strategy outperforms than the others.
-So We choose the last one as the post process for our fusion method and analyse inner reasons during experiment section.
+According to the experiments, the last strategy ``GATE'' outperforms than the others.
+So We choose the last one as the post process for our fusion method and analyse inner reasons during the experiment section.
 
@@
 
-In this section, we first visualize the results of our approach on one synthetic dataset.
+In this section, we first visualize the results of our approach on the synthetic dataset.
 Then we evaluate the perfomance on eight publicly available real-world data sets,
@@
 
-\begin{table*}[t]
-\small
-\centering
-\caption{Mean accuracy on real-world data sets.}
-\begin{tabular}{c|c|c|c|c|c}
-\hline
-Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007    \\\hline
-ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%         &   90.51\%          \\
-MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%         &   85.82\%          \\
-RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
-FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
-LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
-\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item[*]
-  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``-''.
-\end{tablenotes}
-\label{table:total_acc}
-\end{table*}
-
-\begin{table*}[t]
-\small
-\centering
-\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
-\begin{tabular}{c|c|c|c|c|c}
-\hline
-Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
-RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
-FWOT                & $\infty$   & $\infty$  & $\infty$   & 61697           &   19674         \\
-LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
-Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item[*]
-  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``$\infty$''.
-\end{tablenotes}
-\label{table:total_time}
-\end{table*}
-
 %% Flower 17 Time [3.14] [229] [0.26] [1.62]
@@
 Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
-`-' means the contrast algorithm does not work due to heavy memory or time consumption,
-and `$\infty$' means it will take more than one day to complete the corresponding method.
-The computational cost of cross-validation is not counted in FWOT and LPBoost.
+And the computational cost of cross-validation is not counted in FWOT and LPBoost.
 
@@
 
+\begin{table*}[t]
+\small
+\centering
+\caption{Mean accuracy on real-world data sets.}
+\begin{tabular}{c|c|c|c|c|c}
+\hline
+Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007    \\\hline
+ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%         &   90.51\%          \\
+MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%         &   85.82\%          \\
+RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
+FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
+LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
+\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item[*]
+  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``-''.
+\end{tablenotes}
+\label{table:total_acc}
+\end{table*}
+
+\begin{table*}[t]
+\small
+\centering
+\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
+\begin{tabular}{c|c|c|c|c|c}
+\hline
+Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
+RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
+FWOT                & $\infty$   & $\infty$  &  $\infty$     & 61697           &   19674         \\
+LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
+Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item[*]
+  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``$\infty$''.
+\end{tablenotes}
+\label{table:total_time}
+\end{table*}
+
 %\subsubsection{Experiment on Cifar10 dataset}
@@
 FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
-LPBoost algorithm needs to create a $nm\times \calC$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.},
+LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
+\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
 which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
 We also use `-s 2' parameters in liblinear to speedup training process.
-Results of total six competing algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+Results of total six contrast algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
 
@@
 Training and comparison process are the same as CIFAR-10.
+Detailed results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
 
@@
 
-\begin{table}[h]
-\small
+\begin{table}[ht]
+%\small
 \centering
@@
 Strategy            & Wikipedia         & Flowers 17          & Pascal Sentence     \\\hline
-[AVE]               & 47.78\%   & 96.77\%    &   66.40\%       \\\hline
+[AVE]               & 47.78\%           & \textbf{96.77\%}    & 66.40\%             \\\hline
 [VOTE]              & 47.85\%           & 96.61\%             & 66.20\%             \\\hline
-[GATE]              & 49.03\%   & 96.77\%    &   67.20\%       \\
+[GATE]              & \textbf{49.03\%}  & \textbf{96.77\%}    & \textbf{67.20\%}    \\
 \hline

### 2017-02-28 egpaper_for_review.tex
prepare for iccv

--- 2017-02-28 back-aaai/RLF_MF.tex
@@
-\def\year{2017}\relax
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article}
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
+\usepackage{iccv}
+\usepackage{times}
+\usepackage{epsfig}
 \usepackage{graphicx}
@@
 \usepackage{amssymb}
+
+%%%%% 
+\usepackage{subfigure}
+\usepackage{multirow}
 \usepackage{amsthm,mathrsfs,amsfonts,dsfont}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
-\usepackage{threeparttable}
-\usepackage{multirow}
-\usepackage{subfigure}
-\usepackage{color}
 \usepackage{epstopdf}
 \usepackage{bm}
-%\usepackage[vlined,boxed,ruled]{algorithm2e}
-\usepackage{url}
-\usepackage{xspace}
-
 \newtheorem{corollary}{Corollary}
@@
 \newtheorem{remark}{Remark}
-
-\usepackage{aaai17}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
 
@@
 \def\0{{\bf 0}}
-\def\E{{\bf E}}
 \def\G{{\bf G}}
@@
 
-\def\bA{{\bf A}}
 \def\bB{{\bf B}}
@@
 \def\yanblue{\textcolor{blue}}
+%%%%%
 
-\frenchspacing
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
-\pdfinfo{
-/Title (Insert Your Title Here)
-/Author (Put All Your Authors Here, Separated by Commas)}
-\setcounter{secnumdepth}{0}
+% Include other packages here, before hyperref.
+
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+% \iccvfinalcopy % *** Uncomment this line for the final submission
+
+\def\iccvPaperID{283} % *** Enter the ICCV Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ificcvfinal\pagestyle{empty}\fi
 \begin{document}
 
-% The file aaai.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
+%%%%%%%%% TITLE
+\title{Late Fusion via Subspace Search with Consistency Preservation}
 
-%\title{Consistent Late Fusion for Visual Recognition}
-\title{Late Fusion via Subspace Search with Consistency Preservation}
-%% Efficient
-
-\author{AAAI Press\\
-Association for the Advancement of Artificial Intelligence\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\
+\author{First Author\\
+Institution1\\
+Institution1 address\\
+{\tt\small firstauthor@i1.org}
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
+% To save space, use either the email address or home page, not both
+\and
+Second Author\\
+Institution2\\
+First line of institution2 address\\
+{\tt\small secondauthor@i2.org}
 }
@@
 \maketitle
+%\thispagestyle{empty}
 
 \begin{abstract}
-% First: A big picture of the scenario which we would consider
 In many real-world applications, data can be represented in multiple ways or multi-view features,
@@
 In this way, it could often improve the prediction performance by taking advantage of these feature together.
-% Second: what BIG problem would we like to solve?
 Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
-% Third: specify the detailed problem: find a precise position for our paper
 However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
-So there is a requirement of outlier rejection for late fusion algorithms.
-% Fourth: general introduction of our method
+Therefore, there is a requirement of outlier rejection while preserving consistency among different classifier results.
 In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources,
 which could avoid the performance degeneration caused by the controversy of multiple features on test data.
-% Some unvalued sentence(s)
 Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.
@@
 However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
-To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
+To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
 Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.
 
-To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
-As for outlier detection, as shown in Figure~\ref{fig:framework} (notations are introduced shortly), we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
-Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{resource/frame_work.pdf}
+\end{center}
+\caption{Framework of our late fusion algorithm.
+In this example, there are 10 instances 3 classifiers and 3 classes.
+Predictions of each classifier are converted to a binary indicator matrix,
+denoted by $L_1$, $L_2$ and $L_3$.
+Let $L = [L_1, L_2, L_3]$ be the label matrix.
+Our algorithm detects and removes the outliers on $L$ and then recover the underlying low-rank subspace of $L$ as the prediction for testing instances.
+We finally apply a post-processing method to generate the fused results.
+%First, there are $\calC=3$ classifiers' results for $n=10$ instances.
+%Each of them are converted into ``binary'' indicators from the soft prediction results, as $L = [L_1, L_2, L_3]$.
+%Then, our ALM-based optimization process the binary indicator matrix into a recovered matrix $X$,
+%which can be treated as soft prediction scores for testing instances.
+%Finally, the fused prediction results are generated by a post-processing method.
+}
+\label{fig:framework}
+\end{figure}
+
+To prevent from the expensive nuclear norm minimization,
+in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
+Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
+As for outlier detection,
+we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
+Notations are introduced shortly.).
+Due to the fact that the $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction,
+we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
+Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth loss.
 We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
-The main contributions are summarized as below:
+
+The main contributions of this work are summarized as below:
 \begin{itemize}
-  %\item We propose an efficient late fusion algorithm based on matrix factorization.
   \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
   \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss. 
+  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
+  %It is capable of handling large scale problems.
   \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
@@
 Matrix factorization has attracted increasing attention recently.
-Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry.
+Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
 Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
-In~\cite{vandereycken2013lowrank}, the authors propose a low rank geometric conjugate gradient (LRGeomCG) method.
-In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low rank matrix completion by exploiting the low rank constraint.
+In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
+In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
 In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
@@
 In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
-The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm is proposed to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
+The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
 In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
@@
 
-%% Latent Fusion,
+Some other fusion algorithms are propsed for specific tasks, which would be hard to extend to general problems.
+In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
+and they combine the scores of multiple features weighted by their effectiveness.
+In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features impove the accuracy of action recognition.
+In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
+\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
+\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
 
@@
 
-%We first elaborate the formulation of our proposed algorithm.
 We first elaborate the formulation of our proposed algorithm,
 which regards the late fusion problem as a robust matrix recovery problem.
-%Then we show the details about how to use augmented Lagrangian multiplier (ALM) to solve the $\ell_{1,2}$ objective function.
-And then we present the details of using ALM extending matrix factorization to handle $\ell_{1,2}$ loss.
+Then we present the details of using ALM extending matrix factorization to handle $\ell_{1,2}$ loss.
 Finally we introduce our post-process strategy to convert the recovered label matrix to final predictions.
-
-\begin{figure}[ht]
-\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
-\caption{Framework (example of $n=10, \calC=3, m=3$)}
-\label{fig:framework}
-\end{figure}
 
@@
 Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
-Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times m}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
-Let $\bL = [ \bL_1, \bL_2, ..., \bL_\calC ]$.
+Then by applying each single classifier $f_j$ ($1 \leq j \leq m$) on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
+Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
 %%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
@@
 {\small
-$$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
+\begin{align}
+|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
+\end{align}
 }
@@
 \begin{align}\label{eq:l12_rankconstraint}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st ~&~ \rank(\bX) = p   ,
+  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}~~~~~~\st~~\rank(\bX) = p
 \end{align}
@@
 \noindent
-where $\bX \in \dsR^{n \times m\calC}$ is the underlying low rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
+where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
 and $p$ is a scalar.
@@
 
-%\begin{small}
 \begin{algorithm}[ht]
@@
 
-\WHILE{not converge}
+\WHILE{$t = 0$ or $L_1(\bE_{t+1}-\bE_{t}) \geq \epsilon$}
 
@@
 
-    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
     \STATE 1: Obtain $\bX_{t+1}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
 
-    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
     \STATE 2: Obtain $\bE_{t+1}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
@@
 \end{algorithm}
-%\end{small}
-
-%
-%\begin{small}
-%\begin{algorithm}[h!]
-%
-%\begin{algorithmic}
-%
-%\REQUIRE $\bL \in \dsR^{n \times m\calC}$, $p$ (the rank of $\bX$)
-%\ENSURE $\bX \in \dsR^{n \times m\calC}$
-%\STATE Initialize $\rho > 1$, $t = 0$, $\blambda^{(0)} = 0$, and $\mu^{(0)} > 0$.
-%
-%\WHILE{not converge}
-%
-%  \WHILE{not converge}
-%
-%    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
-%    \STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).
-%
-%    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
-%    \STATE 2: Obtain $\bE^{(t)}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).
-%
-%  \ENDWHILE
-%
-%  \STATE 3: $\blambda^{(t+1)} = \blambda^{(t)} + \mu^{(t)} (\bL - \bX^{(t+1)} - \bE^{(t+1)})$.
-%
-%  \STATE 4: $\mu^{(t+1)} = \rho \mu^{(t)}$.
-%
-%  \STATE 5: t = t + 1.
-%
-%\ENDWHILE
-%
-%\end{algorithmic}
-%\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
-%\label{alg:alm_mf}
-%\end{algorithm}
-%\end{small}
 
@@
 \label{theorem:alm_convergence}
-  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
+  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
+  and $\{\blambda_k\}$ is bounded. Any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
 \end{theorem}
@@
   \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
-              %= & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
-              %  & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
-              %= & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
-              = & || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+              = & \frac{\mu}{2} || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
@@
 The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
+In other words, we search the solution for $\bX$ in a low-rank subspace.
 Let $r$ be a known scalar.
@@
 {\small
-\begin{eqnarray}
+\begin{align}
 \M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
@@
            \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
-\end{eqnarray}
+\end{align}
 }
@@
 {\small
-\begin{eqnarray}\label{eq:tangent_vector}
+\begin{align}
+\label{eq:tangent_vector}
 &&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
@@
 \U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
-\end{eqnarray}
+\end{align}
 }
@@
 \begin{eqnarray}\label{eq:grad}
-\grad{f(\bX)} = P_{T_{\bX}\M_{r}}(\G)  ,
+\grad{f(\bX)} = P_{T_{\bX}\M_{r}}(\G)
 \end{eqnarray}
@@
 
-%\begin{small}
+\begin{lemma}
+  Assuming that $\U_{p}$, $\V_{p}$ and $\bM$ are computed by Algorithm~\ref{alg:compute_riemannian_grad},
+  we have {\small${\textnormal{grad}} f(\bX) = \U \bM \V + \U_{p} \V^{\trsp} + \U \V^{\trsp}_{p}$}.
+\end{lemma}
+
+{\small
+\begin{proof}
+\begin{align}
+\label{eq:proof_lemma1}
+       & \grad f(\bX) \\
+       & = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp}  \nonumber \\
+       & = \U(\U^{\trsp} \G \V) \V^{\trsp} + (\bR_{v} - \U \bM) \V^{\trsp} + \U (\bR_{u} - \V \bM^{\trsp})^{\trsp} \nonumber \\
+       & = P_{\U} \G P_{V} + \G \V \V^{\trsp} - \U \bM \V^{\trsp} + \U \U^{\trsp} \G - \U \bM \V^{\trsp} \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U \bM \V^{\trsp} + P_{U} \G  \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U (\U^{\trsp} \bR_{v}) \V^{\trsp} + P_{U} \G  \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U (\U^{\trsp} \G \V) \V^{\trsp} + P_{U} \G  \nonumber \\
+       & = P_{\U} \G P_{V} + (\bI - P_{U}) \G P_{V} + P_{U} \G (\bI - P_{V})  \nonumber \\
+       & = P_{\U} \G P_{V} + P_{U}^{\perp} \G P_{V} + P_{U} \G P_{V}^{\perp}  ,
+\end{align}
+\end{proof}
+}
+
 \begin{algorithm}
@@
     \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.
-
     \STATE 1. $\bR_{u} \leftarrow \G^{\trsp} \U$, $\bR_{v} \leftarrow \G \V$.   
-
     \STATE 2. $\bM \leftarrow \U^{\trsp} \bR_{v}$.    
-
     \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
-
     \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.    
-
   \end{algorithmic}
@@
 \end{algorithm}
-%\end{small}
 
-\begin{lemma}
-  Assuming that $\U_{p}$, $\V_{p}$ and $\bM$ are computed by Algorithm~\ref{alg:compute_riemannian_grad},
-  we have ${\textnormal{grad}} f(\bX) = \U \bM \V + \U_{p} \V^{\trsp} + \U \V^{\trsp}_{p}$.
-\end{lemma}
+Based on the above discussion, the solution of $\bX$ can be solved by Algorithm~\ref{alg:LRGeomCG} as following:
 
-\begin{proof}
-  The proof can be found in Appendix B.
-\end{proof}
-
-%\begin{small}
 \begin{algorithm}
@@
 \end{algorithm}
-%\end{small}
 
@@
 
-%To compute $\grad{f(\bX)}$, we need to calculate the gradient of $f(\bX)$ on Euclidean space.
-%Firstly, the gradient of $\ell(\bX)$ w.r.t. $\bX$, denoted by $\widehat{\G}$, can be calculated by
-%\begin{small}
-%\begin{eqnarray}\label{eq:grad_X_Euc}
-%\widehat{\G}_{ij} = \frac{\partial \ell(\bX)}{\partial \bX_{ij}} = \sum_{z=1}^{L-1} T_{ij}^{z} \cdot h(T_{ij}^{z} \cdot(\theta_{z} - \bX_{ij})).
-%\end{eqnarray}
-%\end{small}
-%where $ij \in \Omega$.
-Note that the gradient of $ \Upsilon (\bX)$ w.r.t.
-$\bX$ is $ \U\diag(\bsigma - \nu/\bsigma^3)\V^{\trsp}$ at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
-The gradient of $f(\bX)$ w.r.t.
-$\bX$ in Euclidian space, denoted by $\G$, can be computed by
-%\begin{small}
-%\begin{eqnarray}
-%\G = \widehat{\G} + \lambda \U\diag(\bsigma - \nu/\bsigma^3)\V^{\trsp}.
-%\end{eqnarray}
-%\end{small}
-%Once $\G$ is computed, $\grad{f(\bX)}$ can be calculated according to equation (\ref{eq:grad}). The details of computation can be found in Appendix A.
-
 \subsection{Optimization of The Subproblem of $\bE$}
@@
 Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
-%\begin{align}\label{eq:subproblem_wrt_E_1}
-%  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
-%              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
-%\end{align}
 {\small
-\begin{align}\label{eq:subproblem_wrt_E_1}
+\begin{align}
+\label{eq:subproblem_wrt_E_1}
   \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
@@
 {\small
-\begin{align}\label{eq:subproblem_wrt_E_2}
+\begin{align}
+\label{eq:subproblem_wrt_E_2}
   \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
@@
 \subsection{Post Process}
-As we recover the low rank matrix $\bX$ from the label assignment matrix $\bL$,
+As we recover the low-rank matrix $\bX$ from the label assignment matrix $\bL$,
 it needs a post process to generate the prediction label for each testing data.
@@
 \begin{itemize}
-  \item $[AVE]$ A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
+  \item \textbf{[AVE].} A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
     The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
-  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
+  \item \textbf{[VOTE].} For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
       Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
       Finally, we choose the label with the most votes to be the prediction results.
-  \item $[GATE]$ $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
+  \item \textbf{[GATE].} $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
       As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
@@
 
-\section{Empirical Studies}
+\subsection{Computation Complexity}
+
+Now we analyze the computation complexity of our proposed algorithm.
+The sub-algorithm in Section~3.3 solve the solution of $\bX$.
+The primary computation is described in Algorithms.~\ref{alg:compute_riemannian_grad} and~\ref{alg:LRGeomCG},
+which uses subspace search to optimize the solution.
+And the complexity is $T \times O((n+{\calC}m){\calC}^2)$, where $T$ is the number of iterations.
+According to \cite{vandereyckensiamjo2013low}, $T$ is less than 100 for most situations,
+and more details can be found in \cite{vandereyckensiamjo2013low}.
+The complexity of optimization on $\bE$ and post-processing can be easily calculated as $O(nm{\calC})$ and $O(nm{\calC})$.
+So, the total comlexity per iteration is $T \times O((n+{\calC}m){\calC}^2) + O(nm{\calC})$,
+which is linear by growing of $n$ and $m$, with the cubic complexity of $\calC$.
+
+Comparing with those nuclear norm based methods~\cite{gaoijcai2016robust,ye2012robust} whose computational complexity is cubic due to the presence of SVDs,
+our algorithm is more efficient for large scale problems.
+For example, \cite{gaoijcai2016robust} reportes their entire complexity is $(m{\calC})^3+n(m{\calC})^2$ per iteration.
+With the increase in the number of classifers,
+the computation costs too much to be affordable due to the cubic complexiry of $m$,
+but ours are able to solve the solution.
+
+\section{Experimental Studies}
 
@@
 Five state-of-the-art fusion methods are compared with our proposed alogrithm :
-(1)~Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
-(2)~Multiple Kernel Learning (MKL).
-MKL learn a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+\begin{itemize}
+\item Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
+\item Multiple Kernel Learning (MKL).
+MKL learns a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
 We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
-(3)~Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}. The core alogrithm in RCEC can be modified to recover X from L in~\ref{eq:l12_mf}, and the post process is same as our method.
-(4)~Feature Weighting via Optimal Thresholding(FWOT)\cite{xuiccv2013feature}.
-The author propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
-(5)~LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
+\item Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
+The core alogrithm in RCEC can be modified to recover $\bX$ from $L$ in Problem.~\ref{eq:l12_mf}, and the post process is same as our method.
+\item Feature Weighting via Optimal Thresholding (FWOT) \cite{xuiccv2013feature}.
+The authors propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
+\item LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
+\end{itemize}
 
-The parameter $\mu$ is selected from $\{0.1, 1, 5\}$ and $\rho$ is select from $\{1.01, 1.05, 1.1\}$ in all our experiments.
+The parameter $\mu$ is selected from $\{0.1, 1, 5\}$,
+$\rho$ is select from $\{1.01, 1.05, 1.1\}$
+and $\epsilon$ is select from $\{1e-2, 1e-3, 1e-4\}$ in all our experiments.
 Among different parameters, there are small differences of the prediction performance.
@@
 In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to generate $n$ instances, which are randomly labeled with $c_i, 1 \leq i \leq n, 1 \leq c_i \leq \calC$.
-And we regard these instances as the ground truth data.
-Then we randomly permute $40\%$ instances' labels, repeating $m = 15$ times to get fifteen classifiers' results.
-Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed alogrithm,
-the visualization results are illustrated in Figure~\ref{fig:ensemble_cluster}.
-
-Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different label.
-The first picture~\ref{subfig:gt_pdf} show the visualized ground truth data, which are copied $m$ times.
-And $m$ noised classifiers' results are pictured as~\ref{subfig:er_pdf}.
-We recover the low rank matrix $\bX$ from the noised matrix by using our late fusion method, which is visualized as~\ref{subfig:re_pdf}.
+And we regard these instances as the ground truth data represened by a matrix $Gt \in \dsR^{280 \times 1}$.
+Then we randomly permute $40\%$ instances' labels,
+repeating $m = 15$ times to get fifteen classifiers' results as $Er \in \dsR^{280 \times 15}$.
+Therefore, the classification error of each classifier is around 40\%.
+Then, we derive an indicator matrix from the predictions of 15 classifiers,
+and recovere this indicator matrix into the final results, $Rec \in \dsR^{280 \times 15}$, by our proposed algorithm.
+%Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed alogrithm,
+%the visualization results are illustrated in Fig.~\ref{fig:ensemble_cluster}.
+We visualize the ground truth information, classifiers' predictions and the recovered results in Fig.~\ref{fig:ensemble_cluster}.
 
@@
     }
-    \subfigure[Outlier Reject]{
+    \subfigure[Our Recovered Result]{
     \label{subfig:re_pdf}
@@
     }
-    \caption{visualized results of the synthetic dataset} \label{fig:ensemble_cluster}
+    \caption{Visualized results of the synthetic dataset.
+    We use different colors to represent different label for each instance.
+   Fig.~\ref{subfig:gt_pdf} show the visualized ground truth data,
+   and each row corresponds to one instance with the class label represented by color.
+   Fig.~\ref{subfig:er_pdf} has 15 columns, each represents one classifiers's predictions.
+   There are also 15 columns in Fig.~\ref{subfig:re_pdf}, which is generated by the recovered results from our algorithm.
+   %Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different labels.
+    %Each picture represents a $280$ instances's information with every $20$ colums corresponding to one classifier.
+    %We use different colors to represent different binary indicator predictions~(20 dimensions).
+    %For~\ref{subfig:gt_pdf}, there is the ground truth information of $280$ instances for $15$ classifiers.
+    %Obviously, the ground truth for different classifiers is the same.
+    %Each kind of color represents one class, and the ground truth picture is generated from 280 synthetic instance lables.
+    %Random noise picture~\ref{subfig:er_pdf} show 15 classifiers's prediction results while the classification accuracy for each one is about 60\%.
+    %The last picture is the recovered result generated by our algorithm.
+    Obviously, most of the outlier elements are correctly recovered by our algorithm with only a few error predictions left.
+    }
+    \label{fig:ensemble_cluster}
 \end{figure}
+
+As we can observe, our proposed algorithm significantly detect the outliers,
+and furthermore, the outlier elements are accurately converted into the right predictions while preserving consistency among all classifiers.
 
@@
 \subsection{Feature Extraction}
-We describe the details of the feature extraction for each dataset we use.
-All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
+%We describe the details of the feature extraction for each dataset we use.
+%All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
+We used the best-performing CNN models for feature extraction including ResNet~\cite{he2015deep}, GoogleNet~\cite{szegedy2015going}, or etc.
+These features are fairly state of the art.
+They have been widely used in various recent research papers and have been verified the most effective features by recent internationally recognized competitions such as the ImageNet competition~\cite{russakovsky2015imagenet}.
 
@@
 
-\subsection{Real-world Experiments}
-
-In this section, we introduce the details about our experiments on each data set,
-and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
-Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
-And the computational cost of cross-validation is not counted in FWOT and LPBoost.
-
-%\subsubsection{Experiment on UCF 101 dataset}
-For action recognition, we present the comparison results on UCF 101 dataset.
-UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
-We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
-As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by liblinear.
-Then by appling five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
-Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
-To be noted, FWOT is too slow to train, we didn't show its result (more than one day).
-
 \begin{table*}[t]
-\small
 \centering
-\caption{Mean accuracy on real-world data sets.}
 \begin{tabular}{c|c|c|c|c|c}
@@
 \end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item[*]
-  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``-''.
-\end{tablenotes}
+\caption{Mean accuracy on real-world data sets.
+FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
+so we omit these results indicated by ``-''.
+}
 \label{table:total_acc}
@@
 \begin{table*}[t]
-\small
 \centering
-\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
 \begin{tabular}{c|c|c|c|c|c}
@@
 \end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item[*]
-  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``$\infty$''.
-\end{tablenotes}
+\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.
+FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
+so we omit these results indicated by ``$\infty$''.}
 \label{table:total_time}
 \end{table*}
+
+\subsection{Real-world Experiments}
+
+In this section, we introduce the details about our experiments on each data set,
+and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
+Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
+The computational cost of cross-validation is not counted in FWOT and LPBoost.
+
+%\subsubsection{Experiment on UCF 101 dataset}
+For action recognition, we present the comparison results on UCF 101 dataset.
+UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
+We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
+As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by liblinear.
+Then by appling five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
+Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
+To be noted, FWOT is too slow to train, we do not show its result (more than one day).
 
@@
 \footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
-which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
+which occupies too much memory and still consumes long time to train,
+so we solve this problem by using sparse matrices and parallel computation in MATLAB.
 We also use `-s 2' parameters in liblinear to speedup training process.
-Results of total six contrast algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
 
@@
 
+From Table~\ref{table:total_acc}, our proposed algorithm provides significant improvement comparing with other effective late fusion methods on most datasets.
+Addtionally, our algorithm is more efficient than other late fusion methods in most situations.
+As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
+However, ours can sovle the large scale problem efficiently.
+%For example, the cost of FWOT is tremendous
+%and it takes more than one day to fuse multiple results on CIFAR and UCF-101.
+%With the growth of class number, LPBoost costs too much on data preparation affecting the overall efficiency.
+%RCEC is usually faster than ours, but ours classification performance is better than its.
+
 \subsection{Post Strategy Selection}
@@
 \begin{table}[ht]
-%\small
 \centering
-\caption{Mean Accuracy with Different Strategies}
 \begin{tabular}{c|c|c|c}
@@
 \end{tabular}
+\caption{Mean accuracy using different strategies on three datasets.}
 \label{table:strategy}
 \end{table}
+
+\subsection{Comparision with State-of-the-art}
+
+In this sub-section, we compare the performance of our algorithm with the state-of-the-art techniques.
+%we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
+We use SVM classifiers based on different features in previous experiments to make a fair comparision with some MKL based mthods.
+Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
+in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
+Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table.\ref{table:state_of_the_art}.
+
+\begin{table}[ht]
+\begin{center}
+\begin{tabular}{ c | c | c }
+    \hline
+                                              & CIFAR-10             & CIFAR-100  \\\hline
+\multirow{2}{*}{ResNet~\cite{he2016identity}} & 110, 134, 164        & 56, 110, 164  \\
+                                              & $164^{*}$, $200^{*}$ & $110^{*}$, $164^{*}$  \\\hline
+\multirow{2}{*}{WRN~\cite{zagoruyko2016wide}} & 16-10, 22-8, 28-10   & 16-10, 22-8, 28-10  \\
+                                              &    40-4, 40-8        & 40-4  \\\hline
+NIN~\cite{lin2013network}                     &     -                & -  \\ \hline
+\end{tabular}
+\end{center}
+\caption{Model selection for CIFAR-10 dataset.
+In the ResNet block, numbers repersent the depth of the selected models.
+``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
+In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
+NIN network has only one formula, so we donot list its depth.}
+\label{table:models}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{c|c|c}\hline
+                                                    &  CIFAR-10 & CIFAR-100  \\\hline
+NIN~\cite{lin2013network}                           &   8.81    &  35.67     \\\hline
+Highway~\cite{srivastava2015highway}                &   7.72    &  32.39     \\\hline
+ELU~\cite{clevert2015fast}                          &   6.55    &  24.28     \\\hline
+Pre-ResNet-1001~\cite{he2016identity}               &   4.92    &  22.71     \\\hline
+WRN-28-10~\cite{zagoruyko2016wide}                  &   4.17    &  20.50     \\\hline
+ResNeXt-29, $16\times64d$~\cite{xie2016aggregated}  &   3.58    &  17.31     \\\hline
+Ours                                                &   3.47    &  17.24     \\\hline
+\end{tabular}
+\caption{Test error of different methods on CIFAR-10 and CIFAR-100 for different architectures.
+}
+\label{table:state_of_the_art}
+\end{table}
+
+We carefully cite the best performances reported in their papers
+\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}
+As we can observe, our fusion is capable of further improving the performance of single model by a large margin.
+A single model has limited performance even with deeper depth or wider channel.
+However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
+To be noticed, our method fuses multiple single models which all perform worse than ResNeXt~\cite{xie2016aggregated},
+but can achieve low test error.
+This demonstrates the benefit of a good late fusion method.
 
@@
 
-\begin{quote}
-\begin{small}
-  \bibliographystyle{aaai}
-  \bibliography{RLF_MF}
-\end{small}
-\end{quote}
+{\small
+\bibliographystyle{ieee}
+\bibliography{egbib}
+}
 

### 2017-02-28 Algorithm/startup.m

@@ -1,0 +1,17 @@
+addpath ('Code');
+addpath ('Auxiliary');
+addpath ('SVM');
+addpath ('Data');
+addpath ('XuanyiFunction');
+addpath ('XuanyiFunction/util');
+addpath ('XuanyiFunction/experiments');
+addpath ('SVM/liblinear/matlab');
+%addpath ('SVM/libsvm/matlab');
+addpath ('caffe/matlab');
+%addpath ('MKL/liblinear-mkl/src/matlab');
+%addpath(genpath('MKL/'));
+%addpath(genpath('MKL/SVM-KM'));
+%addpath(genpath('MKL/simplemkl'));
+%addpath(genpath('MKL/SVM-KMExample'));
+%addpath ('/home/dongxuanyi/mosek/7/toolbox/r2013a');
+%addpath ('/home/dongxuanyi/mosek');

### 2017-02-28 Algorithm/visual/Convert2Image.m

@@ -1,0 +1,19 @@
+function I = Convert2Image(X, RGBs, len)
+    M = numel(X);
+    [N, K] = size(X{1});
+    I = uint8(zeros(N*len, M*K, 3));
+    %[RGBs] = select_color(K);
+    assert(size(RGBs,1) == K);
+    for i = 1:M
+       assert(all([N,K] == size(X{i})));
+       RR = i * K;
+       LL = RR - K + 1;
+       for j = 1:N
+           [~,id] = max(X{i}(j,:));
+           R = j * len; L = R - len + 1;
+           rgb = reshape(RGBs(id,:), 1, 1, 3);
+           I(L:R,LL:RR,:) = repmat(rgb, R-L+1, RR-LL+1, 1);
+       end
+    end
+
+end

### 2017-02-28 Algorithm/visual/SolverSFEC.m

@@ -1,0 +1,69 @@
+function [X] = SolverSFEC(L, M, K, p, mu, max_iters)
+% results is N * M matrix, donate M classifier's results
+time_begin = tic;
+assert( size(L,2) == M * K );
+% First Convert results to cluster assignments
+% Apply ALM Optimization 
+% min ||X-L||_(1,2) , s.t. rank(X) <= k, s.t X = UV, U \belong R(N*k)
+% The augmented Lagrangian function:
+% Lagrangian = ||E||1,2 + <lamda, L-X-E> + mu/2*||L-X-E||^2_F
+% lamda is a MK * N matrix
+N = size(L, 1);
+M = size(L, 2);
+% LRGeomCG :::: Initialize 
+lamda = zeros(N, M); E = zeros(N, M);
+%max_iters = 100;
+fprintf('Initialize paramters: p : %.4f, mu : %.4f, size(L) : [%d,%d]\n',p,mu,size(L));
+
+% Initialize LRGeomCG
+Omega = (1:N*M)';
+prob = get_prob(L,Omega,K);
+x0 = make_start_x(prob);
+options = default_opts();
+
+previous_norm = -100;
+time_begin = tic;
+for iter = 1:max_iters
+    tic;
+    fprintf('%03d/%03d :: ', iter, max_iters);
+    % Obtain X(t) via LRGeomCG
+    X_verse = L - E + (lamda / mu);
+    %X = wrapCG(X_verse, K);
+    %prob = get_prob(X_verse,Omega,K);
+    prob.data = reshape(X_verse, numel(L), 1);
+    prob.temp_omega = sparse(prob.Omega_i, prob.Omega_j, prob.data*1,prob.n1,prob.n2,prob.m);
+    %data_time = toc;
+    %assert(isempty(find(AA~=BB)));
+    [x0,~] = LRGeomCG(prob, options,x0);
+    %CG_time = toc;
+    X = x0.U * diag(x0.sigma) * x0.V';
+    
+    % Obtain E(t) via soft-thresholding
+    Y = L - X + (lamda / mu);
+    alpha = 2 / mu;
+    E = zeros(N, M);
+    for col = 1:M
+        norm2 = norm(Y(:,col));
+        if norm2 > alpha
+            E(:,col) = Y(:,col) * (1-alpha/norm2);
+        end
+    end
+    lamda = lamda + mu * (L - X - E);
+    mu = mu * p;
+    temp = norm(E, 'fro');
+    termination = false;
[…]

### 2017-02-28 Algorithm/visual/generate.m

@@ -1,0 +1,21 @@
+function [GT, ER] = generate(N, M, K, error_ratio)
+X = rand(N,K);
+Y = max(X, [], 2);
+X = X == repmat(Y, 1, K);
+FinalX = cell(M+1, 1);
+FinalX{1} = X;
+for index = 1:M
+    idx = randperm(N, ceil(error_ratio*N));
+    Y = X;
+    for i = 1:numel(idx)
+        Y(idx(i),:) = 0;
+        Y(idx(i),randperm(K,1)) = 1;
+    end
+    FinalX{index+1} = Y;
+end
+ER = FinalX;
+GT = cell(M+1, 1);
+for i = 1:M+1, GT{i} = X; end
+%I = Convert2Image(FinalX,4);
+%imshow(I);
+end

### 2017-02-28 Algorithm/visual/select_color.m

@@ -1,0 +1,18 @@
+function [RGBs] = select_color(num)
+    A = ceil(num^(1/3));
+    B = ceil(sqrt(num/A));
+    C = ceil(num / A / B);
+    A = ceil((1:A) * 255 / A);
+    assert(all(A<=255) && all(A>=1));
+    B = ceil((1:B) * 255 / B);
+    C = ceil((1:C) * 255 / C);
+    RGBs = [];
+    for i = 1:numel(A)
+        for j = 1:numel(B)
+            for k = 1:numel(C)
+                RGBs = [RGBs; [A(i), B(j), C(k)]];
+            end
+        end
+    end
+    RGBs = uint8(RGBs(randperm(size(RGBs,1),num), :));
+end

### 2017-02-28 Algorithm/visual/wrap_vis.m

@@ -1,0 +1,39 @@
+N = 10;
+M = 3;
+K = 3;
+error_ratio = 0.30;
+pix_len = 5;
+[GT, ER] = generate(N, M, K, error_ratio);
+%I = Convert2Image(ER, 5);
+ER = ER(2:end);
+GT = GT(2:end);
+ER{1} = GT{1};
+ER{2} = GT{1};
+L = [];
+for i = 1:numel(ER)
+    L = [L, ER{i}];
+end
+p  = 1.01;
+mu = 1;
+max_iters = 200;
+[X] = SolverSFEC(L, numel(ER), K, p, mu, max_iters);
+beta = 5;
+max_iters = 300;
+%RCEC = SolverRCEC(L, numel(ER), K, beta, max_iters);
+Recover = cell(numel(ER), 1);
+%RCEC_C  = cell(numel(ER), 1);
+for i = 1:numel(ER)
+    Y = X(:,i*K-K+1:i*K);
+    %Y = real(Y > 0.5);
+    Recover{i} = Y;
+    %RCEC_C{i} = RCEC(:,i*K-K+1:i*K);
+end
+RGBs = select_color(K);
+RI = Convert2Image(Recover, RGBs, pix_len);
+EI = Convert2Image(ER, RGBs, pix_len);
+GI = Convert2Image(GT, RGBs, pix_len);
+%GaoI = Convert2Image(RCEC_C, RGBs, pix_len);
+gap = uint8(zeros(N*pix_len,20,3)+255);
+%imshow([GI,gap,EI,gap,RI,gap,GaoI]);
+imshow([GI,gap,EI,gap,RI]);
+% saveas(gcf,'recover','epsc');

### 2017-03-02 egpaper_for_review.tex
iccv v1.1

@@
 such as textures of images and frequencies of text data.
-When building a prediction model, the model trained on one kind of feautures could be biased and hence may incur unsatisfactory performance.
+When building a prediction model, the model trained on one kind of features could be biased and hence may incur unsatisfactory performance.
 Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.
 
-%% late fusion is a common sigle model -> single feature, 介绍late fusion
+%% late fusion is a common single model -> single feature, 介绍late fusion
 Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
@@
 Notations are introduced shortly.).
-Due to the fact that the $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction,
-we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
-Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth loss.
-We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
+The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
+However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
+Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
+Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
+We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.
 
@@
   \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
-  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss. 
+  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to non-smooth $\ell_{1,2}$ loss. 
   %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
@@
 which learns the weights, thresholding and smoothing parameters in a joint framework.
-However, all these mkl based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.
+However, all these MKL based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.
 
@@
 However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
+Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
+but they require the incoherent matrix assumption and a fresh measurements at each iteration.
+Thus their method can not be guaranteed to converge the global solution in our work.
+In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.
 
-Some other fusion algorithms are propsed for specific tasks, which would be hard to extend to general problems.
+Some other fusion algorithms are proposed for specific tasks, which would be hard to extend to general problems.
 In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
 and they combine the scores of multiple features weighted by their effectiveness.
-In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features impove the accuracy of action recognition.
+In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
 In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
@@
 \noindent
-Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a nonsmooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
+Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
 In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).
@@
 
-Most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth $\ell_{1,2}$ loss used in Problem~(\ref{eq:l12_mf}).
+Most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth $\ell_{1,2}$ loss used in Problem~(\ref{eq:l12_mf}).
 In this section, we present an ALM based algorithm to optimize Problem~(\ref{eq:l12_mf}).
@@
 
+The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
+but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
+We proof the convergence of ALM for solving a non-convex problem relying on the gradient, as following:
+
 \begin{theorem}
@@
   Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
-  and $\{\blambda_k\}$ is bounded. Any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
+  and $\{\blambda_k\}$ is bounded.
+  As $k \to \infty$, the gradient of $\calL$ vanishes,
+  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
 \end{theorem}
@@
 where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
-\U^{\trsp}\U = \I \}$ dentoes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
+\U^{\trsp}\U = \I \}$ denotes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
 We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
@@
 where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bN$,
-%and $\alpha = \frac{2}{\mu}$.
 and $\alpha = \frac{1}{2}$.
@@
       As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
-      The similar process as the first strategy is applied to the above results, which predictes the final labels.
+      The similar process as the first strategy is applied to the above results, which predicts the final labels.
 \end{itemize}
 According to the experiments, the last strategy ``GATE'' outperforms than the others.
-So We choose the last one as the post process for our fusion method and analyse inner reasons during the experiment section.
+So We choose the last one as the post process for our fusion method and analyze inner reasons during the experiment section.
 
@@
 And the complexity is $T \times O((n+{\calC}m){\calC}^2)$, where $T$ is the number of iterations.
-According to \cite{vandereyckensiamjo2013low}, $T$ is less than 100 for most situations,
-and more details can be found in \cite{vandereyckensiamjo2013low}.
+According to \cite{vandereycken2013lowrank}, $T$ is less than 100 for most situations,
+and more details can be found in \cite{vandereycken2013lowrank}.
 The complexity of optimization on $\bE$ and post-processing can be easily calculated as $O(nm{\calC})$ and $O(nm{\calC})$.
-So, the total comlexity per iteration is $T \times O((n+{\calC}m){\calC}^2) + O(nm{\calC})$,
+So, the total complexity per iteration is $T \times O((n+{\calC}m){\calC}^2) + O(nm{\calC})$,
 which is linear by growing of $n$ and $m$, with the cubic complexity of $\calC$.
@@
 For example, \cite{gaoijcai2016robust} reportes their entire complexity is $(m{\calC})^3+n(m{\calC})^2$ per iteration.
-With the increase in the number of classifers,
-the computation costs too much to be affordable due to the cubic complexiry of $m$,
+With the increase in the number of classifiers,
+the computation costs too much to be affordable due to the cubic complexity of $m$,
 but ours are able to solve the solution.
@@
 In this section, we first visualize the results of our approach on the synthetic dataset.
-Then we evaluate the perfomance on eight publicly available real-world data sets,
+Then we evaluate the performance on eight publicly available real-world data sets,
 UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
@@
 
-%Details on feature extraction for each dataset are described in the second subsection.
-%, and the confidence scores are set as outputs of LIBLINEAR.
-%Then we put the confidence scores as the input X of our alogrithm.
-
-Five state-of-the-art fusion methods are compared with our proposed alogrithm :
+Five state-of-the-art fusion methods are compared with our proposed algorithm :
 \begin{itemize}
@@
 In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to generate $n$ instances, which are randomly labeled with $c_i, 1 \leq i \leq n, 1 \leq c_i \leq \calC$.
-And we regard these instances as the ground truth data represened by a matrix $Gt \in \dsR^{280 \times 1}$.
+And we regard these instances as the ground truth data represented by a matrix $Gt \in \dsR^{280 \times 1}$.
 Then we randomly permute $40\%$ instances' labels,
@@
 Then, we derive an indicator matrix from the predictions of 15 classifiers,
-and recovere this indicator matrix into the final results, $Rec \in \dsR^{280 \times 15}$, by our proposed algorithm.
-%Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed alogrithm,
+and recovery this indicator matrix into the final results, $Rec \in \dsR^{280 \times 15}$, by our proposed algorithm.
+%Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed algorithm,
 %the visualization results are illustrated in Fig.~\ref{fig:ensemble_cluster}.
@@
 and ``pool5'' of ResNet-50,101,152~\cite{he2015deep}.
-We use the offical pre-trained model provided by Caffe Model Zoo
+We use the official pre-trained model provided by Caffe Model Zoo
 \footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}
@@
 
-%\subsubsection{Experiment on UCF 101 dataset}
 For action recognition, we present the comparison results on UCF 101 dataset.
-UCF101 contains 13320 videos collected from YouTube, categoried into 101 human action classes.
+UCF101 contains 13320 videos collected from YouTube, categorized into 101 human action classes.
 We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
-As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by liblinear.
-Then by appling five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
+As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by LIBLINEAR.
+Then by applying five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
 Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
@@
 
-In CIFAR-10 dataset, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
+In CIFAR-10 dataset, totally 60000 32x32 color pictures are categorized into 10 classes, with 6000 pictures per class.
 There are 50000 training data and 10000 testing data.
@@
 so we solve this problem by using sparse matrices and parallel computation in MATLAB.
-We also use `-s 2' parameters in liblinear to speedup training process.
+We also use `-s 2' parameters in LIBLINEAR to speedup training process.
 Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
-
-%\subsubsection{Experiment on Cifar100 dataset}
 
@@
 Detailed results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
-
-%\subsubsection{Experiment on Oxford-IIIT-Pet dataset}
 
@@
 Since each image may contain more than one label, we filter the multi-label images to obtain 6146 clean data.
-There is similar procesure of sampling, classification and fusion as in Oxford-IIIT-Pet.
+There is similar procedure of sampling, classification and fusion as in Oxford-IIIT-Pet.
 
 From Table~\ref{table:total_acc}, our proposed algorithm provides significant improvement comparing with other effective late fusion methods on most datasets.
-Addtionally, our algorithm is more efficient than other late fusion methods in most situations.
+Additionally, our algorithm is more efficient than other late fusion methods in most situations.
 As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
-However, ours can sovle the large scale problem efficiently.
+However, ours can solve the large scale problem efficiently.
 %For example, the cost of FWOT is tremendous
@@
 In this section, we compare three proposed post strategies on three small datasets: Wikipedia~\cite{rasiwasia2010new}, Oxford Flowers 17~\cite{nilsback2006visual} and Pascal Sentence~\cite{Li2006One}.
-Wikipedia dataset contains paragraphs of text for each picture, and total 2866 image-text pairs are categoried into 10 class.
+Wikipedia dataset contains paragraphs of text for each picture, and total 2866 image-text pairs are categorized into 10 class.
 Only the image label annotation is used in our experiments.
@@
 Oxford Flowers 17 has 17 flower categories with 80 images for each class.
-Pascal Sentence contains 1000 images annotated by caption information and categoried into twenty classes.
+Pascal Sentence contains 1000 images annotated by caption information and categorized into twenty classes.
 Fifty percent of data are sampled as training set and the others as testing set, and experiments are repeated five times on above three datasets.
@@
 
-\subsection{Comparision with State-of-the-art}
+\subsection{Comparison with State-of-the-art}
 
@@
 %we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
-We use SVM classifiers based on different features in previous experiments to make a fair comparision with some MKL based mthods.
+We use SVM classifiers based on different features in previous experiments to make a fair comparison with some MKL based methods.
 Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
@@
 \caption{Model selection for CIFAR-10 dataset.
-In the ResNet block, numbers repersent the depth of the selected models.
+In the ResNet block, numbers represent the depth of the selected models.
 ``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
 In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
-NIN network has only one formula, so we donot list its depth.}
+NIN network has only one formula, so we do not list its depth.}
 \label{table:models}
@@
 %Our proposed algorithm is based on matrix factorization, which is unclear to consider smooth loss function from earlier research.
-Existing matrix factorization algorithms usually consider smooth loss, while it is unclear how to extend them to handle nonsmooth robust loss, \eg, $\ell_{1,2}$ loss.
-We propose an ALM based algorithm to solve matrix factorization problems with nonsmooth loss.
+Existing matrix factorization algorithms usually consider smooth loss, while it is unclear how to extend them to handle non-smooth robust loss, \eg $\ell_{1,2}$ loss.
+We propose an ALM based algorithm to solve matrix factorization problems with non-smooth loss.
 %Specifically, our proposed algorithm first rejects outliers on a label indicator matrix by $\ell_{1,2}$ loss,

### 2017-03-12 egpaper_for_review.tex
small change

@@
 Notations are introduced shortly.).
+\yanred{
 The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
@@
 Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
+}
 Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
@@
 However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
+\yanred{
 Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
@@
 In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.
+}
 
@@
 
+\yanred{
 The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
 but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
-We proof the convergence of ALM for solving a non-convex problem relying on the gradient, as following:
+In addition, we proof the convergence of ALM for solving a non-convex problem relying on the gradient,
+rather than the (xxxxxxxx) for convex problem,
+as following:
+}
 
+\yanred{
 \begin{theorem}
@@
 \end{theorem}
+}
 
@@
 
+\yanred{
+\textbf{Reproducibility.}
+Our implementation is modified from the open-sourced LRGeomCG
+\cite{vandereycken2013lowrank}\footnote{http://www.unige.ch/math/vandereycken/matrix\_completion.html}.
+We will release the source code soon.
+}
+
 \subsection{Synthetic Experiments}
@@
 and furthermore, the outlier elements are accurately converted into the right predictions while preserving consistency among all classifiers.
-
-%% Flower 17 Time [3.14] [229] [0.26] [1.62]
 
@@
 \centering
-\begin{tabular}{c|c|c|c|c|c}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
@@
 RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%          &   90.92\%          \\
-FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
-LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
-\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
+FWOT                & -                & -                & -                & \textbf{92.90\%} &   91.20\%          \\
+LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%          &   \textbf{91.42\%} \\\hline
+\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%} &   90.98\%          \\
 \hline
@@
 \centering
-\begin{tabular}{c|c|c|c|c|c}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
 Method              & UCF-101         & CIFAR-10        & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
-RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
+RCEC                & \textbf{86.60}  & 81.41           &  \textbf{255.51} & \textbf{18.82}  &   16.45         \\
 FWOT                & $\infty$        & $\infty$        &  $\infty$        & 61697           &   19674         \\
-LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
-Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
+LPBoost             & 110.81          & 72.45           &  4750.9          & 43.67           &   \textbf{7.46} \\\hline
+Ours                & 421.23          & \textbf{5.384}  &  417.26          & 76.16           &   16.21         \\
 \hline
@@
 Then by applying five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
-Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
+Results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}, in which we illustrate the performance of six fusion methods.
 To be noted, FWOT is too slow to train, we do not show its result (more than one day).
-
-%\subsubsection{Experiment on Cifar10 dataset}
 
@@
 We also use `-s 2' parameters in LIBLINEAR to speedup training process.
-Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
 
@@
 Training and comparison process are the same as CIFAR-10.
-Detailed results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+Detailed results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
 
@@
 We repeat the sample , training and fusion process five times to get fair results.
-The comparison results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
+The comparison results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
 
@@
 As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
-However, ours can solve the large scale problem efficiently.
-%For example, the cost of FWOT is tremendous
-%and it takes more than one day to fuse multiple results on CIFAR and UCF-101.
-%With the growth of class number, LPBoost costs too much on data preparation affecting the overall efficiency.
-%RCEC is usually faster than ours, but ours classification performance is better than its.
+\yanred{
+However, the time consumption of ours is acceptable in all experiments and quite fast on CIFAR-10/VOC2007.
+In conclusion, our method can solve the large scale problem efficiently.
+}
 
@@
 \centering
-\begin{tabular}{c|c|c|c}
+\begin{tabular}{|c|c|c|c|}
 \hline
@@
 in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
-Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table.\ref{table:state_of_the_art}.
+Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table~\ref{table:state_of_the_art}.
 
@@
 \begin{center}
-\begin{tabular}{ c | c | c }
+\begin{tabular}{| c | c | c |}
     \hline
@@
 \centering
-\begin{tabular}{c|c|c}\hline
-                                                    &  CIFAR-10 & CIFAR-100  \\\hline
+\begin{tabular}{|c|c|c|}\hline
+    Methods                                         &  CIFAR-10       & CIFAR-100           \\\hline
 NIN~\cite{lin2013network}                           &   8.81          &  35.67              \\\hline
@@
 ResNeXt-29, $16\times64d$~\cite{xie2016aggregated}  &   3.58          &  17.31              \\\hline
-Ours                                                &   3.47    &  17.24     \\\hline
+Ours                                                &   \textbf{3.47} &  \textbf{17.24}     \\\hline
 \end{tabular}
@@
 We carefully cite the best performances reported in their papers
-\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}
+\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}.
+\yanred{
 As we can observe, our fusion is capable of further improving the performance of single model by a large margin.
@@
 This demonstrates the benefit of a good late fusion method.
+}
 

### 2017-03-17 egpaper_for_review.tex
finish iccv

@@
 
+\newcommand\mycomment[1]{}
+
+\def\ranksym{p}
+\def\symp{r}
+
+\def\calP{\mathcal{P}}
 \def\M{\mathcal{M}}
@@
 
-\def\yanred{\textcolor{red}}
+\def\yanred{\textcolor{black}}
 \def\yanblue{\textcolor{blue}}
+\def\kuired{\textcolor{red}}
 %%%%%
@@
 \begin{abstract}
-In many real-world applications, data can be represented in multiple ways or multi-view features,
-in order to describe various characteristics of data.
-In this way, it could often improve the prediction performance by taking advantage of these feature together.
+In many real-world applications, data can be represented by multiple ways or multi-view features, in order to describe various characteristics of data.
+In this sense, the prediction performance can be significantly improved by taking advantages of these features together.
 Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
-However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
-Therefore, there is a requirement of outlier rejection while preserving consistency among different classifier results.
-In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources,
-which could avoid the performance degeneration caused by the controversy of multiple features on test data.
-Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.
+However, it is ubiquitous that different features dispute the prediction on the same data with each other, leading to  performance degeneration.
+%Therefore, outlier detection is crucial when combining the predictions of different features.
+In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources,
+aiming to avoid the performance degeneration caused by the controversy of multiple features.
+In this way, the consistency of results by various features can be preserved, which can relieve the performance degeneration.
+Extensive experiments demonstrate efficacy of the proposed method on outlier detection and performance improvement,
+which outperforms the previous state-of-the-art late fusion algorithms on most datasets.
 
@@
 %% late fusion is a common single model -> single feature, 介绍late fusion
-Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
+Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features~\cite{ye2012robust,xuiccv2013feature,lai2015learning,vanicassp2014late}.
 A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{resource/frame_work.pdf}
+\includegraphics[width=0.46\textwidth]{resource/frame_work.pdf}
 \end{center}
@@
 
-To prevent from the expensive nuclear norm minimization,
+To avoid the expensive nuclear norm minimization,
 in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
 Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
-As for outlier detection,
-we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
+This is a hard constraint, and it is different from~\cite{gaoijcai2016robust,ye2012robust} which introduce a soft constraint on the low-rank property.
+On the other hand, to remove the abnormal predictions generated by individual features, we propose to filter out these inconsistent results by using the $\ell_{1,2}$ regularization (See Fig.\ref{fig:framework}.
 Notations are introduced shortly.).
 \yanred{
-The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
-However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
-Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
+Specially, $\ell_{1,2}$ loss preserves the fidelity within each column by $\ell_{2}$ loss in the vertical direction and is robust to sparse errors across all the columns by $\ell_{1}$ loss in the horizontal direction.
+Compared to $\ell_{1,2}$ loss, $\ell_{2}$ loss is sensitive to outliers, so that may not produce robust and satisfactory predictions.
+$\ell_{1}$ loss is not sensitive to outliers, but not capable to detect the abnormal features which generate corrupted results.
 }
-Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
-We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.
+In addition, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
+Thus, we in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.
 
-The main contributions of this work are summarized as below:
+The main contributions of this work are summarized as follows:
 \begin{itemize}
-  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
-  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to non-smooth $\ell_{1,2}$ loss. 
+  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem, which is the first attempt to introduce a hard constraint on the low-rank property to the late fusion problem.
+      Our model intuitively removes inconsistent predictions made by abnormal features and preserves the consistency of predictions from different sources.
+  \item We propose an ALM-based algorithm to enable matrix recovery algorithms to handle non-smooth $\ell_{1,2}$ loss, rather than a simple least square loss which has been frequently studied in literature.
   %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
   %It is capable of handling large scale problems.
+  \item We provide theoretical convergence analysis for the proposed robust matrix recovery algorithm.
   \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
@@
 
-MKL based method is a simple but efficient way to combine different features for multi-model fusion,
-and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
+%MKL based method is a simple but efficient way to combine different features for multi-model fusion,
+%and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
+MKL is a common way to combine different features for multi-model fusion.
 In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel.
-In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
-In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
+Gehler \etal \cite{gehler2009feature} propose boosting approaches to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
+The authors of \cite{natarajan2012multimodal} propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
 In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
 which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
-In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values,
+Xu \etal \cite{xuiccv2013feature} propose an optimization algorithm to combine diverse decision values,
 which learns the weights, thresholding and smoothing parameters in a joint framework.
@@
 Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
-Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
-In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
+Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,Mishra2012,ngonips2012scaled}.
+For instance, in~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
 In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
@@
 In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
-The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
+%The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
 In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
@@
 In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
-However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
-\yanred{
-Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
+In \cite{jain2013low} the authors propose a alternating minimization method for matrix factorization with a global optimality guarantee,
 but they require the incoherent matrix assumption and a fresh measurements at each iteration.
-Thus their method can not be guaranteed to converge the global solution in our work.
-In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.
-}
+Thus their method cannot be guaranteed the global optimality in our work.
+In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method may converge faster than the alternating minimization approach.
+However, most existing matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
 
-Some other fusion algorithms are proposed for specific tasks, which would be hard to extend to general problems.
-In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
+Some other fusion algorithms are proposed for specific tasks.
+The authors of \cite{zheng2015query} estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
 and they combine the scores of multiple features weighted by their effectiveness.
-In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
+Zha \etal \cite{zha2015exploiting} use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
 In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
@@
 \cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
+The authors in~\cite{vanicassp2014late} point out that missing values in predictions can be a challenge for late fusion due to the absence of features.
+These special designed fusion algorithms can be hard to extend to general problems, being lack of generalization.
 
@@
 On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
-{\small
-\begin{align}
-|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
-\end{align}
-}
-\noindent
-Thus, the proposed model can be written as below:
-{\small
+$
+|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }  .
+$
+Thus, a general formulation of recovering the underlying low-rank label matrix can be written as follows:
+{
 \begin{align}\label{eq:l12_rankconstraint}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}~~~~~~\st~~\rank(\bX) = p
+  \min_{\bX} ~&~ || \calP_{\Omega} (\bL - \bX) ||_{1,2}~~~~~~\st~~\rank(\bX) = p
 \end{align}
@@
 where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
+$\Omega$ denotes a subset containing the indices of the observed entries,
 and $p$ is a scalar.
-In our setting, to preserve the consistency among various classifiers, we set $p = \calC$.
+Here $\calP_{\Omega}$ denotes the orthogonal projection onto the linear space of matrices support on $\Omega: \calP_{\Omega}(\bX) = \bX_{ij}$ if $(ij) \in \Omega$; $\calP_{\Omega} = 0$ otherwise.
+This includes some cases where missing elements may occur~\cite{vanicassp2014late}.
+In our setting, to preserve the consistency among various classifiers, we set the hard constraint of the rank, \ie, $p = \calC$.
 
 It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
-We hence transform the original problem as a matrix factorization formulation as below:
-{\small
+We hence transform the original problem as a matrix factorization formulation as follows:
+{
 \begin{align}\label{eq:l12_mf}
-  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
-         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
+  \min_{\bX} || \calP_{\Omega}(\bL - \bX) ||_{1,2} ,~  \st~ \rank(\bX) = p  .
 \end{align}
@@
 
-  \STATE 3: $\blambda_{t+1} = \blambda_{t} + \mu_{t} (\bL - \bX_{t+1} - \bE_{t+1})$.
+  \STATE 3: $\blambda_{t+1} = \blambda_{t} + \mu_{t} (\calP_{\Omega}{(\bL - \bX_{t+1} - \bE_{t+1})})$.
 
@@
 
-By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
-{\small
+By introducing a new variable $\calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)$, we can develop Problem~(\ref{eq:l12_mf}) as below:
+{
 \begin{align}\label{eq:mf_l21_constrained}
   \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
-  \st             ~&~ \bE = \bL - \bX  ,   \nonumber \\
-                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
+  \st             ~&~ \calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)  ,~ \rank(\bX) = p  .
 \end{align}
@@
 The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
-{\small
+{
 \begin{align}\label{eq:lagrangian_l21}
-  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle      \nonumber \\
-                                    & + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
+  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle      \nonumber \\
+                                    & + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2
 \end{align}
@@
 \noindent
-where $\bX = \bU \bV$, $\mu$ is a scalar,
+where $\rank (\bX) = p$, $\mu$ is a scalar,
 and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
@@
 Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.
+The following lemma and theorem provide the theoretical convergence guarantee of the proposed algorithm.
+We emphasize that our problem is a non-convex problem with a rank constraint, which is rarely studied in previous literatures.
 
-\yanred{
-The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
-but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
-In addition, we proof the convergence of ALM for solving a non-convex problem relying on the gradient,
-rather than the (xxxxxxxx) for convex problem,
-as following:
+\begin{lemma}
+Given that the sequence $\{ \mu_{t} \}$ is always increasing, $\mu_{0} > 0$ and $\blambda_{0} = 0$, the sequence $\{ \blambda_{t} \}$ computed by Algorithm~\ref{alg:alm_mf} is bounded.
+\end{lemma}
+
+\begin{proof}
+  The proof can be found in Appendix A.
+  \mycomment{
+  By the optimality of $\bE_{t+1}$ in Step 2 in Algorithm~\ref{alg:alm_mf}, we have the sub-differential of $\calL$ w.r.t. $\bE$ as zeros:
+  {
+  \begin{align}
+  \label{eq:derivatives_calL_E}
+    0 & \in \frac{\calL(\bX_{t+1}, \bE_{t}, \blambda_{t}, \mu_{t})}{\bE_{t+1}} \nonumber \\
+      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t} + \mu_{t} (\calP_{\Omega} (\bL - \bX_{t+1} - \bE_{t+1})) \nonumber \\
+      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t+1}   \nonumber \\
+    \Rightarrow & -\blambda_{t+1} \in \partial(|| \bE_{t+1} ||_{1,2})  .
+  \end{align}
   }
+  \noindent
+  Consider the computation of $\bE_{t+1}$ in Eq~(\ref{eq:column_wise_soft_thresholding}), which is associated with $\bL, \bX_{t+1}$, $\blambda_{t}$ and $\mu_{t}$.
+  $\bL$ is the observation and thus bounded.
+  $\bX_{t+1}$ is bounded due to the convergence guarantee of Step 1 in Algorithm~\ref{alg:alm_mf}~\cite{vandereycken2013lowrank}.
+  $\{ \blambda_{t} \}$ is initialized by setting $\blambda_{0} = 0$ and $\{ \mu_{t} \}$ is non-decreasing.
+  Thus when updating by Algorithm~\ref{alg:alm_mf}, $\bE_{t+1}$, $\partial(\bE_{t+1})$ and $\blambda_{t}$ are all bounded accordingly as $t$ increases.
+  This completes the proof.
+  }
+\end{proof}
 
-\yanred{
 \begin{theorem}
 \label{theorem:alm_convergence}
-  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
-  and $\{\blambda_k\}$ is bounded.
-  As $k \to \infty$, the gradient of $\calL$ vanishes,
+  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf}.
+  As $k \to \infty$, the gradients of $\calL$ w.r.t. $\bX$ and $\bE$ vanish,
   thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
 \end{theorem}
-}
 
+%\vspace{1cm}
 \begin{proof}
 \label{proof:proof_AA}
-  The proof can be found in Appendix A.
+  The proof can be found in Appendix B.
 \end{proof}
 
-\subsection{Optimization of The Subproblem of $\bX$}
+\subsection{Subproblem Optimization w.r.t. $\bX$}
 
-Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
-{\small
+To update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
+{
 \begin{align}\label{eq:langrangian_wrt_X}
-  \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
-              = & \frac{\mu}{2} || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+  \calL (\bX) = & \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2  \nonumber  \\
+              = & \frac{\mu}{2} || \calP_{\Omega} (\bM - \bX) ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
@@
 Hence, we derive the following subproblem \wrt. $\bX$:
-{\small
+{
 \begin{align}\label{eq:subproblem_wrt_X}
-  \min_{\bX} ~&~ || \bM - \bX ||_F^2    \nonumber \\
-  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}   .
+  \min_{\bX} || \calP_{\Omega} (\bM - \bX) ||_F^2,~ \st~ \rank(\bX) = p.
 \end{align}
@@
 
-The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
+The key idea of manifold optimization is that the update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
 In other words, we search the solution for $\bX$ in a low-rank subspace.
-Let $r$ be a known scalar.
-A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
-{\small
+A smooth manifold of fixed-rank-$\ranksym$ matrices is defined as~\cite{vandereycken2013lowrank}:
+{
 \begin{align}
-\M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
-       &=& \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{r}^{n}, \V \in
-           \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
+\M_{\ranksym} &= \{\bX\in \R^{n\times m\calC}: \rank(\bX) = \ranksym\} \nonumber \\
+       &= \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{\ranksym}^{n}, \V \in
+           \textrm{St}_{\ranksym}^{m\calC}, ||\bsigma||_0 = \ranksym\} \nonumber
 \end{align}
@@
 \noindent
-where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
-\U^{\trsp}\U = \I \}$ denotes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
-We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
-which is obtained as below
-{\small
+where $\textrm{St}_{\ranksym}^{n} = \{\U \in \R^{n\times \ranksym}:
+\U^{\trsp}\U = \I \}$ denotes the Stiefel manifold of $n \times \ranksym$ real and orthonormal matrices.
+We denote the tangent space by $T_{\bX}\M_{\ranksym}$ of $\M_{\ranksym}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
+which is obtained as below:
+{
 \begin{align}
 \label{eq:tangent_vector}
-&&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
-\U\V_p^{\trsp}: \bM \in \R^{r\times r}, \nonumber\\ && \U_p \in \R^{n\times r},
-\U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
+&&T_{\bX}\M_{\ranksym} =  \{\U\bM\V^{\trsp} \!\!+\! \U_{\symp} \V^{\trsp} \!\!+\!
+\U\V_{\symp}^{\trsp}: \bM \in \R^{\ranksym \times \ranksym}, \nonumber\\ && \U_{\symp} \in \R^{n\times \ranksym},
+\U_{\symp}^{\trsp}\U = \0, \V_{\symp} \in \R^{m\calC \times \ranksym}, \V_{\symp}^{\trsp}\V = \0\}.
 \end{align}
@@
 \noindent
-One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{r}$,
-with $\bX \in \M_{r}$ and ${\bA},{\bB} \in T_{\bX}\M_{r}$,
-then $\M_{r}$ becomes a Riemannian manifold by restricting
+One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{\ranksym}$,
+with $\bX \in \M_{\ranksym}$ and ${\bA},{\bB} \in T_{\bX}\M_{\ranksym}$,
+then $\M_{\ranksym}$ becomes a Riemannian manifold by restricting
 $\langle\bA,\bB\rangle$
 to the \emph{tangent bundle}, defined as the disjoint union of all tangent spaces:
-$T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
-         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \bP \in T_{\bX}\M_{r}\}.$
+$T\M_{\ranksym} = \bigcup_{\bX\in \M_{\ranksym}}\{\bX\} \times T_{\bX}\M_{\ranksym}
+         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{\ranksym}, \bP \in T_{\bX}\M_{\ranksym}\}.$
 
-Let $f(\bX) = || \bM - \bX ||_F^2$.
+Let $f(\bX) = ||\calP_{\Omega} (\bM - \bX) ||_F^2$.
 %Suppose that $\G$ is the gradient of the smooth function $f(\bX)$ in Euclidean space at $\bX = \U\diag(\bsigma)\V^{\trsp} $.
 Suppose that $\G = \nabla f(\bX)$ in Euclidean space at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
-Then, according to~\cite{vandereycken2013lowrank}, the Riemannian gradient of $f(\bX)$ on $\M_r$ is given as the orthogonal
+Then, according to~\cite{vandereycken2013lowrank}, the Riemannian gradient of $f(\bX)$ on $\M_\ranksym$ is given as the orthogonal
 projection of $\G$ onto the tangent space at $\bX$:
-{\small
+{
 \begin{eqnarray}\label{eq:grad}
-\grad{f(\bX)} = P_{T_{\bX}\M_{r}}(\G)
+\grad{f(\bX)} = P_{T_{\bX}\M_{\ranksym}}(\G)
 \end{eqnarray}
@@
 where
-$P_{T_{\bX}\M_{r}}(\bZ): \bZ \mapsto P_{U}\bZ P_{V} + P_{U}^{\perp} \bZ P_{V} + P_{U} \bZ P_{V}^{\perp}$
+$P_{T_{\bX}\M_{\ranksym}}(\bZ): \bZ \mapsto P_{U}\bZ P_{V} + P_{U}^{\perp} \bZ P_{V} + P_{U} \bZ P_{V}^{\perp}$
 denotes the orthogonal projection of any
 $\bZ \in \R^{n \times m\calC}$ onto the tangent space at $\bX = \U\diag(\bsigma)\V^{\trsp}$.
-Here $P_U = \U \U^{\trsp}$ and $P_U^{\perp} = \I - \U \U^{\trsp}$ for any $\U \in \textrm{St}_{r}^{n}$.
+Here $P_U = \U \U^{\trsp}$ and $P_U^{\perp} = \I - \U \U^{\trsp}$ for any $\U \in \textrm{St}_{\ranksym}^{n}$.
 
 \begin{lemma}
-  Assuming that $\U_{p}$, $\V_{p}$ and $\bM$ are computed by Algorithm~\ref{alg:compute_riemannian_grad},
-  we have {\small${\textnormal{grad}} f(\bX) = \U \bM \V + \U_{p} \V^{\trsp} + \U \V^{\trsp}_{p}$}.
+  Assuming that $\U_{\symp}$, $\V_{\symp}$ and $\bM$ are computed by Algorithm~\ref{alg:compute_riemannian_grad},
+  we can obtain {${\textnormal{grad}} f(\bX) = \U \bM \V + \U_{\symp} \V^{\trsp} + \U \V^{\trsp}_{\symp}$}.
 \end{lemma}
 
-{\small
 \begin{proof}
+  The proof can be found in Appendix C.
+  \mycomment{
 \begin{align}
@@
        & \grad f(\bX) \\
-       & = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp}  \nonumber \\
+       & = \U \bM \V^{\trsp} + \U_{\symp} \V^{\trsp} + \U \V_{\symp}^{\trsp}  \nonumber \\
        & = \U(\U^{\trsp} \G \V) \V^{\trsp} + (\bR_{v} - \U \bM) \V^{\trsp} + \U (\bR_{u} - \V \bM^{\trsp})^{\trsp} \nonumber \\
@@
 \end{align}
+}
 \end{proof}
-}
 
@@
     \STATE 2. $\bM \leftarrow \U^{\trsp} \bR_{v}$.
-    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
-    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.    
+    \STATE 3. $\U_{\symp} \leftarrow \bR_{v} - \U \bM$, $\V_{\symp} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
+    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{\symp} \V^{\trsp} + \U \V_{\symp}^{\trsp} \in T_{\bX}\M_{\ranksym}$.
   \end{algorithmic}
@@
 
-Based on the above discussion, the solution of $\bX$ can be solved by Algorithm~\ref{alg:LRGeomCG} as following:
-
 \begin{algorithm}
   \begin{algorithmic}
-    \REQUIRE Initial $\bX_{1} \in \M_{r}$, tangent vector $\bfeta_{0} = \0$, $k = 1$.
+    \REQUIRE Initial $\bX_{1} \in \M_{\ranksym}$, tangent vector $\bfeta_{0} = \0$, $k = 1$.
 
@@
       \STATE 2. Compute a conjugate direction with PR+:
-             $\bfeta_k = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.
+             $\bfeta_k = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{\ranksym}$.
 
@@
 
-    \ENSURE $\bX \in \M_{r}$.
+    \ENSURE $\bX \in \M_{\ranksym}$.
 
@@
 
+Based on the above discussion, the solution of $\bX$ can be solved by Algorithm~\ref{alg:LRGeomCG}.
 Particularly, in Step 2 of Algorithm~\ref{alg:LRGeomCG}, $\beta_{k}$ is determined by a Polak-Ribi$\grave{e}$re (PR+) rule~\cite{vandereycken2013lowrank}:
-{\small
+{
 \begin{eqnarray}\label{eq:beta}
@@
 \noindent
-The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{r}}$, is chosen such that
-{\small
+The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{\ranksym}}$, is chosen such that
+{
 \begin{align}\label{eq:choose_step_size}
@@
 }
-{\small
+\mycomment{
+{
 \begin{align}\label{eq+choose_step_size2}
@@
 }
+}
 \noindent
@@
 The notation $\mT_{\bX_{k-1} \rightarrow \bX_{k}} (\bfeta_{k-1})$ in Step 2 and $R_{\bX_{k}} (t_k \bfeta_{k})$ denote \emph{vector transport} and \emph{retraction}, respectively.
-For more details of above two operators and the geometry of $\M_{r}$, see~\cite{vandereycken2013lowrank} and the references therein.
+For more details of above two operators and the geometry of $\M_{\ranksym}$, see~\cite{vandereycken2013lowrank} and the references therein.
 
-\subsection{Optimization of The Subproblem of $\bE$}
+\subsection{Subproblem Optimization w.r.t. $\bE$}
 
-Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
-{\small
+Similarly, to update $\bE$, we have the following problem \wrt. $\bE$:
+{
 \begin{align}
-\label{eq:subproblem_wrt_E_1}
-  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+\label{eq:subproblem_wrt_E_2}
+  \min_{\bE} & || \bE ||_{1,2} + || \calP_{\Omega} (\bN - \bE) ||_F^2 ,
 \end{align}
@@
 where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
-We thus obtain the subproblem \wrt. $\bE$ as below:
-{\small
-\begin{align}
-\label{eq:subproblem_wrt_E_2}
-  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
-\end{align}
-}
-\noindent
 The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
-{\small
+{
 \begin{align}\label{eq:column_wise_soft_thresholding}
@@
     \begin{aligned}
-      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
-      & \bN_{i} - \frac{\alpha \bN_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
+      & \zerocolumn,~\text{if}~ ||\calP_{\Omega} (\bN_{i})||_2 \leq \alpha   \\
+      & \calP_{\Omega} (\bN_{i}) - \frac{\alpha \calP_{\Omega} (\bN_{i})}{|| \calP_{\Omega} (\bN_{i}) ||_2},~\text{otherwise,}
     \end{aligned}
@@
 As we recover the low-rank matrix $\bX$ from the label assignment matrix $\bL$,
-it needs a post process to generate the prediction label for each testing data.
-Intuitively, there might be several possible ways to select as below:
+there requires a post process to generate the prediction label for each testing data from $\bX$.
+Intuitively, there might be several possible methods to select as below:
+
 \begin{itemize}
@@
 \begin{itemize}
-\item Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
+\item Average Score Fusion(ASF). we directly average the confidence scores predicted by multiple classifiers. 
+Then the $L_2$ norm is applied on each classifier's results for normalization.
 \item Multiple Kernel Learning (MKL).
-MKL learns a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$.
+MKL learns a weight coefficient $w$ for each classifier, and the final scores are obtained from function $f(s)=w^{T}s,~\sum w = 1$.
 We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
@@
 
-\yanred{
 \textbf{Reproducibility.}
-Our implementation is modified from the open-sourced LRGeomCG
-\cite{vandereycken2013lowrank}\footnote{http://www.unige.ch/math/vandereycken/matrix\_completion.html}.
-We will release the source code soon.
-}
+Our implementation is based on the open-sourced LRGeomCG code by Vandereycken
+\cite{vandereycken2013lowrank}.
+We will release the source code soon on Github.
 
@@
 
-As we can observe, our proposed algorithm significantly detect the outliers,
-and furthermore, the outlier elements are accurately converted into the right predictions while preserving consistency among all classifiers.
-
-\subsection{Feature Extraction}
-%We describe the details of the feature extraction for each dataset we use.
-%All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
-We used the best-performing CNN models for feature extraction including ResNet~\cite{he2015deep}, GoogleNet~\cite{szegedy2015going}, or etc.
-These features are fairly state of the art.
-They have been widely used in various recent research papers and have been verified the most effective features by recent internationally recognized competitions such as the ImageNet competition~\cite{russakovsky2015imagenet}.
-
-In UCF101 dataset, five different features are extracted from the following:
-%\begin{itemize}
-%  \item `fc6' of C3D~\cite{tran2015learning}
-%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-%  \item `pool5' of ResNet-152~\cite{he2015deep}
-%  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
-%\end{itemize}
-`fc6' of C3D~\cite{tran2015learning},
-`pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going},
-`pool5' of ResNet-152~\cite{he2015deep},
-and two `fc6's of Two-Stream~\cite{simonyan2014two}.
-Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
-All models we used are public available on Internet. %% provided by authors.
-
-In Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,110,164 models~\cite{he2016identity}.
-One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt
-\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}
-.
-Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers), trained the same in~\cite{he2015deep}
-Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell
-\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}}
-before extracting features.
-In Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of pre-activation ResNet-20,32,44,56,110,164 models, following the same training process as in~\cite{he2015deep,he2016identity}.
-
-In all other experiments, eight different features are extracted from the following:
-%\begin{itemize}
-%  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
-%  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
-%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-%  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
-%\end{itemize}
-``fc6'' of VGG16, VGG19~\cite{chatfield2014return},
-``fc6'' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet},
-``pool5/7x7\_s1'' from GoogleNet~\cite{szegedy2015going},
-and ``pool5'' of ResNet-50,101,152~\cite{he2015deep}.
-We use the official pre-trained model provided by Caffe Model Zoo
-\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}
-.
-For above eight models, we simply extract features with no extra operation.
+As we can observe, our proposed algorithm significantly detect the outliers.
+Furthermore, the outlier elements are accurately converted into the correct predictions, and only few results are wrong.
+This preserves the consistency among all classifiers.
 
@@
 
+\subsection{Feature Extraction}
+%We describe the details of the feature extraction for each dataset we use.
+%All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
+We used the best-performing CNN models for feature extraction including ResNet~\cite{he2015deep}, GoogleNet~\cite{szegedy2015going}, or etc.
+These features are fairly state of the art.
+They have been widely used in various recent research papers and have been verified the most effective features by recent internationally recognized competitions such as the ImageNet competition~\cite{russakovsky2015imagenet}.
+
+On UCF101 dataset, five different features are extracted from the following:
+%\begin{itemize}
+%  \item `fc6' of C3D~\cite{tran2015learning}
+%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+%  \item `pool5' of ResNet-152~\cite{he2015deep}
+%  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
+%\end{itemize}
+`fc6' of C3D~\cite{tran2015learning},
+`pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going},
+`pool5' of ResNet-152~\cite{he2015deep},
+and two `fc6's of Two-Stream~\cite{simonyan2014two}.
+Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
+All models we used are public available on Internet. %% provided by authors.
+
+On Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,110,164 models~\cite{he2016identity}.
+One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt
+\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}
+.
+Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers), trained the same in~\cite{he2015deep}
+Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell
+\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}}
+before extracting features.
+In Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of pre-activation ResNet-20,32,44,56,110,164 models, following the same training process as in~\cite{he2015deep,he2016identity}.
+
+In all other experiments, eight different features are extracted from the following:
+%\begin{itemize}
+%  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
+%  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
+%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
+%  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
+%\end{itemize}
+``fc6'' of VGG16, VGG19~\cite{chatfield2014return},
+``fc6'' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet},
+``pool5/7x7\_s1'' from GoogleNet~\cite{szegedy2015going},
+and ``pool5'' of ResNet-50,101,152~\cite{he2015deep}.
+We use the official pre-trained models provided by Caffe Model Zoo
+\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}
+.
+For the above eight models, we simply extract features without any extra operations.
+
 \subsection{Real-world Experiments}
@@
 As we have 50000 training data and 10000 testing data,
-FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
-LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
+The FWOT algorithm has one step to deal with $n\times n$ matrices, which are excessive to train~(more than one day).
+The LPBoost algorithm requires to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
 \footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
@@
 %% VOC07
-PASCAL VOC 2007 is a dataset for object detection and image classification.
+PASCAL VOC 2007 is a dataset for general object detection and image classification.
 In our experiments, we only use the image level annotation information.
-Since each image may contain more than one label, we filter the multi-label images to obtain 6146 clean data.
-There is similar procedure of sampling, classification and fusion as in Oxford-IIIT-Pet.
+Since each image may contain more than one label, we filter the multi-label images, resulting in a clean dataset with 6146 images.
+The procedures of sampling, classification and fusion are similar as Oxford-IIIT-Pet.
 
@@
 Additionally, our algorithm is more efficient than other late fusion methods in most situations.
-As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
+As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale datasets.
 \yanred{
 However, the time consumption of ours is acceptable in all experiments and quite fast on CIFAR-10/VOC2007.
-In conclusion, our method can solve the large scale problem efficiently.
+In conclusion, our method can handle the large scale problem efficiently and yield stable performance.
 }
@@
 Wikipedia dataset contains paragraphs of text for each picture, and total 2866 image-text pairs are categorized into 10 class.
-Only the image label annotation is used in our experiments.
+Only the image-level annotation is used in our experiments.
 PASCAL VOC 2007 contains 9963 images annotated with object-level information, which means each picture may have zero or more than one class.
 We choose 6146 images classified into 20 classes by filtering out the no-single class data.
-Oxford Flowers 17 has 17 flower categories with 80 images for each class.
+Oxford Flowers 17 has seventeen flower categories with 80 images for each category.
 Pascal Sentence contains 1000 images annotated by caption information and categorized into twenty classes.
@@
 \end{tabular}
-\caption{Mean accuracy using different strategies on three datasets.}
+\caption{Mean accuracy using different post process strategies on three datasets.}
 \label{table:strategy}
@@
 
-\subsection{Comparison with State-of-the-art}
+\subsection{Comparison with State-of-the-art Models}
 
-In this sub-section, we compare the performance of our algorithm with the state-of-the-art techniques.
+In this sub-section, we compare the performance of our algorithm with the state-of-the-art single models.
 %we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
-We use SVM classifiers based on different features in previous experiments to make a fair comparison with some MKL based methods.
-Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
-in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
-Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table~\ref{table:state_of_the_art}.
+In the previous experiments, we use SVM classifiers based on different features to make a fair comparison with some MKL based methods.
+The performance of SVM classifiers are usually not as good as the results directly predicted by CNN models.
+In order to obtain a higher result, we directly use multiple state-of-the-art CNN predictions and fuse them by our method.
+We demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table~\ref{table:state_of_the_art}.
 
@@
 \cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}.
-\yanred{
-As we can observe, our fusion is capable of further improving the performance of single model by a large margin.
-A single model has limited performance even with deeper depth or wider channel.
-However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
-To be noticed, our method fuses multiple single models which all perform worse than ResNeXt~\cite{xie2016aggregated},
-but can achieve low test error.
-This demonstrates the benefit of a good late fusion method.
-}
+As can be observed, our fusion algorithm is capable of further improving the performance of single models significantly,
+even a single model has satisfactory performance with deeper depth or wider channel.
+%However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
+We emphasize that ResNeXt~\cite{xie2016aggregated} is the best performer in single models, and our method only fuses models which perform worse than ResNeXt,
+but can achieve lower test error than ResNeXt.
+This demonstrates the aim and benefit of our late fusion method.
 
@@
 
-To relieve the performance degeneration in late label fusion from multiple sources, we formulate this problem as matrix factorization which recovers the underlying low-rank matrix and preserves the consistency among different sources.
-%To deal with the dispute on combining multi-view predictions, we formulate the late fusion problem as a matrix recover problem.
-%Our proposed algorithm is based on matrix factorization, which is unclear to consider smooth loss function from earlier research.
-Existing matrix factorization algorithms usually consider smooth loss, while it is unclear how to extend them to handle non-smooth robust loss, \eg $\ell_{1,2}$ loss.
-We propose an ALM based algorithm to solve matrix factorization problems with non-smooth loss.
+Late fusion is proposed to improve prediction performance by taking advantages of multiple features together.
+%In practice, the ubiquitousness of controversy of different features may degenerate the performance.
+In practice, the controversy of different features is ubiquitous and may degenerate the performance.
+To deal with this issue, we formulate this task as a robust matrix recovery problem with a hard constraint on the matrix rank to preserve the consistency among various features.
+Matrix factorization is often considered to handle the hard rank constraint, but only focuses on smooth loss, while it is unclear how to extend them to handle non-smooth robust loss, \eg, $\ell_{1,2}$ loss.
+We thus propose an ALM-based algorithm to cope with the non-smooth loss.
 %Specifically, our proposed algorithm first rejects outliers on a label indicator matrix by $\ell_{1,2}$ loss,

### 2017-06-04 Algorithm/Joint_Bayesian/JB_Test.m
add more scripts

@@ -1,0 +1,127 @@
+load('lbp_WDRef.mat')
+load('id_WDRef.mat')
+labels = id_WDRef;
+X = double(lbp_WDRef);
+X = sqrt(X);
+X = bsxfun(@rdivide,X,sum(X,2));
+train_mean = mean(X, 1);
+%[COEFF,SCORE] = princomp(X,'econ');
+[COEFF, SCORE] = pca(X,'Algorithm','svd','Economy', true);
+fprintf('PCA done');
+
+top_dims = 64;
+
+train_x = SCORE(:,1:top_dims);
+
+
+[mappedX, mapping] = JointBayesian(train_x, labels);
+fprintf('JointBayesian Done\n');
+% Dis_matrix = repmat(mapping.c,1,size(train_x,1))+repmat(mapping.c,1,size(train_x,1))+train_x * mapping.G *train_x';
+[classes, bar, labels] = unique(labels);
+    nc = length(classes);
+train_Intra = zeros(nc*2,2);
+for i=1:nc
+    train_Intra(2*i-1,:) = randperm(sum(labels == i),2) + find(labels == i,1,'first') - 1;
+    train_Intra(2*i,:) = randperm(sum(labels == i),2) + find(labels == i,1,'first') - 1;
+end;
+train_Extra = reshape(randperm(length(labels),20000),10000,2);
+train_Extra(labels(train_Extra(:,1))==labels(train_Extra(:,2)),:)=[];
+train_Extra(size(train_Intra,1)+1:end,:)=[];
+Dis_train_Intra = zeros(size(train_Intra,1),1);
+Dis_train_Extra = zeros(size(train_Intra,1),1);
+
+for i=1:size(train_Intra,1)
+    Dis_train_Intra(i) = train_x(train_Intra(i,1),:) * mapping.A * train_x(train_Intra(i,1),:)' + train_x(train_Intra(i,2),:) * mapping.A * train_x(train_Intra(i,2),:)' - 2 * train_x(train_Intra(i,1),:) * mapping.G * train_x(train_Intra(i,2),:)';
+    Dis_train_Extra(i) = train_x(train_Extra(i,1),:) * mapping.A * train_x(train_Extra(i,1),:)' + train_x(train_Extra(i,2),:) * mapping.A * train_x(train_Extra(i,2),:)' - 2 * train_x(train_Extra(i,1),:) * mapping.G * train_x(train_Extra(i,2),:)';
+end;
[…]

### 2017-06-04 Algorithm/startup.m

@@ -2,11 +2,13 @@ addpath ('Code');
 addpath ('Auxiliary');
 addpath ('SVM');
 addpath ('Data');
-addpath ('XuanyiFunction');
-addpath ('XuanyiFunction/util');
-addpath ('XuanyiFunction/experiments');
-addpath ('SVM/liblinear/matlab');
-%addpath ('SVM/libsvm/matlab');
+%addpath ('XuanyiFunction');
+%addpath ('XuanyiFunction/util');
+%addpath ('XuanyiFunction/experiments');
+%addpath ('SVM/liblinear/matlab');
+addpath ('SVM/libsvm/matlab');
+%addpath ('Joint_Bayesian_Data');
+%addpath ('Joint_Bayesian');
 addpath ('caffe/matlab');
 %addpath ('MKL/liblinear-mkl/src/matlab');
 %addpath(genpath('MKL/'));

### 2017-06-04 Algorithm/Joint_Bayesian/JB_Test.m
add more

@@ -1,32 +1,28 @@
-load('lbp_WDRef.mat')
-load('id_WDRef.mat')
-labels = id_WDRef;
-X = double(lbp_WDRef);
-X = sqrt(X);
-X = bsxfun(@rdivide,X,sum(X,2));
-train_mean = mean(X, 1);
+load ('Test_ALL.mat');
+train_labels = [train_label + 1; train_label + 1];             clear train_label;
+X            = double([train_features{1}; train_features{2}]); clear train_features;
+X            = sqrt(X);
+train_x      = bsxfun(@rdivide,X,sum(X,2));
+train_mean   = mean(train_x, 1);
 %[COEFF,SCORE] = princomp(X,'econ');
-[COEFF, SCORE] = pca(X,'Algorithm','svd','Economy', true);
-fprintf('PCA done');
+%[COEFF, SCORE] = pca(X,'Algorithm','svd','Economy', true);
+%fprintf('PCA done');
 
-top_dims = 64;
-
-train_x = SCORE(:,1:top_dims);
-
-
-[mappedX, mapping] = JointBayesian(train_x, labels);
+[mappedX, mapping] = JointBayesian(train_x, train_labels);
 fprintf('JointBayesian Done\n');
+
 % Dis_matrix = repmat(mapping.c,1,size(train_x,1))+repmat(mapping.c,1,size(train_x,1))+train_x * mapping.G *train_x';
-[classes, bar, labels] = unique(labels);
-    nc = length(classes);
-train_Intra = zeros(nc*2,2);
+[classes, bar, labels] = unique(train_labels);
+nc                     = length(classes);
+train_Intra            = zeros(nc*2, 2);
+
 for i=1:nc
-    train_Intra(2*i-1,:) = randperm(sum(labels == i),2) + find(labels == i,1,'first') - 1;
-    train_Intra(2*i,:) = randperm(sum(labels == i),2) + find(labels == i,1,'first') - 1;
+    train_Intra(2*i-1,:) = randperm(sum(train_labels == i),2) + find(train_labels == i,1,'first') - 1;
+    train_Intra(2*i,:)   = randperm(sum(train_labels == i),2) + find(train_labels == i,1,'first') - 1;
 end;
-train_Extra = reshape(randperm(length(labels),20000),10000,2);
[…]

### 2017-06-04 Algorithm/Joint_Bayesian/JointBayesian.m

@@ -24,20 +24,23 @@ function [mappedX, mapping] = JointBayesian(X, labels)
 %     [COEFF,SCORE] = princomp(X,'econ');
 %     X = SCORE(:,1:400);
 %     X = bsxfun(@minus,X,mapping.mean);
-    m = length(labels);
-    n = size(X,2);
+  max_buffer_number = 20000;
+  max_iteration = 500;
+
+  m = length(labels);
+  n = size(X,2);
 	
 	% Make sure labels are nice
 	[classes, bar, labels] = unique(labels);
-    nc = length(classes);
+  nc = length(classes);
 	
 	% Intialize Sw
 	Sw = zeros(size(X, 2), size(X, 2));
     
-   cur = {};
-    withinCount = 0;
-    numberBuff = zeros(1000,1);
-%     numberInvert = zeros(1000,1);
+  cur = {};
+  withinCount = 0;
+  numberBuff = zeros(max_buffer_number, 1);
+% numberInvert = zeros(1000,1);
     maxNumberInOneClass = [];
     for i=1:nc
         % Get all instances with class i
@@ -86,15 +89,15 @@ function [mappedX, mapping] = JointBayesian(X, labels)
     
     oldSw = Sw;
 %     Gs = cell(maxNumberInOneClass,1);
-    SuFG = cell(1000,1);
-    SwG = cell(1000,1);
+    SuFG = cell(20000,1);
+    SwG = cell(20000,1);
     
-    for l=1:500
+    for l=1:max_iteration
 %         tic;
         F = inv(Sw);
         ep =zeros(n,m);
         nowp = 1;
-        for g = 1:1000
+        for g = 1:max_buffer_number
             if numberBuff(g)==1
                 G = -1 .* (g .* Su + Sw) \ Su / Sw;
                 SuFG{g} = Su * (F + g.*G);
@@ -114,7 +117,7 @@ function [mappedX, mapping] = JointBayesian(X, labels)
 %     Sw = ep*ep'/withinCount;
         fprintf('%d %f\n',l,norm(Sw - oldSw)/norm(Sw));
 %         toc;
-        if norm(Sw - oldSw)/norm(Sw)<1e-6
+        if norm(Sw - oldSw)/norm(Sw)<1e-5
             break;
         end;
         oldSw = Sw;

### 2017-06-04 Algorithm/startup.m

@@ -7,8 +7,8 @@ addpath ('Data');
 %addpath ('XuanyiFunction/experiments');
 %addpath ('SVM/liblinear/matlab');
 addpath ('SVM/libsvm/matlab');
-%addpath ('Joint_Bayesian_Data');
-%addpath ('Joint_Bayesian');
+addpath ('Joint_Bayesian_Data');
+addpath ('Joint_Bayesian');
 addpath ('caffe/matlab');
 %addpath ('MKL/liblinear-mkl/src/matlab');
 %addpath(genpath('MKL/'));

### 2017-06-04 Rebuttal_ICCV.txt
final version of rebuttal

We thank all the reviewers for the comments and suggestions. We take the comments seriously and will carefully revise the paper.

To Reviewer 1:

Thanks for the comments.

- While you generally recognized our technical merit, your major concern is that we did not compare our method to more other fusion methods in which fusion is implicitly tackled at the training stage. Following your suggestion, we conducted more experiment and compared to the Bayesian-based method [1] suggested by you. Because [1] is not directly applicable to fusion, some necessary modification is made. A limitation of [1] is that it requires the same dimensionality of features for fusing, which is not true in many real world applications. The global_pooling layer always generates 64-dimension features. We thus choose the global_pooling layer's feature of all residual-based network used in Table 4 as the input of the joint Bayesian method [1]. In this way, we have feature dimension = 64, 50000 instances (10 models) for total 10 classes. The accuracy of Joint Bayesian [1] is 93.8. Using the SVM predictions with the global pooling feature as input, the accuracy of our method is 95.0, which outperforms the method suggested by you. Additionally, because our method does not require the input feature to be of the same dimension, our method can be applied to a broader range of applications.

- Other two minor issues:
(i)In terms of efficiency, our method and RCEC are the two most efficient methods (See Table 2). The two algorithms have a similar range of running time. On the other hand, our method outperforms RCEC in accuracy for all the five datasets (See Table 2).

(ii) Our method and ResNeXt are two different directions for image classification. Our method can further take ResNeXt as additional input. We conducted the experiments by taking ResNeXt as another input, and our method outperforms ResNeXt by about 3%, which is significant and worthwhile.

[1] Bayesian face revisited: A joint formulation. In ECCV, 2012
We will cite [1] and discuss more implicit fusion methods in our revised version.

To  Reviewer 2:

Thanks for your comments that the paper proposes a new way for information fusion. We also appreciate your suggestions for improving the paper.

Your major concern is that we should add three more experiments. 
To address the concerns, we conducted all the suggested experiments and report the result on CIFAR-10 in this rebuttal due to space limit.

1. SVM-prediction V.S. CNN-prediction as the input of late fusion.
We used SVM prediction as input in our original submission because some of the compared algorithms cannot take CNN predictions as input (see L801 to L803 for our justifications). Nevertheless, we additionally used CNN-predictions learned by end-to-end CNN models as the input of late fusion to address your comments. The accuracy of our method by fusing the CNN-predictions of each model used in Table 1 is 95.93, higher than the fusion of SVM-predictions (95.11). The only two compared methods that are able to use CNN prediction as input are RCEC and average fusion. The accuracies of RCEC and average fusion using CNN prediction are 95.36 and 94.97. Again, our method outperforms the compared methods.

2. Neural network based fusion V.S. Our method

Note that directly training a fusion model that fuses several entire CNN models including all convolutional layers may be intractable due to excessive GPU memory consumption. We thus perform the following two alternative experiments to address your comment.

---(1) Feature fusion via CNN
We conducted an experiment in which fusion is performed at the last pooling layer of all CNN models. Two strategies were used in our experiment. In the first setting, the features are flattened and concatenated (we denote this strategy by 'concatenation'). In the second setting,  we additionally apply max pooling crossing channel (denoted by 'max pooling'), followed by a fc layer with 10 num_outputs and a softmax layer.  
The results (in accuracy) are as follows:
| concatenation | max pooling | ours |
| --- 95.21 --- | -- 94.93 -- | 95.93|

---(2) Late fusion via CNN
We additionally conducted the experiment in which the fusion of different CNNs is performed at the fully connected layer. Below are the experiment results.
| CNN weighting | average | ours |
| --- 95.26 --- |- 95.12 -| 95.93|

As demonstrated by this comparison, our method still achieves the best performance across all baselines.

3. The impact of the number of instances:
You have also asked the impact of the number of instances. We additionally perform an experiment by setting the different number of instances (number of rows in matrix L). In this experiment, SVM-predictions are used as fusion input. The experiment results (in accuracy) are listed below:
| 1000  |  2000  | 4000  |  6000   |  8000  | 10000 |
| 94.94 |  95.10 | 95.12  |  95.10   |  95.11  | 95.11   |

We can observe that our method achieves stable performance when the number is greater than 2000. We will include all new experimental results into the revised paper.

For Reviewer 3:

Thanks for your kind advice. The caption will be revised.
The C represents the number of classes. There are usually not many classes in most real-world applications. In this situation, the complexity is acceptable.
If C is quite large for some specific problems (e.g. YouTube-8M includes 4716 classes). A trade-off method may be splitting all classes into multiple parts, performing late fusion on each part and finally merging together. The above discussions will be included in our revision.

### 2017-07-21 Rebuttal_ICCV.txt
small changes
iccv die....

@@
 
-Thanks for the comments.
-
-- While you generally recognized our technical merit, your major concern is that we did not compare our method to more other fusion methods in which fusion is implicitly tackled at the training stage.
-Following your suggestion, we conducted more experiment and compared to the Bayesian-based method [1] suggested by you.
-Because [1] is not directly applicable to fusion, some necessary modification is made.
-A limitation of [1] is that it requires the same dimensionality of features for fusing, which is not true in many real world applications.
-The global_pooling layer always generates 64-dimension features.
-We thus choose the global_pooling layer's feature of all residual-based network used in Table 4 as the input of the joint Bayesian method [1].
-In this way, we have feature dimension = 64, 50000 instances (10 models) for total 10 classes.
-The accuracy of Joint Bayesian [1] is 93.8.
-Using the SVM predictions with the global pooling feature as input, the accuracy of our method is 95.0, which outperforms the method suggested by you.
-Additionally, because our method does not require the input feature to be of the same dimension, our method can be applied to a broader range of applications.
+Q: Comparisons with more fusion methods.
+A: As suggested, we compared with the Bayesian-based method [1] suggested by you.
+Note that [1] requires the same dimensionality of features for fusing, which, however, is not directly applicable in many real world applications.
+Based on ResNet, recall that the global-pooling layer generates 64-dimension features.
+We thus choose the global-pooling layer's feature of all residual-based networks used in Table 4 as the input of the joint Bayesian method [1].
+In this way, we have 50000 instances with feature dimension = 64 for total 10 classes.
+The accuracy of Joint Bayesian [1] is 93.8; While the accuracy of our method is 95.0, which outperforms Joint Bayesian.
+More importantly, because our method does not require the input feature to be of the same dimension, our method can be applied to a broader range of applications.
 
 - Other two minor issues:
-(i)In terms of efficiency, our method and RCEC are the two most efficient methods (See Table 2).
-The two algorithms have a similar range of running time.
-On the other hand, our method outperforms RCEC in accuracy for all the five datasets (See Table 2).
+(i) In terms of efficiency, our method and RCEC are the two most efficient methods (See Table 2).
+The two algorithms have the similar range of running time.
+Nevertheless, our method outperforms RCEC in terms of accuracy for all the five datasets (See Table 1).
 
-(ii) Our method and ResNeXt are two different directions for image classification.
-Our method can further take ResNeXt as additional input.
-We conducted the experiments by taking ResNeXt as another input, and our method outperforms ResNeXt by about 3%, which is significant and worthwhile.
+(ii) Our method and ResNeXt are two different kinds of methods for image classification.
+With the proposed fusion scheme, our method takes ResNeXt as additional input, and it outperforms ResNeXt by about 3%.
+Thus, the proposed method is significant and worthwhile.
+
+We will cite [1] and discuss more methods in our revised version.
 
 [1] Bayesian face revisited: A joint formulation. In ECCV, 2012
-We will cite [1] and discuss more implicit fusion methods in our revised version.
 
@@
 Your major concern is that we should add three more experiments. 
-To address the concerns, we conducted all the suggested experiments and report the result on CIFAR-10 in this rebuttal due to space limit.
+To address the concerns, we conducted all the suggested experiments and report the results on CIFAR-10 in this rebuttal due to space limit.
 
-1. SVM-prediction V.S. CNN-prediction as the input of late fusion.
-We used SVM prediction as input in our original submission because some of the compared algorithms cannot take CNN predictions as input (see L801 to L803 for our justifications).
-Nevertheless, we additionally used CNN-predictions learned by end-to-end CNN models as the input of late fusion to address your comments.
-The accuracy of our method by fusing the CNN-predictions of each model used in Table 1 is 95.93, higher than the fusion of SVM-predictions (95.11).
-The only two compared methods that are able to use CNN prediction as input are RCEC and average fusion.
-The accuracies of RCEC and average fusion using CNN prediction are 95.36 and 94.97.
+Q1. SVM-prediction V.S. CNN-prediction as the input of late fusion.
+
+A.
+We used the SVM prediction as input in our original submission because some compared algorithms cannot take CNN predictions as input (see L801 to L803 for our justifications).
+Nevertheless, we additionally used CNN-predictions learned by end-to-end CNN models as the input of late fusion.
+By fusing the CNN-predictions, our method achieves an accuracy of 95.93, which is much better than the fusion of SVM-predictions (95.11).
+RCEC and average fusion are two other methods that can use CNN predictions as input, and their accuracies are 95.36 and 94.97, respectively.
 Again, our method outperforms the compared methods.
 
-2. Neural network based fusion V.S. Our method
+Q2. Neural network based fusion V.S. Our method.
 
-Note that directly training a fusion model that fuses several entire CNN models including all convolutional layers may be intractable due to excessive GPU memory consumption.
-We thus perform the following two alternative experiments to address your comment.
+A.
+Directly training a fusion model that fuses several CNN models may be intractable due to excessive GPU memory consumption.
+We thus perform the following two alternative experiments to respond your comment.
 
 ---(1) Feature fusion via CNN
-We conducted an experiment in which fusion is performed at the last pooling layer of all CNN models.
+We conducted an experiment in which we performed the fusion at the last pooling layer of all CNN models.
 Two strategies were used in our experiment.
-In the first setting, the features are flattened and concatenated (we denote this strategy by 'concatenation').
-In the second setting,  we additionally apply max pooling crossing channel (denoted by 'max pooling'), followed by a fc layer with 10 num_outputs and a softmax layer.
+In the first setting, the features are flattened and concatenated (denoted as 'concatenation').
+In the second setting, we apply max-pooling across channels (denoted by 'max pooling').
 The results (in accuracy) are as follows:
@@
 ---(2) Late fusion via CNN
-We additionally conducted the experiment in which the fusion of different CNNs is performed at the fully connected layer. Below are the experiment results.
+We conducted the experiment in which we perform the fusion of different CNNs is performed at the fully connected layer. Below are the experiment results.
 | CNN weighting | average | ours |
@@
 
-As demonstrated by this comparison, our method still achieves the best performance across all baselines.
+Based on the above comparisons, our method still achieves the best performance among all baselines.
 
-3. The impact of the number of instances:
-You have also asked the impact of the number of instances.
-We additionally perform an experiment by setting the different number of instances (number of rows in matrix L).
+Q3. The impact of the number of instances.
+
+A.
+We performed an experiment by setting the different number of instances (number of rows in matrix L).
 In this experiment, SVM-predictions are used as fusion input.
 The experiment results (in accuracy) are listed below:
-| 1000  |  2000  | 4000  |  6000   |  8000  | 10000 |
-| 94.94 |  95.10 | 95.12  |  95.10   |  95.11  | 95.11   |
+|#instances| 1000  | 2000 | 4000 | 6000 | 8000 | 10000 |
+| Accuracy | 94.94 |95.10 |95.12 |95.10 |95.11 | 95.11 |
 
-We can observe that our method achieves stable performance when the number is greater than 2000. We will include all new experimental results into the revised paper.
+From the above comparison, our method achieves stable performance when the number is greater than 2000.
+
+We will include the above experimental results into the revised paper.
 
@@
 
-Thanks for your kind advice. The caption will be revised.
-The C represents the number of classes. There are usually not many classes in most real-world applications. In this situation, the complexity is acceptable.
+Thanks for your kind advice. We will revise the caption.
+The C represents the number of classes.
+There are usually not many classes in most real-world applications.
+In this situation, the complexity is acceptable.
 If C is quite large for some specific problems (e.g.
 YouTube-8M includes 4716 classes).
-A trade-off method may be splitting all classes into multiple parts, performing late fusion on each part and finally merging together.
+A trade-off method may be splitting all classes into multiple parts, and then performing late fusion on each part and finally merging together.
 The above discussions will be included in our revision.

### 2017-07-21 egpaper_for_review.tex
final version of rebuttal
iccv die....

@@
 However, it is ubiquitous that different features dispute the prediction on the same data with each other, leading to performance degeneration.
-%Therefore, outlier detection is crucial when combining the predictions of different features.
-In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources,
-aiming to avoid the performance degeneration caused by the controversy of multiple features.
+In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources, aiming to avoid the performance degeneration caused by the controversy of multiple features.
 In this way, the consistency of results by various features can be preserved, which can relieve the performance degeneration.
-Extensive experiments demonstrate efficacy of the proposed method on outlier detection and performance improvement,
-which outperforms the previous state-of-the-art late fusion algorithms on most datasets.
-
+Extensive experiments demonstrate the efficacy of the proposed method for outlier detection and performance improvement, which outperforms the previous state-of-the-art late fusion algorithms on most datasets.
 \end{abstract}
@@
 \end{tabular}
-\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.
+\caption{Computational time on real-world data sets. Computational time is recorded in seconds.
 FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),

### 2017-07-28 aaai-2018/main.tex
add aaai-2018

--- 2017-07-21 egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\def\year{2018}\relax
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
+\usepackage{aaai18}  %Required
+\usepackage{times}  %Required
+\usepackage{helvet}  %Required
+\usepackage{courier}  %Required
+\usepackage{url}  %Required
+\usepackage{graphicx}  %Required
+\frenchspacing  %Required
+\setlength{\pdfpagewidth}{8.5in}  %Required
+\setlength{\pdfpageheight}{11in}  %Required
 
@@
 \usepackage{amsthm,mathrsfs,amsfonts,dsfont}
+\usepackage{amsmath}
 \usepackage{algorithm}
@@
 \newtheorem{remark}{Remark}
-
 \newcommand\mycomment[1]{}
@@
 \def\symp{r}
-
 \def\calP{\mathcal{P}}
@@
 
-\def\yanred{\textcolor{black}}
-\def\yanblue{\textcolor{blue}}
-\def\kuired{\textcolor{red}}
+\def\eg{\emph{e.g}.} \def\Eg{\emph{E.g}.}
+\def\ie{\emph{i.e}.} \def\Ie{\emph{I.e}.}
+\def\cf{\emph{c.f}.} \def\Cf{\emph{C.f}.}
+\def\etc{\emph{etc}.} \def\vs{\emph{vs}.}
+\def\wrt{w.r.t.} \def\dof{d.o.f.}
+\def\etal{\emph{et al}.}
 %%%%%
 
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{283} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
+%PDF Info Is Required:
+\pdfinfo{
+/Title (Late Fusion via Subspace Search with Consistency Preservation)
+/Author (AAAI Press Staff)
+}
+\setcounter{secnumdepth}{0}  
  \begin{document}
-
-%%%%%%%%% TITLE
+% The file aaai.sty is the style file for AAAI Press 
+% proceedings, working notes, and technical reports.
+%
 \title{Late Fusion via Subspace Search with Consistency Preservation}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+\author{AAAI Press\\
+Association for the Advancement of Artificial Intelligence\\
+2275 East Bayshore Road, Suite 160\\
+Palo Alto, California 94303\\
 }
-
 \maketitle
-%\thispagestyle{empty}
-
 \begin{abstract}
@@
 or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
-Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
+Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf) and word2vec.
 Each category of features tends to capture some specific characteristics of data,
@@
 Notations are introduced shortly.).
-\yanred{
 Specially, $\ell_{1,2}$ loss preserves the fidelity within each column by $\ell_{2}$ loss in the vertical direction and is robust to sparse errors across all the columns by $\ell_{1}$ loss in the horizontal direction.
@@
 $\ell_{1}$ loss is not sensitive to outliers, but not capable to detect the abnormal features which generate corrupted results.
-}
 In addition, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
@@
 
-The main contributions of this work are summarized as follows:
+The main contributions are summarized as follows:
 \begin{itemize}
@@
   \item We provide theoretical convergence analysis for the proposed robust matrix recovery algorithm.
-  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
+  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion andalgorithms and feature fusion methods.
 \end{itemize}
@@
 Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
-Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,Mishra2012,ngonips2012scaled}.
+Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,ngonips2012scaled}.
 For instance, in~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
@@
 In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
-In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
+%In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
 %The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
@@
 \cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
-\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
+\cite{Wang_Transformation,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
 The authors in~\cite{vanicassp2014late} point out that missing values in predictions can be a challenge for late fusion due to the absence of features.
@@
 On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
-$
-|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }  .
-$
+{\small
+\begin{align}
+|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
+\end{align}
+}\noindent
 Thus, a general formulation of recovering the underlying low-rank label matrix can be written as follows:
-{
+{\small
 \begin{align}\label{eq:l12_rankconstraint}
@@
 We hence transform the original problem as a matrix factorization formulation as follows:
-{
+{\small
 \begin{align}\label{eq:l12_mf}
@@
 \noindent
-Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
+Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
 In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).
@@
 By introducing a new variable $\calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)$, we can develop Problem~(\ref{eq:l12_mf}) as below:
-{
+{\small
 \begin{align}\label{eq:mf_l21_constrained}
@@
 The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
-{
+{\small
 \begin{align}\label{eq:lagrangian_l21}
@@
   By the optimality of $\bE_{t+1}$ in Step 2 in Algorithm~\ref{alg:alm_mf}, we have the sub-differential of $\calL$ w.r.t. $\bE$ as zeros:
-  {
+  {\small
   \begin{align}
@@
 \subsection{Subproblem Optimization w.r.t. $\bX$}
+\label{sec:sub_x}
 
 To update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
-{
+{\small
 \begin{align}\label{eq:langrangian_wrt_X}
@@
 Hence, we derive the following subproblem \wrt. $\bX$:
-{
+{\small
 \begin{align}\label{eq:subproblem_wrt_X}
@@
 A smooth manifold of fixed-rank-$\ranksym$ matrices is defined as~\cite{vandereycken2013lowrank}:
-{
+{\small
 \begin{align}
@@
 which is obtained as below:
-{
+{\small
 \begin{align}
@@
 projection of $\G$ onto the tangent space at $\bX$:
-{
+{\small
 \begin{eqnarray}\label{eq:grad}
@@
 Particularly, in Step 2 of Algorithm~\ref{alg:LRGeomCG}, $\beta_{k}$ is determined by a Polak-Ribi$\grave{e}$re (PR+) rule~\cite{vandereycken2013lowrank}:
-{
+{\small
 \begin{eqnarray}\label{eq:beta}
@@
 The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{\ranksym}}$, is chosen such that
-{
+{\small
 \begin{align}\label{eq:choose_step_size}
@@
 }
-\mycomment{
-{
-\begin{align}\label{eq+choose_step_size2}
-  | \langle \grad f(R_{\bX_{k}} (t_{k} \bfeta_{k})), & \mT_{\bX_{k-1} \rightarrow \bX_{k}} (\bfeta_{k}) \rangle |  \nonumber \\
-                           & \leq c_{2} | \langle \grad f(\bX_{k}), \bfeta_{k} \rangle |  ,
-\end{align}
-}
-}
+%\begin{align}\label{eq+choose_step_size2}
+%  | \langle \grad f(R_{\bX_{k}} (t_{k} \bfeta_{k})), & \mT_{\bX_{k-1} \rightarrow \bX_{k}} (\bfeta_{k}) \rangle |  \nonumber \\
+%                           & \leq c_{2} | \langle \grad f(\bX_{k}), \bfeta_{k} \rangle |  ,
+%\end{align}
 \noindent
@@
       Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
-      Finally, we choose the label with the most votes to be the prediction results.
+      The label with the most votes is the final prediction result.
   \item \textbf{[GATE].} $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
       As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
-      The similar process as the first strategy is applied to the above results, which predicts the final labels.
+      The similar process as the first strategy is applied to predict the final labels.
 \end{itemize}
@@
 
-Now we analyze the computation complexity of our proposed algorithm.
-The sub-algorithm in Section~3.3 solve the solution of $\bX$.
-The primary computation is described in Algorithms.~\ref{alg:compute_riemannian_grad} and~\ref{alg:LRGeomCG},
+%Now we analyze the computation complexity of our proposed algorithm.
+%The sub-algorithm in Section~\ref{sec:sub_x} solve the solution of $\bX$.
+For the optimization on $\bX$, the primary computation is described in Algorithms.~\ref{alg:compute_riemannian_grad} and~\ref{alg:LRGeomCG},
 which uses subspace search to optimize the solution.
@@
 the computation costs too much to be affordable due to the cubic complexity of $m$,
-but ours are able to solve the solution.
+but ours can still solve the solution.
 
 \section{Experimental Studies}
-
-In this section, we first visualize the results of our approach on the synthetic dataset.
-Then we evaluate the performance on eight publicly available real-world data sets,
-UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
-The strategy analysis for post process is detailed in the last subsection.
-
-Five state-of-the-art fusion methods are compared with our proposed algorithm :
-\begin{itemize}
-\item Average Score Fusion(ASF). we directly average the confidence scores predicted by multiple classifiers. 
-Then the $L_2$ norm is applied on each classifier's results for normalization.
-\item Multiple Kernel Learning (MKL).
-MKL learns a weight coefficient $w$ for each classifier, and the final scores are obtained from function $f(s)=w^{T}s,~\sum w = 1$.
-We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
-\item Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
-The core alogrithm in RCEC can be modified to recover $\bX$ from $L$ in Problem.~\ref{eq:l12_mf}, and the post process is same as our method.
-\item Feature Weighting via Optimal Thresholding (FWOT) \cite{xuiccv2013feature}.
-The authors propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
-\item LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
-\end{itemize}
-
-The parameter $\mu$ is selected from $\{0.1, 1, 5\}$,
-$\rho$ is select from $\{1.01, 1.05, 1.1\}$
-and $\epsilon$ is select from $\{1e-2, 1e-3, 1e-4\}$ in all our experiments.
-Among different parameters, there are small differences of the prediction performance.
-LIBLINEAR~\cite{fan2008liblinear} is adopted for our basic classification toolbox.
-The parameters are set as default in LIBLINEAR and liblinear-mkl, unless otherwise specified.
-For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from $\{0.01,1,2,4,6,...,20\}$ and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
-For FWOT, the smoothing parameter candidates are $\{0.5, 0.6, ...
-, 0.9\}$ and the parameter $C$ in is selected from $\{10^{-4},10^{-2},...,10^{4}\}$ according to cross-validation, which is same in~\cite{xuiccv2013feature}.
-For LPBoost, we use cross-validation to pick up the best $\nu$ from $\{0.5,0.6,0.7,0.8,0.9\}$ suggested in~\cite{xuiccv2013feature}.
-
-\textbf{Reproducibility.}
-Our implementation is based on the open-sourced LRGeomCG code by Vandereycken
-\cite{vandereycken2013lowrank}.
-We will release the source code soon on Github.
-
-\subsection{Synthetic Experiments}
-
-In synthetic experiments, we set $n = 280$, $m = 15$, $\calC = 20$ to generate $n$ instances, which are randomly labeled with $c_i, 1 \leq i \leq n, 1 \leq c_i \leq \calC$.
-And we regard these instances as the ground truth data represented by a matrix $Gt \in \dsR^{280 \times 1}$.
-Then we randomly permute $40\%$ instances' labels,
-repeating $m = 15$ times to get fifteen classifiers' results as $Er \in \dsR^{280 \times 15}$.
-Therefore, the classification error of each classifier is around 40\%.
-Then, we derive an indicator matrix from the predictions of 15 classifiers,
-and recovery this indicator matrix into the final results, $Rec \in \dsR^{280 \times 15}$, by our proposed algorithm.
-%Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed algorithm,
-%the visualization results are illustrated in Fig.~\ref{fig:ensemble_cluster}.
-We visualize the ground truth information, classifiers' predictions and the recovered results in Fig.~\ref{fig:ensemble_cluster}.
-
-\begin{figure}[htp]
-\center
-    \subfigure[Ground Truth]{
-    \label{subfig:gt_pdf}
-    \includegraphics[width=0.14\textwidth]{resource/ground_truth.eps}
-    }
-    \subfigure[Random Noise]{
-    \label{subfig:er_pdf}
-    \includegraphics[width=0.14\textwidth]{resource/random_error.eps}
-    }
-    \subfigure[Our Recovered Result]{
-    \label{subfig:re_pdf}
-    \includegraphics[width=0.14\textwidth]{resource/recover.eps}
-    }
-    \caption{Visualized results of the synthetic dataset.
-    We use different colors to represent different label for each instance.
-   Fig.~\ref{subfig:gt_pdf} show the visualized ground truth data,
-   and each row corresponds to one instance with the class label represented by color.
-   Fig.~\ref{subfig:er_pdf} has 15 columns, each represents one classifiers's predictions.
-   There are also 15 columns in Fig.~\ref{subfig:re_pdf}, which is generated by the recovered results from our algorithm.
-   %Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different labels.
-    %Each picture represents a $280$ instances's information with every $20$ colums corresponding to one classifier.
-    %We use different colors to represent different binary indicator predictions~(20 dimensions).
-    %For~\ref{subfig:gt_pdf}, there is the ground truth information of $280$ instances for $15$ classifiers.
-    %Obviously, the ground truth for different classifiers is the same.
-    %Each kind of color represents one class, and the ground truth picture is generated from 280 synthetic instance lables.
-    %Random noise picture~\ref{subfig:er_pdf} show 15 classifiers's prediction results while the classification accuracy for each one is about 60\%.
-    %The last picture is the recovered result generated by our algorithm.
-    Obviously, most of the outlier elements are correctly recovered by our algorithm with only a few error predictions left.
-    }
-    \label{fig:ensemble_cluster}
-\end{figure}
-
-As we can observe, our proposed algorithm significantly detect the outliers.
-Furthermore, the outlier elements are accurately converted into the correct predictions, and only few results are wrong.
-This preserves the consistency among all classifiers.
 
@@
 LPBoost       & 110.81          & 72.45           &  4750.9          & 43.67           &   \textbf{7.46} \\\hline
-Ours                & 421.23          & \textbf{5.384}  &  417.26          & 76.16           &   16.21         \\
+\bf{Ours}     & 421.23          & \textbf{5.384}  &  417.26          & 76.16           &   15.21         \\
 \hline
@@
 
-\subsection{Feature Extraction}
-%We describe the details of the feature extraction for each dataset we use.
-%All CNN features are extracted using Caffe~\cite{jia2014caffe}, a deep learning framework.
-We used the best-performing CNN models for feature extraction including ResNet~\cite{he2015deep}, GoogleNet~\cite{szegedy2015going}, or etc.
+\subsection{Synthetic Experiments}
+
+We set $n = 280$, $m = 15$, $\calC = 20$ to generate $n$ instances, which are randomly labeled with $c_i, 1 \leq i \leq n, 1 \leq c_i \leq \calC$.
+We regard these instances as the ground truth data represented by a matrix $Gt \in \dsR^{280 \times 1}$.
+Then we randomly permute $40\%$ instances' labels,
+repeating $m = 15$ times to get fifteen classifiers' results as $Er \in \dsR^{280 \times 15}$.
+Therefore, the classification error of each classifier is around 40\%.
+Then, we derive an indicator matrix from the predictions of 15 classifiers,
+and recovery this indicator matrix into the final results, $Rec \in \dsR^{280 \times 15}$, by our proposed algorithm.
+%Deriving an indicator matrix $\bL \in \dsR^{280 \times 300}$ from the synthetic classifiers' results as the input of our proposed algorithm,
+%the visualization results are illustrated in Fig.~\ref{fig:ensemble_cluster}.
+We visualize the ground truth information, classifiers' predictions and the recovered results in Fig.~\ref{fig:ensemble_cluster}.
+
+\begin{figure}[ht]
+\center
+\subfigure[Ground Truth]{
+\label{subfig:gt_pdf}
+\includegraphics[width=0.14\textwidth]{resource/ground_truth.eps}
+}
+\subfigure[Random Noise]{
+\label{subfig:er_pdf}
+\includegraphics[width=0.14\textwidth]{resource/random_error.eps}
+}
+\subfigure[\bf{Our Results}]{
+\label{subfig:re_pdf}
+\includegraphics[width=0.14\textwidth]{resource/recover.eps}
+}
+\caption{Visualized results of the synthetic dataset.
+Different colors represent different labels for each instance. 
+Fig.~\ref{subfig:gt_pdf} show the visualized ground truth data, and each row corresponds to one instance with the class label represented by color.
+Fig.~\ref{subfig:er_pdf} has 15 columns, each represents one classifiers's predictions.
+There are also 15 columns in Fig.~\ref{subfig:re_pdf}, which is generated by the recovered results from our algorithm.
+Obviously, most of the outlier elements are correctly recovered with only a few error predictions left.
+}
+\label{fig:ensemble_cluster}
+\end{figure}
+
+As we can observe, our proposed algorithm significantly detect the outliers.
+Furthermore, the outlier elements are accurately converted into the correct predictions, and only few results are wrong.
+This preserves the consistency among all classifiers.
+
+\subsection{Real-world Experiments}
+
+We evaluate the performance on eight publicly available real-world data sets,
+UCF101~\cite{UCF101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
+
+\subsubsection{Feature Extraction}
+
+We used the best-performing CNN models for feature extraction including GoogleNet~\cite{szegedy2015going}, ResNet~\cite{he2015deep}, ResNeXt~\cite{xie2016aggregated}, Pre-ResNet~\cite{he2016identity} and VGG~\cite{chatfield2014return} or etc.
 These features are fairly state of the art.
@@
 On UCF101 dataset, five different features are extracted from the following:
-%\begin{itemize}
-%  \item `fc6' of C3D~\cite{tran2015learning}
-%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-%  \item `pool5' of ResNet-152~\cite{he2015deep}
-%  \item two `fc6's of Two-Stream~\cite{simonyan2014two}
-%\end{itemize}
-`fc6' of C3D~\cite{tran2015learning},
-`pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going},
-`pool5' of ResNet-152~\cite{he2015deep},
-and two `fc6's of Two-Stream~\cite{simonyan2014two}.
-Given a video, we extract the above five features following the same process in~\cite{simonyan2014two,tran2015learning}(GoogleNet and ResNet-152 feature are same as spatial net in~\cite{simonyan2014two}).
-All models we used are public available on Internet. %% provided by authors.
+`fc6' of C3D~\cite{tran2015learning}, `pool5/7x7\_s1' from GoogleNet, `pool5' of ResNet-152, and two `fc6's of Two-Stream~\cite{simonyan2014two}.
+Given a video, we extract the above five features following the same process described in Two-Stream.
 
-On Cifar10 dataset, the features are extracted from the `global\_pool' layer of ResNet-20,32,44,56,110~\cite{he2015deep} and of pre-activation ResNet-20,32,44,56,110,164 models~\cite{he2016identity}.
-One feature is extracted from `pool3' layer's features of cifar10\_full model described in caffe example prototxt
-\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/cifar10_full.prototxt}}
-.
-Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers), trained the same in~\cite{he2015deep}
-Each ResNet model is trained following the standard procedure in~\cite{he2015deep,he2016identity}, and cifar10\_full model is trained by an official shell
-\footnote{\url{https://github.com/BVLC/caffe/blob/master/examples/cifar10/train_full.sh}}
-before extracting features.
-In Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of pre-activation ResNet-20,32,44,56,110,164 models, following the same training process as in~\cite{he2015deep,he2016identity}.
+On Cifar10 dataset, the features are extracted from the global pooling layer of ResNet-20,32,44,56,110 and of Pre-ResNet-20,32,44,56,110,164 models.
+One feature is extracted from the last pooling layer of cifar10\_full model described in caffe example prototxt.
+Two modified networks VGG16 and GoogleNet are used to extract final pooling features~(Modify the stride 2 in conv4 and conv5 layers to stride 1 and fc layers to global pooling layers).
+On Cifar100 dataset, we use `global\_pool' layer features of ResNet-20,32,44,56,68,110 and of Pre-ResNet-20,32,44,56,110,164 models.
 
-In all other experiments, eight different features are extracted from the following:
-%\begin{itemize}
-%  \item `fc6' of VGG16,VGG19~\cite{chatfield2014return}
-%  \item `fc6' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet}
-%  \item `pool5/7x7\_s1' from GoogleNet~\cite{szegedy2015going}
-%  \item `pool5' of ResNet-50,101,152~\cite{he2015deep}
-%\end{itemize}
-``fc6'' of VGG16, VGG19~\cite{chatfield2014return},
+In all other datasets, eight different features are extracted from the following: ``fc6'' of VGG16, VGG19, 
 ``fc6'' of AlexNet,CaffeNet~\cite{krizhevsky2012imagenet},
-``pool5/7x7\_s1'' from GoogleNet~\cite{szegedy2015going},
-and ``pool5'' of ResNet-50,101,152~\cite{he2015deep}.
-We use the official pre-trained models provided by Caffe Model Zoo
-\footnote{\url{https://github.com/BVLC/caffe/wiki/Model-Zoo}}
-.
-For the above eight models, we simply extract features without any extra operations.
+``pool5/7x7\_s1'' from GoogleNet, and ``pool5'' of ResNet-50,101,152.
 
-\subsection{Real-world Experiments}
+\subsubsection{Late Fusion}
+Five state-of-the-art late fusion methods are compared with our proposed algorithm.
+Average Score Fusion (ASF): we directly average the results from multiple classifiers, then the $L_2$ norm is applied on each classifier's results for normalization.
+Multiple Kernel Learning (MKL): MKL learns a weight coefficient $w$ for each classifier, and the final scores are obtained from function $f(s)=w^{T}s,~\sum w = 1$.
+Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}: we modify the core alogrithm in RCEC to recover $\bX$ from $L$ in Eq.~\ref{eq:l12_mf}, and use the same post process.
+Feature Weighting via Optimal Thresholding (FWOT) \cite{xuiccv2013feature}: they propose to learn thresholding, smoothing parameters and weights in a joint framework to combine multiple prediction results.
+LPBoost~\cite{gehler2009feature}: A variant linear combination is applied to multiple classifiers to boost performance.
 
-In this section, we introduce the details about our experiments on each data set,
-and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
-Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
-The computational cost of cross-validation is not counted in FWOT and LPBoost.
+The parameter $\mu$ is selected from $\{0.1, 1, 5\}$,
+$\rho$ is select from $\{1.01, 1.05, 1.1\}$
+and $\epsilon$ is select from $\{1e-2, 1e-3, 1e-4\}$ in all our experiments.
+Among different parameters, there are only small differences of the prediction performance.
+LIBLINEAR~\cite{fan2008liblinear} is adopted for our basic classification toolbox.
+The parameters are set as default in LIBLINEAR and liblinear-mkl, unless otherwise specified.
+For RCEC method, we use 5 folder cross validation to select the best parameter $\beta$ from $\{0.01,1,2,4,6,...,20\}$ and set $\lambda = 0.1, \gamma = 0.01$, which are suggested by author~\cite{yiicdm2012robust}.
+For FWOT, the smoothing parameter candidates are $\{0.5, 0.6, ...
+, 0.9\}$ and the parameter $C$ in is selected from $\{10^{-4},10^{-2},...,10^{4}\}$ according to cross-validation, which is same in~\cite{xuiccv2013feature}.
+For LPBoost, we use cross-validation to pick up the best $\nu$ from $\{0.5,0.6,0.7,0.8,0.9\}$ suggested in~\cite{xuiccv2013feature}.
 
-For action recognition, we present the comparison results on UCF 101 dataset.
-UCF101 contains 13320 videos collected from YouTube, categorized into 101 human action classes.
-We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
-As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by LIBLINEAR.
-Then by applying five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
-Results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}, in which we illustrate the performance of six fusion methods.
-To be noted, FWOT is too slow to train, we do not show its result (more than one day).
+Five datasets are used for late fusion comparison.
+UCF 101 is commonly used for action recognition task, which has 9573 training videos and 3783 testing videos, categorized into 101 human action classes.
+CIFAR-10 dataset contains 60000 pictures with 10 classes.
+CIFAR-100 similar with CIFAR-10, except it, has 100 classes containing 600 images each.
+The Oxford-IIIT-Pet dataset contains 7349 images covering 37 different breeds of cats and dogs.
+PASCAL VOC 2007 is a dataset for general object detection and image classification.
+We only use the image with a single class, which includes 6146 images.
+For UCF 101, we use the official split-1 set for training and testing.
+For Oxford-IIIT-Pet and PASCAL VOC 2007, we randomly sample fifty percent pictures as our training data and the others as testing data.
+We repeat the sample, training and fusion process five times to get fair results.
 
-In CIFAR-10 dataset, totally 60000 32x32 color pictures are categorized into 10 classes, with 6000 pictures per class.
-There are 50000 training data and 10000 testing data.
-Fourteen CNN features are extracted from multiple state of the art models.
-This experiments exhibit the ability of our algorithm to handle large scale data.
-
-As we have 50000 training data and 10000 testing data,
-The FWOT algorithm has one step to deal with $n\times n$ matrices, which are excessive to train~(more than one day).
-The LPBoost algorithm requires to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
-\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
-which occupies too much memory and still consumes long time to train,
-so we solve this problem by using sparse matrices and parallel computation in MATLAB.
-We also use `-s 2' parameters in LIBLINEAR to speedup training process.
-Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
-
-CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
-There are 50000 training data and 10000 testing data as CIFAR-10.
-Twelve CNN features used in this experiment are described in the feature selection section.
-Training and comparison process are the same as CIFAR-10.
-Detailed results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
-
-The Oxford-IIIT-Pet dataset contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
-There are roughly 200 pictures in each category with a large variations in multiple views, such as pose, scale and lighting.
-We randomly sample fifty percent pictures as our training data and the others as testing data.
-And then we train svm on each single feature and fuse the predictions by our proposed method.
-We repeat the sample , training and fusion process five times to get fair results.
-The comparison results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
-
-%% VOC07
-PASCAL VOC 2007 is a dataset for general object detection and image classification.
-In our experiments, we only use the image level annotation information.
-Since each image may contain more than one label, we filter the multi-label images, resulting in a clean dataset with 6146 images.
-The procedures of sampling, classification and fusion are similar as Oxford-IIIT-Pet.
-
-From Table~\ref{table:total_acc}, our proposed algorithm provides significant improvement comparing with other effective late fusion methods on most datasets.
+Table~\ref{table:total_acc} shows the mean accuracy results for the five datasets, and our proposed algorithm provides a significant improvement compared with other effective late fusion methods on most datasets.
 Additionally, our algorithm is more efficient than other late fusion methods in most situations.
 As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale datasets.
-\yanred{
-However, the time consumption of ours is acceptable in all experiments and quite fast on CIFAR-10/VOC2007.
+For example, FWOT is too slow to train; thus we do not show its result for UCF101 and CIFAR (more than one day).
+The time consumption of ours is acceptable in all experiments and quite fast on CIFAR-10/VOC2007.
+Our method and RCEC have the similar range of running time. Nevertheless, our method outperforms RCEC regarding accuracy for all the five datasets.
 In conclusion, our method can handle the large scale problem efficiently and yield stable performance.
-}
+
+\subsubsection{Feature Fusion}
+Feature fusion usually has some limitation when we combine too many models.
+For example, directly training a fusion model that fuses several CNN models may be intractable due to excessive GPU memory consumption.
+We compare three different feature fusion methods in Table~\ref{table:feature}.
+The Bayesian-based method \cite{chen2012bayesian} requires the same dimensionality of features for fusion.
+Thus we choose the global-pooling layer's feature of all residual-based networks used in Table~\ref{table:total_acc} for \cite{chen2012bayesian}.
+For the other two feature fusion methods, we directly concatenate the global-pooling layer (or the probability prediction layer) of the same networks in the Bayesian-based method; and use a fully connected layer with ten output to combine the concatenation feature to the final prediction for the CIFAR-10 dataset.
+For our fusion algorithm, we use the CNN predictions rather than the SVM predictions used in Table~\ref{table:total_acc}.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+   Bayesian  & Pooling Layer & Prob Layer   & \bf{Ours}     \\\hline
+    94.10\%  & 95.21\%       &   95.32\%    & \bf{95.93\%}  \\
+\hline
+\end{tabular}
+\caption{Mean accuracy on CIFAR-10 to compare different feature fusion methods with ours.
+Bayesian represents \cite{chen2012bayesian}, ``Pooling Layer''/``Prob Layer'' represent we concatenate the features from the last pooling layer/the probability layer.}
+\label{table:feature}
+\end{table}
+
+From the Table~\ref{table:feature}, our method still achieves the best performance among these feature fusion methods.
+Some other detailed comparison can be found Appendix D.
 
@@
 
-In this section, we compare three proposed post strategies on three small datasets: Wikipedia~\cite{rasiwasia2010new}, Oxford Flowers 17~\cite{nilsback2006visual} and Pascal Sentence~\cite{Li2006One}.
-Wikipedia dataset contains paragraphs of text for each picture, and total 2866 image-text pairs are categorized into 10 class.
-Only the image-level annotation is used in our experiments.
-PASCAL VOC 2007 contains 9963 images annotated with object-level information, which means each picture may have zero or more than one class.
-We choose 6146 images classified into 20 classes by filtering out the no-single class data.
-Oxford Flowers 17 has seventeen flower categories with 80 images for each category.
-Pascal Sentence contains 1000 images annotated by caption information and categorized into twenty classes.
+In this section, we compare three proposed post strategies on three datasets.
+Wikipedia dataset \cite{rasiwasia2010new} contains paragraphs of text for each picture, and total 2866 image-text pairs are categorized into 10 class.
+Oxford Flowers 17 \cite{nilsback2006visual} has seventeen flower categories with 80 images for each category.
+Pascal Sentence \cite{Li2006One} contains 1000 images annotated by caption information and categorized into twenty classes.
 Fifty percent of data are sampled as training set and the others as testing set, and experiments are repeated five times on above three datasets.
@@
 
-In this sub-section, we compare the performance of our algorithm with the state-of-the-art single models.
-%we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
+We compare the performance of our algorithm with the state-of-the-art single models.
 In the previous experiments, we use SVM classifiers based on different features to make a fair comparison with some MKL based methods.
-The performance of SVM classifiers are usually not as good as the results directly predicted by CNN models.
+The performance of SVM classifiers is usually not as good as the results directly predicted by CNN models.
 In order to obtain a higher result, we directly use multiple state-of-the-art CNN predictions and fuse them by our method.
+The models used for ``Ours$^{*}$'' in Table \ref{table:state_of_the_art} are shown in Table \ref{table:models}.
 We demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table~\ref{table:state_of_the_art}.
@@
 \begin{table}[ht]
-\begin{center}
-\begin{tabular}{| c | c | c |}
-    \hline
+\centering
+\begin{tabular}{| c | c | c |} \hline
                                            & CIFAR-10             & CIFAR-100  \\\hline
-\multirow{2}{*}{ResNet~\cite{he2016identity}} & 110, 134, 164        & 56, 110, 164  \\
+\multirow{2}{*}{ResNet} & 110, 134, 164    & 56, 110, 164  \\
                                            & $164^{*}$, $200^{*}$ & $110^{*}$, $164^{*}$  \\\hline
-\multirow{2}{*}{WRN~\cite{zagoruyko2016wide}} & 16-10, 22-8, 28-10   & 16-10, 22-8, 28-10  \\
+\multirow{2}{*}{WRN} & 16-10, 22-8, 28-10  & 16-10, 22-8, 28-10  \\
                                            &    40-4, 40-8        & 40-4  \\\hline
-NIN~\cite{lin2013network}                     &     -                & -  \\ \hline
+NIN                                        &     -                & -  \\ \hline
 \end{tabular}
-\end{center}
 \caption{Model selection for CIFAR-10 dataset.
@@
 ``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
-In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
-NIN network has only one formula, so we do not list its depth.}
+In WRN~\cite{zagoruyko2016wide} block, ``x-y'', x represents the depth, and y represents the widening factor.
+NIN~\cite{lin2013network} has only one formula, so we do not list its depth.}
 \label{table:models}
@@
     Methods              &  CIFAR-10       & CIFAR-100           \\\hline
-NIN~\cite{lin2013network}                           &   8.81          &  35.67              \\\hline
-Highway~\cite{srivastava2015highway}                &   7.72          &  32.39              \\\hline
-ELU~\cite{clevert2015fast}                          &   6.55          &  24.28              \\\hline
-Pre-ResNet-1001~\cite{he2016identity}               &   4.92          &  22.71              \\\hline
-WRN-28-10~\cite{zagoruyko2016wide}                  &   4.17          &  20.50              \\\hline
-ResNeXt-29, $16\times64d$~\cite{xie2016aggregated}  &   3.58          &  17.31              \\\hline
-Ours                                                &   \textbf{3.47} &  \textbf{17.24}     \\\hline
+Highway                  &   7.72          &  32.39              \\\hline
+Pre-ResNet (1001 layers) &   4.92          &  22.71              \\\hline
+WRN-28-10                &   4.17          &  20.50              \\\hline
+ResNeXt-29-16x16d        &   3.58          &  17.31              \\\hline
+Ours$^{*}$               &   3.47          &  17.24              \\\hline
+Ours (fuse ResNeXt)      &   \textbf{3.19} &  \textbf{16.99}     \\\hline
 \end{tabular}
@@
 
-We carefully cite the best performances reported in their papers
-\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}.
+We carefully cite the best performances reported in their papers, Highway \cite{srivastava2015highway}, Pre-ResNet \cite{he2016identity}, WRN-28-10 \cite{zagoruyko2016wide}, ResNeXt-29-16x16d \cite{xie2016aggregated}.
 As can be observed, our fusion algorithm is capable of further improving the performance of single models significantly,
-even a single model has satisfactory performance with deeper depth or wider channel.
-%However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
-We emphasize that ResNeXt~\cite{xie2016aggregated} is the best performer in single models, and our method only fuses models which perform worse than ResNeXt,
-but can achieve lower test error than ResNeXt.
+even a single model has the satisfactory performance with deeper depth or wider channel.
+We emphasize that ResNeXt is the best performer in single models, and our method only fuses models which perform worse than ResNeXt, but can achieve lower test error than ResNeXt.
+Including the results of ResNeXt-29-16x16d in our fusion method, we can obtain a much lower test error.
 This demonstrates the aim and benefit of our late fusion method.
@@
 We thus propose an ALM-based algorithm to cope with the non-smooth loss.
-%Specifically, our proposed algorithm first rejects outliers on a label indicator matrix by $\ell_{1,2}$ loss,
-%and then generates the predictions by combining robust outlier rejection information and prediction confidence scores from basic classifiers.
-Empirical studies on large scale real-world data sets demonstrate that our proposed method can effectively improve performance compared to the state-of-the-art late fusion methods.
+Empirical studies on large scale real-world data sets demonstrate that our proposed method can effectively improve performance compared to the state-of-the-art fusion methods.
 
-{\small
-\bibliographystyle{ieee}
+{
+\footnotesize
+\bibliographystyle{aaai}
 \bibliography{egbib}

### 2018-05-17 cvpr-2017/review-cvpr/review-cvpr.tex
re-organize

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{bm}
%\usepackage[vlined,boxed,ruled]{algorithm2e}
\usepackage{url}
\usepackage{xspace}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\def\yanred{\textcolor{red}}

\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\def\yanred{\textcolor{red}}
\def\yanblue{\textcolor{blue}}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}
 \begin{document}

% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

%\title{Outlier Reject for Late Fusion on Visual Recognition}
\title{Reviews for Late Fusion via Subspace Search with Consistency Preservation}

\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}

\maketitle

\section{Assigned Reviewer 1 (Borderline)}
\subsection{Paper Summary}
This paper proposed an interesting late prediction fusion strategy by formulating the problem as a fixed-rank matrix recovery problem with additional $l_{1,2}$ norm accounting for outliers.
In order to solve the corresponding formulation, the authors proposed an ALM based optimization algorithm which transforms original unknown problem to solvable existing subproblems.
Empirical studies on popular datasets show promising performance gains from existing late fusion alternatives.

\subsection{Paper Strengths}
This paper is well written. The logic flow is clear and most technical parts are correct.
I like the idea to apply matrix factorization with $l_{1,2}$ norms to deal with outliers in the late prediction fusion problem. 
Low rank matrix factorization and/or many flavors of sparse-inducing norms have been well studied focusing on their theoretical properties. 
Using such formulation is both intuitively well-grounded e.g. [1] and empirically validated as shown in the experiment sections. 
Therefore I found this proposal to be interesting and useful.
The authors also proposed an optimization solution via ALM to transform their formulation to solvable subproblems. The application of ALM is standard. I am less experience in the field of model ensemble and other fusion methods, I cannot judge the novelty of this application.

[1] Liu, Guangcan, et al. "Robust recovery of subspace structures by low-rank representation." IEEE Transactions on Pattern Analysis and Machine Intelligence 35.1 (2013): 171-184.

\subsection{Paper Weaknesses}
One of my major concern is that, I found the technical part in Sec 3.2 a little over-sold. For example, Theorem 1 aka the convergence of ALM is not novel and should not appear as a theorem of this paper without any reference. The same concern applies to the technical derivations after eq (6) which are basically contents from [41] etc.

There are some minor mistakes as follows:

line 173-174 grammar error
line 212-215, I think the notation of m and C were messed up here, please fix it.

\subsection{Preliminary Evaluation}
I found the application of low-rank matrix factorization and $l_{1,2}$ norm to the model fusion problem to be interesting. However, I think the technical contribution is relatively limited and I suggest the authors to re-organize their technical parts according to details above.

\section{Assigned Reviewer 2 (Weak Reject)}

\subsection{Paper Summary}
This paper presents a method for fusing the outputs of an ensemble of classifiers using a low-rank constraint coupled with a column-wise sparsity penalty. The resulting pipeline is deployed on a number of recognition tasks and compared against existing baselines.

\subsection{Paper Strengths}
With the rise of many different methods for generating diverse feature types and classifiers, fusion methods can have significant practical value, especially if efficient implementations exist, such as that proposed here.

\subsection{Paper Weaknesses}
This paper exhibits weaknesses that relate to technical novelty and significance. 
First, the basic concept of performing late fusion using robust low-rank representations has already been explored in the literature, e.g., references [10] and [50]. Hence the remaining space for novelty and impact lies here only in attempts to speed up these formulations by replacing the nuclear norm with a low-rank matrix factorization, a common substitution in the matrix recovery literature (see P. Jain et al., "Low-rank Matrix Completion using Alternating Minimization," STOC 2013). The proposed algorithm itself is based on a very standard augmented Lagrangian formulation that is commonly used for related problems with $L_{(1,2)}$ column sparsity norms, adopted to mute the impact of outliers (e.g., Liu et al., "Robust Recovery of Subspace Structures by Low-Rank Representation," PAMI 2013). We then must examine the various component parts for technical contributions, but here is where additional issues arise.

First, all of Section 3.3, and more than one page of the technical meat of the paper, is spent attempting to solve the subproblem given by eq. (6), which is just minimizing the Frobenius norm of M - X over X, subject to a low-rank factorization constraint $X = UV$. Of course there exists a well-known closed-form solution to eq. (6). Indeed this problem is equivalent to solving $min_X || M - X ||_F s.t., rank(X) <= p$, which has a simple solution in terms of the SVD of M. Please see Vidal and Favaro, "Low Rank Subspace Clustering," Pattern Recognition Letters, 2013, although this result exists in many standard text-books as well given that it is just another basic representation of PCA.

Hence my guess, although not stated in the paper, is that perhaps the obvious closed-form solution via SVD is deemed too computationally expensive in high dimensions? However, even if this is the case, one could always just use standard alternating minimization to solve for U with V fixed and V with U fixed as is done in matrix recovery problems (see the P. Jain et al., 2013 reference from above). Each of these iterations will also have closed-form solutions via least squares, but at a much lower dimension, and geometric convergence can be guaranteed, often to the global solution. In contrast, for the proposed method from Section 3.3 via a complicated Riemannian manifold method, it is unclear to me whether or not any kind of convergence guarantee to a global solution is ever possible.

So Algorithms 2 and 3 may be unnecessary, or at least replaceable with something much simpler, and we turn to the other subproblem of updating E. But this is just an obvious thresholding result as well since the problem easily decouples across columns, so there is no wiggle room for novel technical contributions here (in fact, update rules of this type appear in many places, including reference [47]).

Beyond this, from a technical contribution standpoint we have Theorem 1, which relates any accumulation points of the proposed iterations to stationary points (presumably assuming the inner loop updates for X actually even converge). However, the underlying objective function is nonconvex, and some typcial ALM analysis may not apply, so how do we even know that the sequence of $lambda_k$ will be bounded as required, or that accumulation points will even exist? Without these aspects, the result has limited value, so it would seem that some details are missing from this construction.

Finally, from an empirical standpoint, in Table 1 we observe that LPBoost performs similarly to the proposed method; however, it may be difficult to draw firm conclusions given all of the post-processing steps and parameters involved in tuning various methods. Additionally, in Table 5, why not compare against other state-of-the-art fusion methods, as opposed to just single model results?

\subsection{Preliminary Evaluation}
Given the incremental nature of this paper per the points raised above, my feeling is that this work is not yet sufficient for CVPR, but I am open to counterarguments during the rebuttal period as I could have misinterpreted certain contributions.

\subsection{Reproducibility}
I did not quite understand the description of the experiments carried out in Section 4.5. Is the point that a fused model with extra information can perform better than the best single model performance as implied in lines 782-783? If so this seems like a rather obvious conclusion, but I could be missing something.

\section{Assigned Reviewer 3(Weak Accept)}

\subsection{Paper Summary}
The paper proposes a matrix decomposition approach to discovering structure in the set of labels for a set of data points produced by multiple classifiers. The structure is then utilized to make a consistent prediction in a way that is robust to outliers by some of the classifiers.

The focus is on speed and robustness. The method is faster than the baselines used in comparisons. In fact, it is by several orders of magnitudes faster by the method that is closest in accuracy.

\subsection{Paper Strengths}
Looks correct to me. I could think of many other ways of doing this, and can't be sure that the authors' approach is the best, but in comparisons, it achieves all the goals.

\subsection{Paper Weaknesses}
Minor:

- The math starts in lines 208-215 with notation that does not match the figure, or the math later (which does match the figure).

- Equation 5, line 302-3, I think you missed $\mu/2$ in front of the first term

- Discuss how the $l_{1,2}$ norm helps with outliers; show what happens if you use $l_2$ norm as usual

- Post-processing to finalize the labels is a bit adhoc and generalizes consensus voting; What if some classifiers are adversarial (deliberately, or accidentally, like switching two labels consistently). Even if some classifiers consistently switch labels for some classes, they would still be adding the information to the ensemble, and the subspace model would in fact catch it (you'd see that $L=1$ really is evidence for $L=2$). It would be worth discussing and showing an example where one of the classifiers is bad like this but helps the ensemble do well (George Constanza idea of doing the opposite; the decomposition detects Constanza's)

\subsection{Preliminary Evaluation}
See above, plus a suggestion:

There is no reason why this method could not be used to add classifiers that predict things we are not interested in (e.g., we are classifying image as indoors/outdoors, but some oft he classifiers do not predict these labels, but instead predict some of the imagenet categories)

\end{document}

### 2018-07-07 BACKUP/cvpr-2017/Fusion-cvpr2017-RebuttalKit/rebuttal-fusion.txt
update for minor

\section{Overall}
We thank all the reviewers.
R3 is positive.
R1 has some suggestions about technical analysis.
R2 ...
We take the comments seriously and will carefully revise the paper. 
Typos will be corrected. Code will be released.

\section{For Assigned Reviewer 1}

Q1: The technical part in Sec 3.2 a little over-sold.

A1:
First, ALM is usually used for convex problem~[50] and (G. Liu etal, TPAMI 2013),
but our Problem~(2) is non-convex.
Therefore, the convergence behavior of Algorithm 1 may be unclear.
Second, to make the paper self-contained, it is necessary to present every phase of Algorithm~1.
Third, we explicitly indicate the connection between the definition (Eq (8)) and the computation (Algorithm 2) of Riemannian gradient by presenting Lemma 1.
This did not present in the previous work.
To make the contributions more clear, we will provide more references and explain the difference between our paper and previous works as suggested.

\section{For Assigned Reviewer 2}

Q1. Weakness of technical novelty and significance}

A1:
Previous works~[50] that formulate late fusion as matrix completion are based on nuclear norm.
They cannot handle large-scale problems.
We thus propose an efficient matrix factorization-based algorithm.
On one hand, previous matrix factorization algorithms only consider smooth loss rather than non-smooth robust loss.
On the other hand, previous ALM-related papers consider convex problems, so it is unclear how its convergence behavior is in the non-convex case.
To address both issues, this paper proposes a new matrix factorization-based algorithm to handle non-smooth loss and provides convergence analysis.

Q2. Problem~(6) can be solved by SVD or alternating minimization.

A2:
In P. Jain et al., 2013, the authors provide global optimality of $\epsilon$-solution (i.e. the loss function satisfies $|| M - X ||_F^2 \leq \epsilon$. See Theorem 2.5 in this paper.) of alternating minimization, rather than a strictly unique global optimum.
Our paper provides the convergence guarantee of a strictly local minimum where the gradient w.r.t. $\bX$ vanishes.
Thus, their result and ours may not be comparable.

Q3. Algorithms 2 and 3 may be unnecessary.}

A3: 
The algorithm should be self-contained and it may be necessary to describe solutions for any formula.
But we are pleasure to simplify our presentation.

Q4. Will the sequence of $\lambda_k$ be bounded as required, or that accumulation points even exist?

A4:
Boundedness of $\blambda_k$:
After the inner loop (Step 1,2) of Algorithm 1 converges, we have 
$\calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k}) = ||\bE_{k+1}||_{1,2} + \frac{1}{2\mu_{k}}(||\blambda_{k+1}||_{F}^2 - ||\blambda_{k}||_{F}^2)$.
Due to the convergence and $\frac{1}{\mu_{k}} \rightarrow 0$ when $k \rightarrow + \infty$, we have $||\blambda_{k+1}||_{F}^2 - ||\blambda_{k}||_{F}^2 < +\infty$, and thus the boundedness of $\blambda_{k}$.

As proof of Theorem 1, $k \rightarrow \infty$, $\bL - \bX_{k} - \bE_{k}$ and the gradient of $\calL$ w.r.t. $\bX_{k}$ vanishes.
Thus $\bX_{k}$ is a stationary point as long as $\bX_{k}$ is generated according to Algorithm 1.

Q5. Empirical issues in Table 1 and Table 5.

A5:
As shown in Table 1, our method outperforms LPBoost significantly on UCF-101 and CIFAR-100,
and our fusion method performs well on most datasets comparing with other methods.

Q6. Why not compare against other SOTA fusion methods in Table.5, but just single model results ?

A6:
We compare our method with state-of-the-art single models in Sec 4.5 and list the test error in Table 5 to verify the improvement of our late fusion algorithm.
Test error of competing models are referred from the original papers.
Comparison between our method and other late fusion methods is performed specifically in Sec 4.3 (Table 1 and Table 2).

Q7. Reproducibility - It is obvious that a fused model is better than the best single model.

A7:
It can't guarantee that a fused model can definitely perform better than the best single model.
By comparing with single models, we aim to verify the effectiveness of our method.
The best single model performance on CIFAR-10 is currently in~\cite{xie2016aggregated} (test error 3.58).
Our method fuse multiple single models which all perform worse than~~\cite{xie2016aggregated}, but can achieve low test error on CIFAR-10 (3.47 in Table 5).
This demonstrates the benefit of a good late fusion method.

\section{For Assigned Reviewer 3}

Q1. Discuss how the $\ell_{1,2}$ norm helps with outliers; show what happens if you use $l_2$ norm as usual}

A1:
As indicated in lines 106-110, $\ell_{1,2}$ loss preserves the fidelity within columns of $\bL$ and filters out those columns with low fidelity.
$\ell_{2}$ loss is known to be sensitive to outliers.
$\ell_{2}$ loss is not robust to large outliers and the result may be biased to them.
We will add a $\ell_{2}$ variant of our approach as a baseline in the revised version to illustrate the difference.

Q2. Discussions about classifiers are adversarial.

A2:
In fact, Sec 4.1 and Figure 2 show a similar situation: 40\% predicted labels are switched from ground-truth (adversarial classifiers).
In this situation, our algorithm performs well and recovers most of the results.

Q3. Add classifiers that predict uninterested things.}

A3:
Thanks for this interesting and helpful suggestion.
We will investigate this problem in our future work.

### 2018-07-07 BACKUP/cvpr-2017/rebuttal-cvpr/rebuttal.tex
update for minor

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{bm}
%\usepackage[vlined,boxed,ruled]{algorithm2e}
\usepackage{url}
\usepackage{xspace}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\def\yanred{\textcolor{red}}

\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\def\yanred{\textcolor{red}}
\def\yanblue{\textcolor{blue}}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}
 \begin{document}

% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

%\title{Outlier Reject for Late Fusion on Visual Recognition}
\title{Rebuttal Material 
for ``Late Fusion via Subspace Search with Consistency Preservation''}

\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}

\maketitle

\section{Review 1}
\begin{itemize}
  \item 2: (modest or incremental contribution)
  \item 2: (minor inconsistencies or small fixable errors) 
  \item 2: (relevant literature cited but could expand)
  \item 2: (more or less readable)
  \item 2: (interest limited to specialty area) 
  \item 4: (++++)
\end{itemize}

This paper presents a late fusion method based on $\ell_{1, 2}$ optimization. An efficient optimization method based on ALM is derived for solving the proposed method. The method is very simple and easy to follow. Various experiments show the significance of the proposed method.

The main drawback of this method is that if there are many samples in the test set and many different classifiers then the resulting matrix can be very large. Optimizing this large matrix can be an issue in practice.

The other problem is that it can not be applied in the case when there is only a single test sample, which is very common in biometrics applications such as verification.

\section{Rebuttal For R1}

1. Our algorithm is capable to handle large scale matrices, particularly compared to the nuclear norm based methods whose computational complexity can be cubic due to the presence of SVDs.
The per-iteration complexity of our algorithm is $O((n+Cm)C^2 +nmC)$,
(n instances, C classes and m classifiers),
which can be more efficient, and thus capable to large scale problems.

2. We agree that our algorithm is not applicable to handle the case where there is only a single test sample. However, there are many applications where there are many samples when testing. As demonstrated in our experiments, our method could perform well on these tasks.

\section{Review 2}
\begin{itemize}
  \item 2: (modest or incremental contribution)
  \item 2: (minor inconsistencies or small fixable errors) 
  \item 2: (relevant literature cited but could expand)
  \item 2: (more or less readable)
  \item 3: (some interest beyond specialty area)
  \item -2: (--)
\end{itemize}

The main contribution of the paper is proposing an ALM-based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1, 2}$ loss.
This paper aims at outlier rejection for late fusion algorithms and proposes an e cient matrix factorization based approach to fuse predictions from multiple sources. One contribution of the paper is proposed an ALM-based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1, 2}$ loss.
The comments of the paper are listed as follows:

1.The definition of outlier in the late fusion problem is not legible from Fig 1. In Fig 1, L1 and L2 are just the same, and the second and third columns of L3, which are different from L1 and L2, are marked as outlier. Generally, the decisions based on different feature representations are quite different, in this situation, what is the outlier?

2.From the description of the proposed approach, it is not clear how the method realizes late fusion via subspace search with consistency preservation.

3.The reasons for using robust $\ell_{1, 2}$ loss to catch the outlier columns should be given. As a consequence, the reasons why the proposed method is effective in handling outliers is not clear. It will be better if the paper discusses the advantages of $\ell_{1, 2}$ loss in catching the outlier columns.

4.In the proof of Theorem 1, u should be uk and u/2 should be 2/u.

5.In the feature extraction experiment, the rationality of the selected features is not clearly shown. In this experiment, the author just reported the selected features of each data set, this can not illustrate the advantages of the proposed method in feature selection.

In conclusion, I suggest that the article may not be accepted.

\section{Rebuttal For R2}

1. Decisions on different features are not necessarily very different from each other, given sufficient training data and reasonably good feature representations.
As shown in Fig 1, we convert the predictions of all classifiers to a 0/1 indicator matrix,
and assume that there are anomalous columns,
which means for specific classes, some classifier would perform poorly.
Therefore, by applying $\ell_{1, 2}$ loss, our algorithm would work well in the case that there are sparse anomalous (outlier) columns.

2. We introduce a low-rank constraint on the indicator label matrix to our late fusion algorithm,
which would search the solution in a low-rank subspace of the label matrix.
Meanwhile, the low-rank structure would preserve consistency among all the classifiers.

3. In an indicator matrix, $\ell_{1, 2}$ loss preserves the fidelity within each column by L2 loss in the vertical direction,
and is tolerant of sparse errors across all the columns by L1 loss in the horizontal direction.
Thus, if there are outlier columns, $\ell_{1, 2}$ loss would simply capture these columns whose l2 loss is sufficiently large.

4. In the experiment, we select the best-performing CNN models for feature extraction.
We believe that they are good at representing different aspects of data.
By leveraging the classifiers trained on single features as base classifiers,
we investigate the performance improvement of our proposed late fusion algorithm.
Experimental results show performance improvement by fusing their decisions, which verifies the validity of our algorithm.

\section{Review 3}
\begin{itemize}
  \item 2: (modest or incremental contribution)
  \item 3: (correct)
  \item 3: (excellent coverage of related work)
  \item 2: (more or less readable)
  \item 3: (some interest beyond specialty area)
  \item 2: (++)
\end{itemize}

The authors provide an algorithm that performs late fusion, meaning that it combines predictions of classifiers that use separate sets of features. Their approach learns a model by optimizing an objective based on matrix factorization with the non-smooth $\ell_{2,1}$ loss, via ALM.

The authors introduce a rank constraint on L to preserve consistency between classifiers.
\yanred{This can also be achieved through a penalty that explicitly computes differences between predictions.}
I don’t think the term `accumulation point' is correctly used.

The paragraph where the `tangent bubble' is introduced needs to be better explained. Please break down into several sentences and give some intuition as to why it’s needed.

The authors compare their methods against algorithms from the same class (i.e. fusion). However, there are other state-of-the-art techniques that outperform their accuracy.

For CIFAR-10, better results were obtained with fractional Max Pooling

https://arxiv.org/abs/1412.6071

Wide residual networks also obtained higher accuracy

https://arxiv.org/abs/1605.07146

Why should we use this approach for these particular applications?
The runtime is faster and the models are simpler and potentially easier to understand, but this doesn’t seem to be crucial for image classification tasks.

\section{Rebuttal for R3}

1. Accumulation point is the limit point of a sequence, and used in many literatures, eg, Tae-Hyun Oh, et al. TPAMI2016 doi:10.1109/TPAMI.2015.2465956.

2. We guess the reviewer is asking “tangent bundle”.
It consists of all the tangent spaces, to which we restrict the inner product of two tangent vectors.
The introduction of the tangent bundle is crucial for optimization on Riemannian manifold.
More details can be found in (Vandereycken, B. 2013) in main text.

3. This work presents a late fusion algorithm based on a set of classifiers trained on individual features.
We investigate the performance of the proposed late fusion algorithm, instead of achieving higher results on a specific task, eg, CIFAR10.
As a result, we treat the fusion methods as baselines, rather than the state-of-the-art models trained on a single feature.
By replacing the base model with the state-of-the-art single model,
the performance of our method would also improve and may outperform the base model.

\iffalse
\subsubsection{For Review 2}

1.~Fig 1 is an illustration to explain how our algorithm works via synthetic data.
%% hard label -> multiple binary problem
%% Training data , sufficiently good supervison , their from multiple can not be quit different .tend to be stable. similar .
The soft decisions based on different feature representations are certainly quite different,
but we convert them to hard label assignment and further decompose them into multiple binary classifition results.
With sufficiently good supervison, e.g enough training data,
these hard binary decisions from multiple features can not be quit different and tend to be stable and similar.
In Fig 1, the algorithm process the hard input to generate soft values,
and the most different columns comparing with the original one are the outliers as abnormal columns.
From matrix X, we could see the last two columns of L3 are quite different with the original one,
so outliers are detected and repaired.

2.~We pursue a low rank property of the decision matrix by finding a solution in the subspace, which is subspace search.
Low rank structure always results in consistency among multiple decisions.
%leading into a subspace structure, and  is used to solve Algorithm 3 LRGeomCG which is mentioned in Formula 10.
%consistency preservation

3.~$\ell_{1, 2}$ loss enforces sparsity over groups and non-sparsity within a group~[1].
Specifically, $\ell_{1, 2}$ exploits L2 loss within columns to guarantee high fidelity,
then by L1 loss the columns with high L2 loss tend to be removed.
%among all the columns we use L1 loss to 
%but for some abnorm columns we use L1 loss to 
%4.~Sorry, it's a mistake in writing.

5.~\yanred{The CNN models for extracting features in our paper used to be the state-of-the-art CNN models.
They are good at different aspects of feature representations.
%The feature are extracted from the several commonly used deep learning nerual networks, which used to be the state-of-art CNN models.
Comparing the hand-craft features, a single CNN feature, like fc6 from VGG16, outperforms than fuse multiple hand-craft features on most dataset (e.g Oxford-Flower 17 in [2]).
Further more, our algorithm improves performance from these advanced CNN features comparing with other state-of-the-art fusion methods in most dataset.}

\subsubsection{For Review 3}

1. We carefully use the term `accumulation point' according to Proposition 1 of [4].

2. We guess the reviewer would like to ask about `tangent bundle'.
Tangent bundle consists of all the tangent spaces, 
to which we restrict the inner product of two tangent vectors.
The definition of the tangent bundle is crucial for optimizaiton on Riemannian manifold~[3].

3. This paper is to verify improvement of late fusion.
It may not be necessary to compare with single model.
We can replace classifiers' results with single model's results from the state-of-the-art techniques, and it will also lead improvements.

4. It's unfair to simply compare our results with state-of-the-art techniques by two facts:
1) the single classifier's result in our experiments are trained by SVM using pooling or fully-connection features.
This will reduce the performance comparing with the results directly from CNN models.
2) we use the features from the state-of-the-art CNN models.
But we do not fine tune them on specific dataset (e.g UCF-101) or select the best architecture due to expensive CNN model training cost (e.g ResNet-1001 on CIFAR-10).

5. Single model has limition on representations.
For example, WRN-28-10 and ResNet-1001 on Cifar-10 can hardly improve their performance by making layer deeper or channel wider.
In this situation, our approach can significantly improve performance of the single state-of-the-art model.

\subsubsection{For Review 1}

1.~Specifically, the theoretical complexity for our algorithm is $O((n+Cm)C^2 + nmC^2) + O(nCm)$, (n testing instances, C classees and m classifiers).
It's linear for growing of n and m, but has cubic complex of C.
So it can optimize large matrix in some special situations~(e.g large instances with small classes)

2.~Our algorithm works for some applications but can not be qualified to all situations.
To our knowledge, verification is to ask two things are identity or not. A common way is to extract features and calculate cosine distrance.
It can be seen as a binary classification problem in some way and if there are multiple features then our algorithm can also handle verification problem.

\section{Refference}
\begin{itemize}
  \item [1] A Robust Convex Formulation for Ensemble Clustering.
  \item [2] On Feature Combination for Multiclass Object Classification.
  \item [3] Low-rank matrix completion by Riemannian optimization.
  \item [4] Partial sum minimization of singular values in Robust PCA: Algorithm and applications
\end{itemize}

\fi

\section{Final Version}

We thank all the reviewers. R1 and R3 are positive. R2 has a few questions regarding the experiment and implementation details, without criticizing the technical part and novelty. We will carefully revise the paper according to all suggestions.

\subsubsection{To R1 }

1. The complexity of existing nuclear norm based methods is cubic due to the presence of SVDs.The per-iteration complexity of our algorithm is $O((n+Cm)C^2 +nmC)$, which is more efficient.

2. We agree that our algorithm can’t handle the cases where there is only a single test sample. However, there are many applications where there are more than one samples.

\subsubsection{To R2}

Q1. Decisions of features are quite different.

A1. 
Please kindly note that even though the “soft labels” derived from different features could be different,
the “binary class labels” should not be very different,
given sufficient training data and reasonably good feature representations.
In Figure 1, we converted the predictions of all features to a “binary” indicator matrix.
In this case, if the feature is a good one the binary class labels are expected to be consistent among different features.
If a binary label is very different from others, it is more likely it is an outlier which should be filtered out.

Q2. how to implement late fusion

A2. The output of Algorithm-3, i.e., X, is used to generate the final labels by post processing (“post process” section). Step 2 and Step 3 in Algorithm-3 perform the subspace search. The procedure of Algorithm-3 guarantees the consistency of different classifiers by imposing the rank constraint into.

Q3. Why robust loss

A3. Thanks for the question. We will add the discussion in the revision. Briefly, the l1,2 loss preserves the fidelity within each column by L2 loss vertically, and is robust to sparse errors across all the columns by L1 loss horizontally.  l1,2 loss will capture the outlier columns whose l2 loss is large. 
 
Q4. Experiment:

A4. We used the best-performing CNN models for feature extraction including VGGNet, GoogleNet, etc..  These features are fairly state of the art. They have been widely used in various recent research papers and have been verified the most effective features by recent internationally recognized competitions such as the ImageNet competition.
   
\subsubsection{To R3}

Q1. Accumulation point

A1. Accumulation point is the limit point of a sequence. We will avoid using this term in the revision.

Q2. tangent bundle

A2. Tangent bundle is crucial for Riemannian optimization because it helps define the Riemannian metric on manifold, which is the base of computation of Riemannian gradient. More details can be found in (Vandereycken, B. 2013) and will be added into our revision.

Q3: Not compare to suggested papers

A3: The focus of this paper is late fusion as opposed to improving a specific task, eg, CIFAR10. Thus, we used the fusion methods as baselines, rather than the state-of-the-art models trained on a single feature. Following your suggestion, we additionally take wide residual network as an input of our algorithm for fusion, and the performance is better than the recommended paper. We will report this result and cite the two papers.

\end{document}

### 2018-07-07 BACKUP/cvpr-2017/RLF_MF_v2.tex
update for minor

--- 2017-02-28 back-aaai/RLF_MF.tex
@@
-\def\year{2017}\relax
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article}
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
+\usepackage{cvpr}
+\usepackage{times}
+\usepackage{epsfig}
 \usepackage{graphicx}
 \usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{subfigure}
+\usepackage{multirow}
 \usepackage{amsthm,mathrsfs,amsfonts,dsfont}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
-\usepackage{threeparttable}
-\usepackage{multirow}
-\usepackage{subfigure}
-\usepackage{color}
 \usepackage{epstopdf}
@@
 
-\frenchspacing
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
-\pdfinfo{
-/Title (Insert Your Title Here)
-/Author (Put All Your Authors Here, Separated by Commas)}
-\setcounter{secnumdepth}{0}
+% Include other packages here, before hyperref.
+
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+% \cvprfinalcopy % *** Uncomment this line for the final submission
+
+\def\cvprPaperID{3651} % *** Enter the CVPR Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ifcvprfinal\pagestyle{empty}\fi
 \begin{document}
 
-% The file aaai.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-%\title{Consistent Late Fusion for Visual Recognition}
+%%%%%%%%% TITLE3
 \title{Late Fusion via Subspace Search with Consistency Preservation}
-%% Efficient
-
-\author{AAAI Press\\
-Association for the Advancement of Artificial Intelligence\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\
+\author{First Author\\
+Institution1\\
+Institution1 address\\
+{\tt\small firstauthor@i1.org}
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
+% To save space, use either the email address or home page, not both
+\and
+Second Author\\
+Institution2\\
+First line of institution2 address\\
+{\tt\small secondauthor@i2.org}
 }
@@
 However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
-To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
+To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
 Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.
 
-To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
-As for outlier detection, as shown in Figure~\ref{fig:framework} (notations are introduced shortly), we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
-Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{resource/frame_work.pdf}
+\end{center}
+\caption{Framework of our late fusion algorithm.
+In this example, there are 10 instances 3 classifiers and 3 classes.
+Predictions of each classifier are converted to a binary indicator matrix,
+denoted by $L_1$, $L_2$ and $L_3$.
+Let $L = [L_1, L_2, L_3]$ be the label matrix.
+Our algorithm detects and removes the outliers on $L$ and then recover the underlying low-rank subspace of $L$ as the prediction for testing instances.
+We finally apply a post-processing method to generate the fused results.
+%First, there are $\calC=3$ classifiers' results for $n=10$ instances.
+%Each of them are converted into ``binary'' indicators from the soft prediction results, as $L = [L_1, L_2, L_3]$.
+%Then, our ALM-based optimization process the binary indicator matrix into a recovered matrix $X$,
+%which can be treated as soft prediction scores for testing instances.
+%Finally, the fused prediction results are generated by a post-processing method.
+}
+\label{fig:framework}
+\end{figure}
+
+To prevent from the expensive nuclear norm minimization,
+in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
+%As for outlier detection, our framework is shown in Figure~\ref{fig:framework} (notations are introduced shortly).
+Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
+As for outlier detection,
+we propose to filter out these inconsistent predictions on specific classes of models (See Fig.~\ref{fig:framework}.
+Notations are introduced shortly.).
+%as shown in Figure~\ref{fig:framework} (notations are introduced shortly),
+Due to the fact that the $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction,
+we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
+Furthermore, most existing matrix factorization optimization methods,
+however, only consider smooth loss functions, rather than the nonsmooth loss.
 We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
@@
   \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss. 
+  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
+  %It is capable of handling large scale problems.
   \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
@@
 
-%% Latent Fusion,
+Some other fusion algorithms are propsed for specific tasks, which would be hard to extend to general problems.
+In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
+and they combine the scores of multiple features weighted by their effectiveness.
+In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features impove the accuracy of action recognition.
+In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
+\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
+\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
+
+%% Feature 
+%Some algorithms exploit the early fusion methods, \textit{i.e.} feature fusion,
+%to improve the performance of their CNN architectures.
 
@@
 
-\begin{figure}[ht]
-\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
-\caption{Framework (example of $n=10, \calC=3, m=3$)}
-\label{fig:framework}
-\end{figure}
-
 \subsection{Problem Formulation}
@@
 Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
-Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times m}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
-Let $\bL = [ \bL_1, \bL_2, ..., \bL_\calC ]$.
+Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
+Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
 %%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
@@
 On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
-{\small
-$$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
+{
+\begin{align}
+|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
+\end{align}
 }
@@
 Thus, the proposed model can be written as below:
-{\small
+{
 \begin{align}\label{eq:l12_rankconstraint}
   \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
-  \st ~&~ \rank(\bX) = p   ,
+  \st ~&~ \rank(\bX) = p
 \end{align}
@@
 We hence transform the original problem as a matrix factorization formulation as below:
-{\small
+{
 \begin{align}\label{eq:l12_mf}
@@
 By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
-{\small
+{
 \begin{align}\label{eq:mf_l21_constrained}
@@
 The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
-{\small
+{
 \begin{align}\label{eq:lagrangian_l21}
@@
 \label{theorem:alm_convergence}
-  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
+  %Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point
+  %\footnote{the limit point of a sequence}~\cite{oh2016partial} $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
+  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
+  and $\{\blambda_k\}$ is bounded. Any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
 \end{theorem}
@@
 Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
-{\small
+{
 \begin{align}\label{eq:langrangian_wrt_X}
   \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
-              %= & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
-              %  & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
-              %= & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
-              = & || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
+              = & \frac{\mu}{2} || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
 \end{align}
@@
 Hence, we derive the following subproblem \wrt. $\bX$:
-{\small
+{
 \begin{align}\label{eq:subproblem_wrt_X}
@@
 The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
+In other words, we search the solution for $\bX$ in a low-rank subspace.
 Let $r$ be a known scalar.
 A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
-{\small
+{
 \begin{eqnarray}
@@
 which is obtained as below
-{\small
+{
 \begin{eqnarray}\label{eq:tangent_vector}
@@
 projection of $\G$ onto the tangent space at $\bX$:
-{\small
+{
 \begin{eqnarray}\label{eq:grad}
@@
 
-%\begin{small}
-\begin{algorithm}
-  \begin{algorithmic}
-    \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.
-
-    \STATE 1. $\bR_{u} \leftarrow \G^{\trsp} \U$, $\bR_{v} \leftarrow \G \V$.
-
-    \STATE 2. $\bM \leftarrow \U^{\trsp} \bR_{v}$.
-
-    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
-
-    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.
-
-  \end{algorithmic}
-  \caption{Computation of $\grad f(\bX)$ (Algorithm 2 in~\cite{vandereycken2013lowrank})}
-  \label{alg:compute_riemannian_grad}
-\end{algorithm}
-%\end{small}
-
 \begin{lemma}
@@
 \begin{proof}
-  The proof can be found in Appendix B.
+\begin{align}
+\label{eq:proof_lemma1}
+       & \grad f(\bX) \\
+       & = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp}  \nonumber \\
+       & = \U(\U^{\trsp} \G \V) \V^{\trsp} + (\bR_{v} - \U \bM) \V^{\trsp} + \U (\bR_{u} - \V \bM^{\trsp})^{\trsp} \nonumber \\
+       & = P_{\U} \G P_{V} + \G \V \V^{\trsp} - \U \bM \V^{\trsp} + \U \U^{\trsp} \G - \U \bM \V^{\trsp} \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U \bM \V^{\trsp} + P_{U} \G  \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U (\U^{\trsp} \bR_{v}) \V^{\trsp} + P_{U} \G  \nonumber \\
+       & = P_{\U} \G P_{V} + \G P_{V} - 2\U (\U^{\trsp} \G \V) \V^{\trsp} + P_{U} \G  \nonumber \\
+%       & = P_{\U} \G P_{V} + \G P_{V} - \U (\U^{\trsp} \G \V) \V^{\trsp} + P_{U} \G - \U (\U^{\trsp} \G \V) \V^{\trsp} \nonumber \\
+       & = P_{\U} \G P_{V} + (\bI - P_{U}) \G P_{V} + P_{U} \G (\bI - P_{V})  \nonumber \\
+       & = P_{\U} \G P_{V} + P_{U}^{\perp} \G P_{V} + P_{U} \G P_{V}^{\perp}  ,
+\end{align}
 \end{proof}
 
-%\begin{small}
+\begin{algorithm}
+  \begin{algorithmic}
+    \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.
+    \STATE 1. $\bR_{u} \leftarrow \G^{\trsp} \U$, $\bR_{v} \leftarrow \G \V$.   
+    \STATE 2. $\bM \leftarrow \U^{\trsp} \bR_{v}$.    
+    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
+    \ENSURE $\grad f(\bX) = \U \bM \V^{\trsp} + \U_{p} \V^{\trsp} + \U \V_{p}^{\trsp} \in T_{\bX}\M_{r}$.    
+  \end{algorithmic}
+  \caption{Computation of $\grad f(\bX)$ (Algorithm 2 in~\cite{vandereycken2013lowrank})}
+  \label{alg:compute_riemannian_grad}
+\end{algorithm}
+
+Based on the above discussion, the solution of $\bX$ can be solved by Algorithm~\ref{alg:LRGeomCG} as following:
+
 \begin{algorithm}
@@
 \end{algorithm}
-%\end{small}
 
 Particularly, in Step 2 of Algorithm~\ref{alg:LRGeomCG}, $\beta_{k}$ is determined by a Polak-Ribi$\grave{e}$re (PR+) rule~\cite{vandereycken2013lowrank}:
-{\small
+{
 \begin{eqnarray}\label{eq:beta}
@@
 The step size $t_{k}$ in Step 3, given a search direction $\bfeta_{k} \in T_{\bX_{k} \M_{r}}$, is chosen such that
-{\small
+{
 \begin{align}\label{eq:choose_step_size}
@@
 }
-{\small
+{
 \begin{align}\label{eq+choose_step_size2}
@@
 Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
-%\begin{align}\label{eq:subproblem_wrt_E_1}
-%  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
-%              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
-%\end{align}
-{\small
+{
 \begin{align}\label{eq:subproblem_wrt_E_1}
@@
 We thus obtain the subproblem \wrt. $\bE$ as below:
-{\small
+{
 \begin{align}\label{eq:subproblem_wrt_E_2}
@@
 The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
-{\small
+{
 \begin{align}\label{eq:column_wise_soft_thresholding}
@@
     }
-    \caption{visualized results of the synthetic dataset} \label{fig:ensemble_cluster}
+    \caption{Visualized results of the synthetic dataset.
+    We use different colors to represent different label for each instance.
+	Fig.~\ref{subfig:gt_pdf} show the visualized ground truth data,
+	and each row corresponds to one instance with the class label represented by color.
+	Fig.~\ref{subfig:er_pdf} has 15 columns, each represents one classifiers's predictions.
+	There are also 15 columns in Fig.~\ref{subfig:re_pdf}, which is generated by the recovered results from our algorithm.
+	%Each subfigure contains $n\times m$ small narrow blocks visualized in diverse color according to different labels.
+    %Each picture represents a $280$ instances's information with every $20$ colums corresponding to one classifier.
+    %We use different colors to represent different binary indicator predictions~(20 dimensions).
+    %For~\ref{subfig:gt_pdf}, there is the ground truth information of $280$ instances for $15$ classifiers.
+    %Obviously, the ground truth for different classifiers is the same.
+    %Each kind of color represents one class, and the ground truth picture is generated from 280 synthetic instance lables.
+    %Random noise picture~\ref{subfig:er_pdf} show 15 classifiers's prediction results while the classification accuracy for each one is about 60\%.
+    %The last picture is the recovered result generated by our algorithm.
+    Obviously, most of the outlier elements are correctly recovered by our algorithm with only a few error predictions left.
+    }
+    \label{fig:ensemble_cluster}
 \end{figure}
+
+As we can observe, our proposed algorithm significantly detect the outliers,
+and furthermore, the outlier elements are accurately converted into the right predictions while preserving consistency among all classifiers.
 
@@
 \end{tabular}
+\caption{Mean accuracy using different strategies on three datasets.}
 \label{table:strategy}
 \end{table}
+
+\subsection{Comparision with State-of-the-art}
+
+In this sub-section, we compare the performance of our algorithm with the state-of-the-art techniques.
+%we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
+We use SVM classifiers based on different features in previous experiments to make a fair comparision with some MKL based mthods.
+Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
+in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
+Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table.\ref{table:state_of_the_art}.
+
+\begin{table}[ht]
+\begin{center}
+\begin{tabular}{ c | c | c }
+    \hline
+                                              & CIFAR-10             & CIFAR-100  \\\hline
+\multirow{2}{*}{ResNet~\cite{he2016identity}} & 110, 134, 164        & 56, 110, 164  \\
+                                              & $164^{*}$, $200^{*}$ & $110^{*}$, $164^{*}$  \\\hline
+\multirow{2}{*}{WRN~\cite{zagoruyko2016wide}} & 16-10, 22-8, 28-10   & 16-10, 22-8, 28-10  \\
+                                              &    40-4, 40-8        & 40-4  \\\hline
+NIN~\cite{lin2013network}                     &     -                & -  \\ \hline
+\end{tabular}
+\end{center}
+\caption{Model selection for CIFAR-10 dataset.
+In the ResNet block, numbers repersent the depth of the selected models.
+``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
+In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
+NIN network has only one formula, so we donot list its depth.}
+\label{table:models}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{c|c|c}\hline
+                                      &  CIFAR-10 & CIFAR-100  \\\hline
+NIN~\cite{lin2013network}             &   8.81    &  35.67     \\\hline
+Highway~\cite{srivastava2015highway}  &   7.72    &  32.39     \\\hline
+ELU~\cite{clevert2015fast}            &   6.55    &  24.28     \\\hline
+Pre-ResNet-1001~\cite{he2016identity} &   4.92    &  22.71     \\\hline
+WRN-28-10~\cite{zagoruyko2016wide}    &   4.17    &  20.50     \\\hline
+Ours                                  &   3.47    &  17.94     \\\hline
+\end{tabular}
+\caption{Test error of different methods on CIFAR-10 and CIFAR-100 with the same training strategies as the original paper~\cite{he2016identity,zagoruyko2016wide,lin2013network}.}
+\label{table:state_of_the_art}
+\end{table}
+
+As we can observe, our fusion is capable of further improving the performance of single model.
+A single model has limited performance even with deeper depth or wider channel.
+However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
 
@@
 
-\begin{quote}
-\begin{small}
-  \bibliographystyle{aaai}
+{\small
+\bibliographystyle{ieee}
 \bibliography{RLF_MF}
-\end{small}
-\end{quote}
+}
 
